---
title: "Drug_repurposing_genetic_screen_mouse_brain_10X_ALZ_v2"
output: html_document
author: "Linda Kvastad"
date: "2024-09-16"
---

NOTE: Plots part of Figure 7a.

Load libraries
```{r}
library(STutility)
library(dplyr)
library(tidyverse)
library(UpSetR)
library(ComplexHeatmap)
```


Load ST data:
```{r}

infoTable <- read.csv("seurat_objects/brain_mouse_10X/infoTable_mouse_coronal.csv", sep = ";")


se <- InputFromTable(infotable = infoTable, 
                      minUMICountsPerGene = 100, 
                      minSpotsPerGene = 5,
                      minUMICountsPerSpot = 500,
                      platform =  "Visium")

```

Load OpenTarget files: OBS! Update file location for relevant OpenTargets files
```{r}
get_opentarget <- function (opentarget_dir = paste0(getwd(),"/OpenTargets/all_traits_study"), mouse_genes = NULL ){
  OT.files <- list()
  disease.names <- character()
  i <- 1
  column.names <- c("Gene_symbol","Overall_assoc.score","Genetic_assoc.","Somatic_mutation","Drugs","Pathways_system_biology","Text_mining","RNA_expression","Animal_models","Target_name")
  
  if (!is.null(mouse_genes)){
    

      conversion.table <- read.table(mouse_genes,
                                     sep = "\t",
                                     header = TRUE) 
      #if mouse_genes dataframe is specified, load it

  }
  
  for (OT.file in list.files(opentarget_dir)){
    if (grepl("diseases_", OT.file)){
      print(OT.file)
  
      df <- read.table(paste(opentarget_dir, OT.file, sep= "/"),
                     sep= "\t",
                     header=TRUE,
                     quote = "")
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
    
      
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
      
      if (!is.null(mouse_genes)){
        df$Gene_symbol <- conversion.table[match(df$Gene_symbol,conversion.table$hgnc_symbol),]$mgi_symbol #convert human to mouse annotation
        OT.files[[i]] <- df
        } else {
          OT.files[[i]] <- df
        }
      i <- i+1
      disease.name <- sub(".*diseases_","", OT.file)
      disease.name <- gsub(".tsv", "", disease.name)
      disease.names <- append(disease.names, disease.name)
    }
  }

  names(OT.files) <-  disease.names
  OT.files <- map(OT.files, ~.x %>%
                    distinct())
  return(OT.files)
}
```

OBS! Update file location for relevant OpenTargets files
```{r}
OpenTargets.path <- "OpenTargets/all_traits_study"
OT.files <- get_opentarget( opentarget_dir = OpenTargets.path ,mouse_genes = "mouse_human_genes_feb_23.tsv")
#OT.files.human <-get_opentarget(opentarget_dir = OpenTargets.path)

```

#Clean out genes not present in the Seurat object AND removes duplicates
```{r}
# clean OT.files from duplicates
OT.files <- map(OT.files, ~.x %>%
  dplyr::select(Gene_symbol, Overall_assoc.score, Genetic_assoc.,Drugs, Animal_models)%>%
  distinct() %>%
  filter(!is.na(Gene_symbol)&Gene_symbol %in% rownames(se)) %>%
    group_by(Gene_symbol)%>%
  dplyr::slice(which.max(Overall_assoc.score))%>% #==> when there is a gene mentioned twice, only keep the row where the overall association score is the highest ==> reason for duplicates is that multiple human genes have the same mouse homolog etc...
    ungroup())

# saveRDS(OT.files, file = paste("OpenTargets", sample,"OT_files_list.rds", sep = "/"))


```

Gene sets for MOUSE
```{r}
#create gene sets from the 
all_gene_sets <- list()
list.names <- character()
i <- 1
j <- 1
for (df in OT.files){
  ## Genes overall association score
  OpenTarget_Overall_assoc.score_xxx <- arrange(df, desc(Overall_assoc.score))
  OpenTarget_Overall_assoc.score_xxx <- OpenTarget_Overall_assoc.score_xxx[!is.na(OpenTarget_Overall_assoc.score_xxx$Overall_assoc.score),]$Gene_symbol
  ## Genes genetic association score
  OpenTarget_Genetic_assoc._xxx <- arrange(df, desc(Genetic_assoc.))
  OpenTarget_Genetic_assoc._xxx <- OpenTarget_Genetic_assoc._xxx[!is.na(OpenTarget_Genetic_assoc._xxx$Genetic_assoc.),]$Gene_symbol
  print(length(OpenTarget_Genetic_assoc._xxx))
  ## Genes drug target
  OpenTarget_Drugs_xxx <- arrange(df, desc(Drugs))
  # print(dim(OpenTarget_Drugs_xxx_top100_[!is.na("Drugs"),]))
  OpenTarget_Drugs_xxx <- OpenTarget_Drugs_xxx[!is.na(OpenTarget_Drugs_xxx$Drugs),]$Gene_symbol
  all_gene_sets[[i]] <- unique(OpenTarget_Overall_assoc.score_xxx)
  all_gene_sets[[i+1]] <- unique(OpenTarget_Genetic_assoc._xxx)
  all_gene_sets[[i+2]] <- unique(OpenTarget_Drugs_xxx)
  list.names <- append(list.names,(c(gsub("xxx", names(OT.files[j]),"OpenTarget_Overall_assoc.score_xxx"),
                            gsub("xxx", names(OT.files[j]),"OpenTarget_Genetic_assoc._xxx"),
                            gsub("xxx", names(OT.files[j]),"OpenTarget_Drugs_xxx"))))
  j <- j+1
  i <- i+3
}
names(all_gene_sets) <- list.names
```

Subsetting list to only Drugs gene lists
```{r}
patterns <- c("Drugs")

all_gene_sets <- all_gene_sets[grep(
  paste(patterns, collapse = "|"),
  names(all_gene_sets),
  ignore.case = TRUE
  )]
```

Removing empty terms
```{r}
all_gene_sets$OpenTarget_Drugs_total_cholesterol_measurement_v23.06
all_gene_sets$OpenTarget_Drugs_total_cholesterol_measurement_v23.06 <- NULL
all_gene_sets$OpenTarget_Drugs_low_density_lipoprotein_cholesterol_measurement_v23.06
all_gene_sets$OpenTarget_Drugs_low_density_lipoprotein_cholesterol_measurement_v23.06 <- NULL
```

Load ALZ genetic and drug gene list
```{r}
OpenTargets_ALZ_Genetic_ <- as.character(t(read.table(file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ALZ_Genetic.csv")))
OpenTargets_ALZ_Genetic_top_ <- OpenTargets_ALZ_Genetic_[1:70]

OpenTargets_ALZ_drug_targets_ <- as.character(t(read.table(file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ALZ_Drugs.csv")))
length(OpenTargets_ALZ_drug_targets_)

```



```{r}
# Initialize an empty vector to store all genes
all_genes <- c()

# Loop through each element in the list
for (i in 1:length(all_gene_sets)) {
  # Concatenate the genes from each list element
  all_genes <- c(all_genes, all_gene_sets[[i]])
}

# Get unique genes
all_genes <- c(all_genes,OpenTargets_ALZ_Genetic_,OpenTargets_ALZ_drug_targets_)
all_genes <- unique(all_genes)

```


Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```


Non-brain and brain related traits
```{r}
all_gene_sets_brain_traits <- all_gene_sets
all_gene_sets_brain_traits$OpenTarget_Drugs_chronic_obstructive_pulmonary_disease_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_crohns_disease_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_myocardial_infarction_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_ulcerative_colitis_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_liver_disease_v23.09 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_cirrhosis_of_liver_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_coronary_artery_disease_v23.06 <- NULL
all_gene_sets_brain_traits$`OpenTarget_Drugs_non-alcoholic_fatty_liver_disease_v23.06` <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_inflammatory_bowel_disease_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_lung_disease_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_chronic_kidney_disease_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_congenital_heart_disease_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_bronchial_disease_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_asthma_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_type_1_diabetes_mellitus_v24.03 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_type_2_diabetes_mellitus_v24.03 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_large_intestine_disorder_v23.06 <- NULL
all_gene_sets_brain_traits$OpenTarget_Drugs_inherited_kidney_disorder_v23.06 <- NULL


all_gene_sets_non_brain_traits <- all_gene_sets
all_gene_sets_non_brain_traits$OpenTarget_Drugs_epilepsy_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_autism_spectrum_disorder_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_attention_deficit_hyperactivity_disorder_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_insomnia_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_major_depressive_disorder_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_anterior_horn_disorder_v23.12 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_alzheimer_disease_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_amyotrophic_lateral_sclerosis_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_bipolar_disorder_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_schizophrenia_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_parkinson_disease_v23.06 <- NULL
all_gene_sets_non_brain_traits$OpenTarget_Drugs_multiple_sclerosis_v23.06 <- NULL

```


```{r}
# Initialize an empty vector to store all genes
all_genes_brain <- c()

# Loop through each element in the list
for (i in 1:length(all_gene_sets_brain_traits)) {
  # Concatenate the genes from each list element
  all_genes_brain <- c(all_genes_brain, all_gene_sets_brain_traits[[i]])
}

# Get unique genes for all brain and non-brain traits
all_genes_brain <- unique(all_genes_brain)

```


```{r}
# Initialize an empty vector to store all genes
all_genes_non_brain <- c()

# Loop through each element in the list
for (i in 1:length(all_gene_sets_non_brain_traits)) {
  # Concatenate the genes from each list element
  all_genes_non_brain <- c(all_genes_non_brain, all_gene_sets_non_brain_traits[[i]])
}

# Get unique genes for all brain and non-brain traits
all_genes_non_brain <- unique(all_genes_non_brain)

```

```{r}
# Number of drug targets in brain related traits
length(all_genes_brain)

# Number of drug targets in non-brain related traits
length(all_genes_non_brain)

# Number of overlapping genes between brain and non-brain related traits
length(intersect(all_genes_brain,all_genes_non_brain))

```



Select genes for correlation analysis
```{r}
# Include genetic genes from top or all, depending on which enrichment selection you are interested in from your gene list. Also include all drug targets for brain and non-brain related traits that overlap with all genetically associated genes for the trait.
all_genes_cormat <- unique(c(OpenTargets_ALZ_Genetic_top_,(all_genes_brain[all_genes_brain %in% OpenTargets_ALZ_Genetic_]),(all_genes_non_brain[all_genes_non_brain %in% OpenTargets_ALZ_Genetic_])))


#subset_genes_cormat <- unique(c(all_genes_non_brain[all_genes_non_brain %in% all_genes_cormat],all_genes_brain[all_genes_brain %in% all_genes_cormat]))

```


Select data from OT gene list
```{r}
mydata <- FetchData(se,vars=all_genes_cormat)
```


Create spearman correlation heat map
```{r}
cormat <- cor(mydata,method = c("spearman"))
melted_cormat <- reshape2::melt(cormat)
melted_cormat$value <- ifelse(melted_cormat$Var1 == melted_cormat$Var2, NA, melted_cormat$value)

```


Prepare data legends
```{r}
ALZ_genes_legend_Genetic <- as.character(rownames(cormat) %in% OpenTargets_ALZ_Genetic_)
ALZ_genes_legend_Genetic <- replace(ALZ_genes_legend_Genetic,ALZ_genes_legend_Genetic=="TRUE","ALZ_Genetic")
ALZ_genes_legend_Genetic <- replace(ALZ_genes_legend_Genetic,ALZ_genes_legend_Genetic=="FALSE","nonALZ_Genetic")

ALZ_genes_legend_Drugs <- as.character(rownames(cormat) %in% OpenTargets_ALZ_drug_targets_)
ALZ_genes_legend_Drugs <- replace(ALZ_genes_legend_Drugs,ALZ_genes_legend_Drugs=="TRUE","ALZ_Drug_targets")
ALZ_genes_legend_Drugs <- replace(ALZ_genes_legend_Drugs,ALZ_genes_legend_Drugs=="FALSE","nonALZ_Drug_targets")

Brain_trait_genes_legend <- as.character(rownames(cormat) %in% all_genes_brain)
Brain_trait_genes_legend <- replace(Brain_trait_genes_legend,Brain_trait_genes_legend=="TRUE","Brain_traits_drug_targets")
Brain_trait_genes_legend <- replace(Brain_trait_genes_legend,Brain_trait_genes_legend=="FALSE","nonBrain_traits")

Non_brain_trait_genes_legend <- as.character(rownames(cormat) %in% all_genes_non_brain)
Non_brain_trait_genes_legend <- replace(Non_brain_trait_genes_legend,Non_brain_trait_genes_legend=="TRUE","Non_brain_trait_drug_targets")
Non_brain_trait_genes_legend <- replace(Non_brain_trait_genes_legend,Non_brain_trait_genes_legend=="FALSE","Brain_traits")


df_legend <- data.frame(ALZ_genes_legend_Genetic,ALZ_genes_legend_Drugs,Brain_trait_genes_legend,Non_brain_trait_genes_legend)

```


```{r}
library(circlize)
col_fun = colorRamp2(c(-0.4, 0, 0.4), c("blue","white","red"))
col_fun(seq(-3, 3))
```


Complex Heatmaps
```{r}
#Heatmat annotations
ha = HeatmapAnnotation(
    ALZ_genetic = ALZ_genes_legend_Genetic,
    ALZ_drug_targets = ALZ_genes_legend_Drugs,
    Brain_traits_drug_targets = Brain_trait_genes_legend,
    Non_brain_trait_drug_targets = Non_brain_trait_genes_legend,
    col = list(ALZ_genetic = c("ALZ_Genetic" = "dodgerblue3", "nonALZ_Genetic" = "white"),
               ALZ_drug_targets =c("ALZ_Drug_targets"="red","nonALZ_Drug_targets"="white"),
               Brain_traits_drug_targets = c("Brain_traits_drug_targets" = "gold", "nonBrain_traits" = "white"),
               Non_brain_trait_drug_targets = c("Non_brain_trait_drug_targets" = "gold4", "Brain_traits" = "white")
    ),
    annotation_legend_param = list(at=c("ALZ_Genetic","ALZ_Drug_targets","Brain_traits_drug_targets","Non_brain_trait_drug_targets"))
)

set.seed(123)

myheatmap <-  Heatmap(cormat,name="Spearman\nCorrelation",row_names_gp = gpar(fontsize = 4),column_names_gp = gpar(fontsize = 4),clustering_method_columns = "complete",clustering_method_rows = "complete",show_row_dend = F,show_column_names = T,top_annotation = ha,row_split = 3, column_split = 3,col = col_fun)

myheatmap
```


PDF
```{r, eval=FALSE}
pdf(file = "Drug_repurposing_genetic_top70_screen_mouse_brain_10X_ALZ.pdf", height = 7, width = 10)

myheatmap

dev.off()
```


Find drug targets that spatially co-localize with trait enriched tissue substructures by selecting the heatmap cluster that includes substructure specific genes.
```{r}
# Initialize the heatmap (this ensures clusters are finalized)
myheatmap <- draw(myheatmap)

# Extract the row order of genes for each cluster
row_order_list <- row_order(myheatmap)

# Retrieve the genes in clusters of interest
genes_cluster_3 <- rownames(cormat)[row_order_list[[3]]]

genes_clusters_of_interest <- c(genes_cluster_3)

# Print or store the genes in cluster of interest
print(genes_clusters_of_interest)

```


Non-intersected genes
```{r}
# Add a not-in function
`%!in%` <- Negate(`%in%`)
```


Drug targets with genetic evidence brain related traits
```{r}
Brain_trait_genes <- unique(genes_clusters_of_interest[genes_clusters_of_interest %in% all_genes_brain])
Non_brain_trait_genes <- unique(genes_clusters_of_interest[genes_clusters_of_interest %in% all_genes_non_brain])


length(Brain_trait_genes)
length(Non_brain_trait_genes)
length(intersect(Brain_trait_genes,Non_brain_trait_genes))

ALZ_brain_drug_targets <- unique(OpenTargets_ALZ_Genetic_[OpenTargets_ALZ_Genetic_ %in% Brain_trait_genes])
ALZ_brain_drug_targets

ALZ_non_brain_drug_targets <- unique(OpenTargets_ALZ_Genetic_[OpenTargets_ALZ_Genetic_ %in% Non_brain_trait_genes])
ALZ_non_brain_drug_targets

Potential_new_drug_targets <- unique(c(ALZ_brain_drug_targets,ALZ_non_brain_drug_targets))
Potential_new_drug_targets <- unique(Potential_new_drug_targets[Potential_new_drug_targets %!in% OpenTargets_ALZ_drug_targets_])
Potential_new_drug_targets
```


```{r, fig.height=4, fig.width=10}
ST.FeaturePlot(se, features = Potential_new_drug_targets, cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3, grid.ncol = 2)
```



Create matrix with drug target candicates and from which drug gene lists they overalped with
```{r}
Drug_repurposing_candidates <- as.data.frame(matrix(data = NA, nrow = length(Potential_new_drug_targets), ncol = 2, dimnames = list(Potential_new_drug_targets,c("Potential_new_drug_targets","OpenTargets_Drug_gene_list_overlap"))))

Drug_repurposing_candidates$Potential_new_drug_targets <- Potential_new_drug_targets


```


```{r}
# Loop through each target in Potential_new_drug_targets
for (i in 1:length(Potential_new_drug_targets)) {
    # Check which gene sets contain the current drug target
    found_in <- sapply(all_gene_sets, function(x) Potential_new_drug_targets[i] %in% x)
    
    # Get the names of the gene sets where the target was found
    found_gene_sets <- names(all_gene_sets)[found_in]
    
    # Remove the 'OpenTarget_Drugs_' prefix from each found gene set name
    found_gene_sets_clean <- gsub("OpenTarget_Drugs_", "", found_gene_sets)
    
    # Store the results as a comma-separated string in column 2 of the matrix
    Drug_repurposing_candidates[i, 2] <- paste(found_gene_sets_clean, collapse = ", ")
}

# View the updated matrix
Drug_repurposing_candidates

```

Save
```{r, eval=FALSE}
write.table(Drug_repurposing_candidates,file = "Drug_repurposing_genetic_screen_output/Drug_repurposing_genetic_screen_mouse_brain_10X_ALZ_top70.csv", row.names = F, col.names = T,sep = ";")
```



Notes
```{r}
sessionInfo()
```

