---
title: "pval_distribution_[significant_drug_genes_and_all_genes_pvalues]_selected_tissue_trait_pairs"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Creates the plot for Figure 2 e, and calculates the pi1 statistics (nominal p-value distribution) for selected trait-tissue pairs, by calculating the proportion of significant drug target enriched structures that are also enriched for genetically implicated gene sets (genetic all).

#Load libraries
```{r}
library(dplyr)
library(ggplot2)
library(qvalue)
```


#Load data
```{r}
pval_data <- read.csv(file="pval_distribution_[all_datasets]_summary_selected_tissue_trait_pairs.csv",sep = ";")
```


Subset to significant drug targets
```{r}
#subset to significant drugs (based on p.val.adj)
data_drugs <- subset(pval_data, neg.log10.p.val.adj_drugs >= -log10(0.05))

# Remove rows with N/A (some traits did not have drug associated genes on Open Targets)
data_drugs[data_drugs == "N/A"] <- NA
data_drugs <- na.omit(data_drugs)

#remove columns with genetic data
data_drugs <- data_drugs[, !names(data_drugs) %in% c("median.score_genetic","neg.log10.p.val_genetic","neg.log10.p.val.adj_genetic")]
```


```{r}
# select traits to get allGene data from
patterns <- names(table(data_drugs$trait))

# Combine patterns into a single regular expression
pattern_string <- paste(patterns, collapse = "|")

# Subset rows from pval_data where trait matches any of the patterns
data_drugs_allGenes <- pval_data[grepl(pattern_string, pval_data$trait), ]

# Only include data from allGenes
data_drugs_allGenes <- data_drugs_allGenes[grepl("all", data_drugs_allGenes$gene_list), ]

# Find traits with no drug data
no_drug_data <- pval_data[!grepl("top", pval_data$gene_list), ]
no_drug_data <- no_drug_data[grepl("N/A", no_drug_data$neg.log10.p.val.adj_drugs), ]
patterns_no_drugs <- names(table(no_drug_data$trait))
pattern_string_no_drugs <- paste(patterns_no_drugs, collapse = "|")

# Subset rows from data_drugs_allGenes to remove traits with no pval data
data_drugs_allGenes <- data_drugs_allGenes[!grepl(pattern_string_no_drugs, data_drugs_allGenes$trait), ]

# Prepare for merging: remove columns and only save allGene data and identifiers
data_drugs_allGenes <- data_drugs_allGenes[, names(data_drugs_allGenes) %in% c("dataset","trait","cluster","median.score_genetic","neg.log10.p.val_genetic","neg.log10.p.val.adj_genetic")]
```

Merge
```{r}
# Merge the data
pval_data_allGenes_of_drugs <- merge(data_drugs,data_drugs_allGenes)

```

Change p-value scale
```{r}
# change from character to numeric
pval_data_allGenes_of_drugs$neg.log10.p.val_genetic <- as.numeric(pval_data_allGenes_of_drugs$neg.log10.p.val_genetic)

# change/add new p-value scale to dataframe
pval_data_allGenes_of_drugs$p.val_genetic <- 10^(-pval_data_allGenes_of_drugs$neg.log10.p.val_genetic)
```

Plot
```{r}
theme_set(theme_classic())

# Color by groups
p1 <- ggplot(pval_data_allGenes_of_drugs, aes(x=p.val_genetic)) + 
                geom_histogram(alpha=1, color="black",position="identity", fill="grey") +
                ylab("trait-structure pairs")+
                xlab("p-values Genetic") +
                ggtitle("Significant Drug targets") +
                ylim(0,250)+
                #coord_cartesian(ylim = c(0, 10))+
                theme_classic(base_size = 25)+
                theme(plot.title = element_text(size = 25))+
                geom_vline(xintercept = 0.05, linetype = "dashed", color = "red", size = 1)

p1
```


PDF
```{r, eval=FALSE}
pdf(file = "Fig_traits_with_significant_drug_targets_all_Genes_selected_tissue_trait_pairs.pdf", width=5,height=5)

p1

dev.off()
```



Estimate π1 with pi0est function from the qvalue package
```{r}
pi0_estimate <- pi0est(p=pval_data_allGenes_of_drugs$p.val_genetic, pi0.method = c("bootstrap"))
pi0_estimate

pi0 <- pi0_estimate$pi0
pi1 <- 1-pi0

pi1
```



#Notes
```{r}
sessionInfo()
```

