---
title: "Step2.Generate_Metacell_with_STEAM"
output: html_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---



# Load libraries

Load the necessary libraries.
```{r, message=FALSE, warning=FALSE}
library(Seurat)
library(SeuratObject)
library(dplyr)
library(steam)
library(future)
```


# Load data

Load Seurat object.
```{r}
se <- readRDS("Seurat_objects/se_250_cells_filtered_normalized.RDS")
se
head(se[[]])
```


Check number of cell per cell type of the cluster annotation you want to create Metacells from.
```{r}
table(se$subclass_label)
```


# Generat Metacell clusters


Here we want to generate Metacells from the cluster annotation 'subclass_label'. The generateMetacellClusters function subsets all selected clusters into separate Seurat objects and then uses NormalizeData, FindVariableFeatures, ScaleData, RunPCA and FindNeighbors on each and saving the to a list. For each Seurat in the list the optimal clustering resolution setting test iterated using the FindClusters function, starting at a user given inital resolution (initial_resolution) and moving by 0.1 until the average number of cells per cluster (future Metacell) is > 10 (num_cells_per_metacell). The generateMetacellClusters iterations then reduces the clustering resolution with 0.1 if the average number of cells per cluster (future Metacell) is < 10 (num_cells_per_metacell), and then stops.

Please note that if the desired number of average cells per cluster is not possible the reach, the function will stall out. If that happens try using +/- 1 desired number of average cells per cluster and re-run.
```{r}
plan("sequential")

metacells <- generate_metacell_clusters(
   se = se,
   cluster_anno = "subclass_label",
   num_cells_per_metacell = 10,
   pca_dims = 10,
   initial_resolution = 0.1
 )

```


Lets investigate the output and look at the distribution of the number of cells per cluster that we will aggregate into Metacells. All look good to go, watch out for extremely skewed distributions. If that happens, investigate if other QC filtering settings after subsampling might help.
```{r}
# Count how many cells per type
cell_counts <- table(se$subclass_label)

# Keep only those with at least 50 cells
valid_cell_types <- names(cell_counts[cell_counts >= 50])

# Extract only valid cell types present in the data
cell_types <- intersect(unique(se$subclass_label), valid_cell_types)

# Sort alphabetically
sorted_indices <- order(cell_types)
cell_types <- cell_types[sorted_indices]
metacells <- metacells[sorted_indices]  # reorder metacells to match

# Check clustering and print number of clusters for each cell type subset
invisible(lapply(1:length(metacells), function(i) {
    ct_subset <- metacells[[i]]  # Get the current cell type subset

    # Get the number of clusters (unique values in the 'seurat_clusters' column)
    num_clusters <- length(unique(ct_subset$seurat_clusters))

    # Print the number of clusters for the current cell type
    print(paste("Number of clusters for cell type", cell_types[i], ":", num_clusters))

    # Size of each cluster (how many cells per cluster)
    print(paste("Cluster distribution:"))
    cluster_distribution <- table(ct_subset$seurat_clusters)
    print(cluster_distribution)

    # Plot the histogram of the cluster distribution
    hist(cluster_distribution,
         main = paste("Cluster distribution for", cell_types[i]),
         xlab = "Cells in MetaCluster",
         ylab = "Number of MetaClusters",
         col = "lightblue",
         border = "black")

    # Calculate the mean and median of the cluster distribution
    mean_cluster_size <- mean(cluster_distribution)
    median_cluster_size <- median(cluster_distribution)

    # Add a red line at the mean and blue to the median
    abline(v = mean_cluster_size, col = "red", lwd = 2, lty = 2)
    abline(v = median_cluster_size, col = "blue", lwd = 2, lty = 2)

    print("________________________________________________________________")
}))
```


# Aggregate Metacell clusters

Now, let's aggregates the expression data across clusters (Metacells) by summing counts within each cluster of each cell type, and create a Metacell Seurat object!
```{r}
metacell_seurat <- aggregate_metacells(metacells, cluster_col = "subclass_label")
table(metacell_seurat$subclass_label)
metacell_seurat
```

Check results
```{r, fig.height=15}
VlnPlot(metacell_seurat, features = c("nFeature_RNA", "nCount_RNA"), ncol = 1, group.by = "subclass_label")
```

Save the Metacell Seurat object for downstream analysis!
```{r, eval=TRUE}
saveRDS(metacell_seurat, file = "Seurat_objects/Metacell.rds")
```


Normalize data with SCTransform.
```{r, message=FALSE, warning=FALSE, results='hide', , eval=TRUE}
options(future.globals.maxSize = 4 * 1024^3)
metacell_seurat_normalized <- SCTransform(metacell_seurat,assay = "RNA",return.only.var.genes = T)
```


```{r}
metacell_seurat_normalized
```

Save the normalized Metacell Seurat object for downstream analysis!
```{r, eval=TRUE}
saveRDS(metacell_seurat_normalized, file = "Seurat_objects/Metacell_normalized.rds")
```


Notes
```{r}
sessionInfo()
```


