---
title: "pval_distribution_all_cor_[kidney_datasets]_spearman"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Script for calculating Spearman correlations across spatial structures for selected tissue-trait pairs from all genetically associated genes. Comparing p-values and a) genes or b) UMIs. This was done for data generated for each organ and the output summarized in organ specific files. See folder named 'pval_data_cor_organs_all_traits_spearman' for all such files.

# Load libraries
```{r}
library(scales)
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(MASS)
```



# Load data
Load distribution data:
```{r}

# KIDNEY

##human_JCI
meta.data.CKD_human_JCI <- readRDS(file = "Kidney/human_JCI/p_value_distribution/pval.distribution_CKD_all_genes.RDS")

meta.data.IKD_human_JCI <- readRDS(file = "Kidney/human_JCI/p_value_distribution/pval.distribution_IKD_all_genes.RDS")


##mouse_10X_coronal
meta.data.CKD_mouse_10X_coronal <- readRDS(file = "Kidney/mouse_10X_coronal/p_value_distribution/pval.distribution_CKD_all_genes.RDS")

meta.data.IKD_mouse_10X_coronal <- readRDS(file = "Kidney/mouse_10X_coronal/p_value_distribution/pval.distribution_IKD_all_genes.RDS")


##mouse_JCI
meta.data.CKD_mouse_JCI <- readRDS(file = "Kidney/mouse_JCI/p_value_distribution/pval.distribution_CKD_all_genes.RDS")

meta.data.IKD_mouse_JCI <- readRDS(file = "Kidney/mouse_JCI/p_value_distribution/pval.distribution_IKD_all_genes.RDS")

```



# human_JCI
```{r}
# human_JCI
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JCI_CKD = data.frame(median.genes = (cor(x=meta.data.CKD_human_JCI$`-log10(p.val_genetic)`,y=meta.data.CKD_human_JCI$`median(genes)`,method = "spearman")))
data_cor_human_JCI_CKD = cbind(data_cor_human_JCI_CKD,data.frame(median.umi = (cor(x=meta.data.CKD_human_JCI$`-log10(p.val_genetic)`,y=meta.data.CKD_human_JCI$`median(umi)`,method = "spearman"))))
data_cor_human_JCI_CKD = cbind(data_cor_human_JCI_CKD,data.frame(median.score_genetic = (cor(x=meta.data.CKD_human_JCI$`-log10(p.val_genetic)`,y=meta.data.CKD_human_JCI$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JCI_CKD$trait <- "CKD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JCI_IKD = data.frame(median.genes = (cor(x=meta.data.IKD_human_JCI$`-log10(p.val_genetic)`,y=meta.data.IKD_human_JCI$`median(genes)`,method = "spearman")))
data_cor_human_JCI_IKD = cbind(data_cor_human_JCI_IKD,data.frame(median.umi = (cor(x=meta.data.IKD_human_JCI$`-log10(p.val_genetic)`,y=meta.data.IKD_human_JCI$`median(umi)`,method = "spearman"))))
data_cor_human_JCI_IKD = cbind(data_cor_human_JCI_IKD,data.frame(median.score_genetic = (cor(x=meta.data.IKD_human_JCI$`-log10(p.val_genetic)`,y=meta.data.IKD_human_JCI$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JCI_IKD$trait <- "IKD"


data_cor_human_JCI_all <- rbind(data_cor_human_JCI_CKD,data_cor_human_JCI_IKD)

```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_human_JCI_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_human_JCI_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_human_JCI_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```






# mouse_10X_coronal
```{r}
# mouse_10X_coronal
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_10X_coronal_CKD = data.frame(median.genes = (cor(x=meta.data.CKD_mouse_10X_coronal$`-log10(p.val_genetic)`,y=meta.data.CKD_mouse_10X_coronal$`median(genes)`,method = "spearman")))
data_cor_mouse_10X_coronal_CKD = cbind(data_cor_mouse_10X_coronal_CKD,data.frame(median.umi = (cor(x=meta.data.CKD_mouse_10X_coronal$`-log10(p.val_genetic)`,y=meta.data.CKD_mouse_10X_coronal$`median(umi)`,method = "spearman"))))
data_cor_mouse_10X_coronal_CKD = cbind(data_cor_mouse_10X_coronal_CKD,data.frame(median.score_genetic = (cor(x=meta.data.CKD_mouse_10X_coronal$`-log10(p.val_genetic)`,y=meta.data.CKD_mouse_10X_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_10X_coronal_CKD$trait <- "CKD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_10X_coronal_IKD = data.frame(median.genes = (cor(x=meta.data.IKD_mouse_10X_coronal$`-log10(p.val_genetic)`,y=meta.data.IKD_mouse_10X_coronal$`median(genes)`,method = "spearman")))
data_cor_mouse_10X_coronal_IKD = cbind(data_cor_mouse_10X_coronal_IKD,data.frame(median.umi = (cor(x=meta.data.IKD_mouse_10X_coronal$`-log10(p.val_genetic)`,y=meta.data.IKD_mouse_10X_coronal$`median(umi)`,method = "spearman"))))
data_cor_mouse_10X_coronal_IKD = cbind(data_cor_mouse_10X_coronal_IKD,data.frame(median.score_genetic = (cor(x=meta.data.IKD_mouse_10X_coronal$`-log10(p.val_genetic)`,y=meta.data.IKD_mouse_10X_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_10X_coronal_IKD$trait <- "IKD"


data_cor_mouse_10X_coronal_all <- rbind(data_cor_mouse_10X_coronal_CKD,data_cor_mouse_10X_coronal_IKD)

```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_10X_coronal_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_10X_coronal_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_10X_coronal_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


# mouse_JCI
```{r}
# mouse_JCI
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JCI_CKD = data.frame(median.genes = (cor(x=meta.data.CKD_mouse_JCI$`-log10(p.val_genetic)`,y=meta.data.CKD_mouse_JCI$`median(genes)`,method = "spearman")))
data_cor_mouse_JCI_CKD = cbind(data_cor_mouse_JCI_CKD,data.frame(median.umi = (cor(x=meta.data.CKD_mouse_JCI$`-log10(p.val_genetic)`,y=meta.data.CKD_mouse_JCI$`median(umi)`,method = "spearman"))))
data_cor_mouse_JCI_CKD = cbind(data_cor_mouse_JCI_CKD,data.frame(median.score_genetic = (cor(x=meta.data.CKD_mouse_JCI$`-log10(p.val_genetic)`,y=meta.data.CKD_mouse_JCI$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JCI_CKD$trait <- "CKD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JCI_IKD = data.frame(median.genes = (cor(x=meta.data.IKD_mouse_JCI$`-log10(p.val_genetic)`,y=meta.data.IKD_mouse_JCI$`median(genes)`,method = "spearman")))
data_cor_mouse_JCI_IKD = cbind(data_cor_mouse_JCI_IKD,data.frame(median.umi = (cor(x=meta.data.IKD_mouse_JCI$`-log10(p.val_genetic)`,y=meta.data.IKD_mouse_JCI$`median(umi)`,method = "spearman"))))
data_cor_mouse_JCI_IKD = cbind(data_cor_mouse_JCI_IKD,data.frame(median.score_genetic = (cor(x=meta.data.IKD_mouse_JCI$`-log10(p.val_genetic)`,y=meta.data.IKD_mouse_JCI$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JCI_IKD$trait <- "IKD"


data_cor_mouse_JCI_all <- rbind(data_cor_mouse_JCI_CKD,data_cor_mouse_JCI_IKD)

```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_JCI_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_JCI_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_JCI_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# Merge all histogram
```{r}
data_cor_human_JCI_all$dataset <- "human_JCI"
data_cor_human_JCI_all
data_cor_mouse_10X_coronal_all$dataset <- "mouse_10X_coronal"
data_cor_mouse_10X_coronal_all
data_cor_mouse_JCI_all$dataset <- "mouse_JCI"
data_cor_mouse_JCI_all

#Merge
data_cor_kidney_all_traits <- rbind(data_cor_human_JCI_all,data_cor_mouse_10X_coronal_all)
data_cor_kidney_all_traits <- rbind(data_cor_kidney_all_traits,data_cor_mouse_JCI_all)

#Save data
#saveRDS(data_cor_kidney_all_traits, file = "pval_data_cor_organs_all_traits_spearman/data_cor_kidney_all_traits_spearman.rds")
#write.matrix(data_cor_kidney_all_traits,file="pval_data_cor_organs_all_traits_spearman/data_cor_kidney_all_traits_spearman.csv",sep = ";")

```


## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_kidney_all_traits, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```
Median Genes
```{r}
# basic histogram
data_cor_kidney_all_traits_no_na <- na.exclude(data_cor_kidney_all_traits)

p <- ggplot(data_cor_kidney_all_traits_no_na, aes(x=median.genes)) + 
  geom_histogram(bins = (length(data_cor_kidney_all_traits_no_na$median.genes))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.genes)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_kidney_all_traits_no_na$median.genes)
print("mean")
mean(data_cor_kidney_all_traits_no_na$median.genes)
print("standard deviation")
sd(data_cor_kidney_all_traits_no_na$median.genes)
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_kidney_all_traits, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median UMI
```{r}
# basic histogram
data_cor_kidney_all_traits_no_na <- na.exclude(data_cor_kidney_all_traits)

p <- ggplot(data_cor_kidney_all_traits_no_na, aes(x=median.umi)) + 
  geom_histogram(bins = (length(data_cor_kidney_all_traits_no_na$median.umi))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.umi)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_kidney_all_traits_no_na$median.umi)
print("mean")
mean(data_cor_kidney_all_traits_no_na$median.umi)
print("standard deviation")
sd(data_cor_kidney_all_traits_no_na$median.umi)
```


## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_kidney_all_traits, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median score genetic
```{r}
# basic histogram
data_cor_kidney_all_traits_no_na <- na.exclude(data_cor_kidney_all_traits)

p <- ggplot(data_cor_kidney_all_traits_no_na, aes(x=median.score_genetic)) + 
  geom_histogram(bins = (length(data_cor_kidney_all_traits_no_na$median.score_genetic))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.score_genetic)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_kidney_all_traits_no_na$median.score_genetic)
print("mean")
mean(data_cor_kidney_all_traits_no_na$median.score_genetic)
print("standard deviation")
sd(data_cor_kidney_all_traits_no_na$median.score_genetic)
```


# Merge all Boxplot

## median.genes
```{r}
# Boxplot

data_cor_kidney_all_traits %>%
  ggplot( aes(x=trait, y=median.genes, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")

```


## median.umi
```{r}
# Boxplot

data_cor_kidney_all_traits %>%
  ggplot( aes(x=trait, y=median.umi, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```


## median.score_genetic
```{r}
# Boxplot

data_cor_kidney_all_traits %>%
  ggplot( aes(x=trait, y=median.score_genetic, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```

# Notes
```{r}
sessionInfo()
```

