---
title: "pval_distribution_all_cor_[intestine_datasets]_spearman"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Script for calculating Spearman correlations across spatial structures for selected tissue-trait pairs from all genetically associated genes. Comparing p-values and a) genes or b) UMIs. This was done for data generated for each organ and the output summarized in organ specific files. See folder named 'pval_data_cor_organs_all_traits_spearman' for all such files.

# Load libraries
```{r}
library(scales)
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(MASS)
```



# Load data
Load distribution data:
```{r}

# INTESTINE

##adult_HFGA_A1
meta.data.CD_adult_HFGA_A1 <- readRDS(file = "Intestine/adult_HFGA_A1/p_value_distribution/pval.distribution_CD_all_genes.RDS")

meta.data.UC_adult_HFGA_A1 <- readRDS(file = "Intestine/adult_HFGA_A1/p_value_distribution/pval.distribution_UC_all_genes.RDS")

meta.data.IBD_adult_HFGA_A1 <- readRDS(file = "Intestine/adult_HFGA_A1/p_value_distribution/pval.distribution_IBD_all_genes.RDS")

meta.data.LID_adult_HFGA_A1 <- readRDS(file = "Intestine/adult_HFGA_A1/p_value_distribution/pval.distribution_LID_all_genes.RDS")

##adult_RRST_349_B1
meta.data.CD_adult_RRST_349_B1 <- readRDS(file = "Intestine/adult_RRST_349_B1/p_value_distribution/pval.distribution_CD_all_genes.RDS")

meta.data.UC_adult_RRST_349_B1 <- readRDS(file = "Intestine/adult_RRST_349_B1/p_value_distribution/pval.distribution_UC_all_genes.RDS")

meta.data.IBD_adult_RRST_349_B1 <- readRDS(file = "Intestine/adult_RRST_349_B1/p_value_distribution/pval.distribution_IBD_all_genes.RDS")

meta.data.LID_adult_RRST_349_B1 <- readRDS(file = "Intestine/adult_RRST_349_B1/p_value_distribution/pval.distribution_LID_all_genes.RDS")


##mouse_healing_ctrl
meta.data.CD_mouse_healing_ctrl <- readRDS(file = "Intestine/mouse_healing_ctrl/p_value_distribution/pval.distribution_CD_all_genes.RDS")

meta.data.UC_mouse_healing_ctrl <- readRDS(file = "Intestine/mouse_healing_ctrl/p_value_distribution/pval.distribution_UC_all_genes.RDS")

meta.data.IBD_mouse_healing_ctrl <- readRDS(file = "Intestine/mouse_healing_ctrl/p_value_distribution/pval.distribution_IBD_all_genes.RDS")

meta.data.LID_mouse_healing_ctrl <- readRDS(file = "Intestine/mouse_healing_ctrl/p_value_distribution/pval.distribution_LID_all_genes.RDS")

##pcw12_HFGA_A8
meta.data.CD_pcw12_HFGA_A8 <- readRDS(file = "Intestine/pcw12_HFGA_A8/p_value_distribution/pval.distribution_CD_all_genes.RDS")

meta.data.UC_pcw12_HFGA_A8 <- readRDS(file = "Intestine/pcw12_HFGA_A8/p_value_distribution/pval.distribution_UC_all_genes.RDS")

meta.data.IBD_pcw12_HFGA_A8 <- readRDS(file = "Intestine/pcw12_HFGA_A8/p_value_distribution/pval.distribution_IBD_all_genes.RDS")

meta.data.LID_pcw12_HFGA_A8 <- readRDS(file = "Intestine/pcw12_HFGA_A8/p_value_distribution/pval.distribution_LID_all_genes.RDS")


##pcw19_HFGA_A4
meta.data.CD_pcw19_HFGA_A4 <- readRDS(file = "Intestine/pcw19_HFGA_A4/p_value_distribution/pval.distribution_CD_all_genes.RDS")

meta.data.UC_pcw19_HFGA_A4 <- readRDS(file = "Intestine/pcw19_HFGA_A4/p_value_distribution/pval.distribution_UC_all_genes.RDS")

meta.data.IBD_pcw19_HFGA_A4 <- readRDS(file = "Intestine/pcw19_HFGA_A4/p_value_distribution/pval.distribution_IBD_all_genes.RDS")

meta.data.LID_pcw19_HFGA_A4 <- readRDS(file = "Intestine/pcw19_HFGA_A4/p_value_distribution/pval.distribution_LID_all_genes.RDS")


```



# adult_HFGA_A1
```{r}
# adult_HFGA_A1
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_HFGA_A1_CD = data.frame(median.genes = (cor(x=meta.data.CD_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.CD_adult_HFGA_A1$`median(genes)`,method = "spearman")))
data_cor_adult_HFGA_A1_CD = cbind(data_cor_adult_HFGA_A1_CD,data.frame(median.umi = (cor(x=meta.data.CD_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.CD_adult_HFGA_A1$`median(umi)`,method = "spearman"))))
data_cor_adult_HFGA_A1_CD = cbind(data_cor_adult_HFGA_A1_CD,data.frame(median.score_genetic = (cor(x=meta.data.CD_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.CD_adult_HFGA_A1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_HFGA_A1_CD$trait <- "CD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_HFGA_A1_UC = data.frame(median.genes = (cor(x=meta.data.UC_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.UC_adult_HFGA_A1$`median(genes)`,method = "spearman")))
data_cor_adult_HFGA_A1_UC = cbind(data_cor_adult_HFGA_A1_UC,data.frame(median.umi = (cor(x=meta.data.UC_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.UC_adult_HFGA_A1$`median(umi)`,method = "spearman"))))
data_cor_adult_HFGA_A1_UC = cbind(data_cor_adult_HFGA_A1_UC,data.frame(median.score_genetic = (cor(x=meta.data.UC_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.UC_adult_HFGA_A1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_HFGA_A1_UC$trait <- "UC"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_HFGA_A1_IBD = data.frame(median.genes = (cor(x=meta.data.IBD_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.IBD_adult_HFGA_A1$`median(genes)`,method = "spearman")))
data_cor_adult_HFGA_A1_IBD = cbind(data_cor_adult_HFGA_A1_IBD,data.frame(median.umi = (cor(x=meta.data.IBD_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.IBD_adult_HFGA_A1$`median(umi)`,method = "spearman"))))
data_cor_adult_HFGA_A1_IBD = cbind(data_cor_adult_HFGA_A1_IBD,data.frame(median.score_genetic = (cor(x=meta.data.IBD_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.IBD_adult_HFGA_A1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_HFGA_A1_IBD$trait <- "IBD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_HFGA_A1_LID = data.frame(median.genes = (cor(x=meta.data.LID_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.LID_adult_HFGA_A1$`median(genes)`,method = "spearman")))
data_cor_adult_HFGA_A1_LID = cbind(data_cor_adult_HFGA_A1_LID,data.frame(median.umi = (cor(x=meta.data.LID_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.LID_adult_HFGA_A1$`median(umi)`,method = "spearman"))))
data_cor_adult_HFGA_A1_LID = cbind(data_cor_adult_HFGA_A1_LID,data.frame(median.score_genetic = (cor(x=meta.data.LID_adult_HFGA_A1$`-log10(p.val_genetic)`,y=meta.data.LID_adult_HFGA_A1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_HFGA_A1_LID$trait <- "LID"

data_cor_adult_HFGA_A1_all <- rbind(data_cor_adult_HFGA_A1_CD,data_cor_adult_HFGA_A1_IBD)
data_cor_adult_HFGA_A1_all <- rbind(data_cor_adult_HFGA_A1_all,data_cor_adult_HFGA_A1_LID)
data_cor_adult_HFGA_A1_all <- rbind(data_cor_adult_HFGA_A1_all,data_cor_adult_HFGA_A1_UC)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_adult_HFGA_A1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_adult_HFGA_A1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_adult_HFGA_A1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# adult_RRST_349_B1
```{r}
# adult_RRST_349_B1
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_RRST_349_B1_CD = data.frame(median.genes = (cor(x=meta.data.CD_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.CD_adult_RRST_349_B1$`median(genes)`,method = "spearman")))
data_cor_adult_RRST_349_B1_CD = cbind(data_cor_adult_RRST_349_B1_CD,data.frame(median.umi = (cor(x=meta.data.CD_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.CD_adult_RRST_349_B1$`median(umi)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_CD = cbind(data_cor_adult_RRST_349_B1_CD,data.frame(median.score_genetic = (cor(x=meta.data.CD_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.CD_adult_RRST_349_B1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_CD$trait <- "CD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_RRST_349_B1_UC = data.frame(median.genes = (cor(x=meta.data.UC_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.UC_adult_RRST_349_B1$`median(genes)`,method = "spearman")))
data_cor_adult_RRST_349_B1_UC = cbind(data_cor_adult_RRST_349_B1_UC,data.frame(median.umi = (cor(x=meta.data.UC_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.UC_adult_RRST_349_B1$`median(umi)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_UC = cbind(data_cor_adult_RRST_349_B1_UC,data.frame(median.score_genetic = (cor(x=meta.data.UC_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.UC_adult_RRST_349_B1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_UC$trait <- "UC"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_RRST_349_B1_IBD = data.frame(median.genes = (cor(x=meta.data.IBD_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.IBD_adult_RRST_349_B1$`median(genes)`,method = "spearman")))
data_cor_adult_RRST_349_B1_IBD = cbind(data_cor_adult_RRST_349_B1_IBD,data.frame(median.umi = (cor(x=meta.data.IBD_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.IBD_adult_RRST_349_B1$`median(umi)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_IBD = cbind(data_cor_adult_RRST_349_B1_IBD,data.frame(median.score_genetic = (cor(x=meta.data.IBD_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.IBD_adult_RRST_349_B1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_IBD$trait <- "IBD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_RRST_349_B1_LID = data.frame(median.genes = (cor(x=meta.data.LID_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.LID_adult_RRST_349_B1$`median(genes)`,method = "spearman")))
data_cor_adult_RRST_349_B1_LID = cbind(data_cor_adult_RRST_349_B1_LID,data.frame(median.umi = (cor(x=meta.data.LID_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.LID_adult_RRST_349_B1$`median(umi)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_LID = cbind(data_cor_adult_RRST_349_B1_LID,data.frame(median.score_genetic = (cor(x=meta.data.LID_adult_RRST_349_B1$`-log10(p.val_genetic)`,y=meta.data.LID_adult_RRST_349_B1$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_RRST_349_B1_LID$trait <- "LID"

data_cor_adult_RRST_349_B1_all <- rbind(data_cor_adult_RRST_349_B1_CD,data_cor_adult_RRST_349_B1_IBD)
data_cor_adult_RRST_349_B1_all <- rbind(data_cor_adult_RRST_349_B1_all,data_cor_adult_RRST_349_B1_LID)
data_cor_adult_RRST_349_B1_all <- rbind(data_cor_adult_RRST_349_B1_all,data_cor_adult_RRST_349_B1_UC)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_adult_RRST_349_B1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_adult_RRST_349_B1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_adult_RRST_349_B1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# mouse_healing_ctrl
```{r}
# mouse_healing_ctrl
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_healing_ctrl_CD = data.frame(median.genes = (cor(x=meta.data.CD_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.CD_mouse_healing_ctrl$`median(genes)`,method = "spearman")))
data_cor_mouse_healing_ctrl_CD = cbind(data_cor_mouse_healing_ctrl_CD,data.frame(median.umi = (cor(x=meta.data.CD_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.CD_mouse_healing_ctrl$`median(umi)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_CD = cbind(data_cor_mouse_healing_ctrl_CD,data.frame(median.score_genetic = (cor(x=meta.data.CD_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.CD_mouse_healing_ctrl$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_CD$trait <- "CD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_healing_ctrl_UC = data.frame(median.genes = (cor(x=meta.data.UC_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.UC_mouse_healing_ctrl$`median(genes)`,method = "spearman")))
data_cor_mouse_healing_ctrl_UC = cbind(data_cor_mouse_healing_ctrl_UC,data.frame(median.umi = (cor(x=meta.data.UC_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.UC_mouse_healing_ctrl$`median(umi)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_UC = cbind(data_cor_mouse_healing_ctrl_UC,data.frame(median.score_genetic = (cor(x=meta.data.UC_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.UC_mouse_healing_ctrl$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_UC$trait <- "UC"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_healing_ctrl_IBD = data.frame(median.genes = (cor(x=meta.data.IBD_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.IBD_mouse_healing_ctrl$`median(genes)`,method = "spearman")))
data_cor_mouse_healing_ctrl_IBD = cbind(data_cor_mouse_healing_ctrl_IBD,data.frame(median.umi = (cor(x=meta.data.IBD_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.IBD_mouse_healing_ctrl$`median(umi)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_IBD = cbind(data_cor_mouse_healing_ctrl_IBD,data.frame(median.score_genetic = (cor(x=meta.data.IBD_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.IBD_mouse_healing_ctrl$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_IBD$trait <- "IBD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_healing_ctrl_LID = data.frame(median.genes = (cor(x=meta.data.LID_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.LID_mouse_healing_ctrl$`median(genes)`,method = "spearman")))
data_cor_mouse_healing_ctrl_LID = cbind(data_cor_mouse_healing_ctrl_LID,data.frame(median.umi = (cor(x=meta.data.LID_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.LID_mouse_healing_ctrl$`median(umi)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_LID = cbind(data_cor_mouse_healing_ctrl_LID,data.frame(median.score_genetic = (cor(x=meta.data.LID_mouse_healing_ctrl$`-log10(p.val_genetic)`,y=meta.data.LID_mouse_healing_ctrl$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_healing_ctrl_LID$trait <- "LID"

data_cor_mouse_healing_ctrl_all <- rbind(data_cor_mouse_healing_ctrl_CD,data_cor_mouse_healing_ctrl_IBD)
data_cor_mouse_healing_ctrl_all <- rbind(data_cor_mouse_healing_ctrl_all,data_cor_mouse_healing_ctrl_LID)
data_cor_mouse_healing_ctrl_all <- rbind(data_cor_mouse_healing_ctrl_all,data_cor_mouse_healing_ctrl_UC)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_healing_ctrl_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_healing_ctrl_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_healing_ctrl_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# pcw12_HFGA_A8
```{r}
# pcw12_HFGA_A8
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw12_HFGA_A8_CD = data.frame(median.genes = (cor(x=meta.data.CD_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.CD_pcw12_HFGA_A8$`median(genes)`,method = "spearman")))
data_cor_pcw12_HFGA_A8_CD = cbind(data_cor_pcw12_HFGA_A8_CD,data.frame(median.umi = (cor(x=meta.data.CD_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.CD_pcw12_HFGA_A8$`median(umi)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_CD = cbind(data_cor_pcw12_HFGA_A8_CD,data.frame(median.score_genetic = (cor(x=meta.data.CD_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.CD_pcw12_HFGA_A8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_CD$trait <- "CD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw12_HFGA_A8_UC = data.frame(median.genes = (cor(x=meta.data.UC_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.UC_pcw12_HFGA_A8$`median(genes)`,method = "spearman")))
data_cor_pcw12_HFGA_A8_UC = cbind(data_cor_pcw12_HFGA_A8_UC,data.frame(median.umi = (cor(x=meta.data.UC_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.UC_pcw12_HFGA_A8$`median(umi)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_UC = cbind(data_cor_pcw12_HFGA_A8_UC,data.frame(median.score_genetic = (cor(x=meta.data.UC_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.UC_pcw12_HFGA_A8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_UC$trait <- "UC"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw12_HFGA_A8_IBD = data.frame(median.genes = (cor(x=meta.data.IBD_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.IBD_pcw12_HFGA_A8$`median(genes)`,method = "spearman")))
data_cor_pcw12_HFGA_A8_IBD = cbind(data_cor_pcw12_HFGA_A8_IBD,data.frame(median.umi = (cor(x=meta.data.IBD_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.IBD_pcw12_HFGA_A8$`median(umi)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_IBD = cbind(data_cor_pcw12_HFGA_A8_IBD,data.frame(median.score_genetic = (cor(x=meta.data.IBD_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.IBD_pcw12_HFGA_A8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_IBD$trait <- "IBD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw12_HFGA_A8_LID = data.frame(median.genes = (cor(x=meta.data.LID_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.LID_pcw12_HFGA_A8$`median(genes)`,method = "spearman")))
data_cor_pcw12_HFGA_A8_LID = cbind(data_cor_pcw12_HFGA_A8_LID,data.frame(median.umi = (cor(x=meta.data.LID_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.LID_pcw12_HFGA_A8$`median(umi)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_LID = cbind(data_cor_pcw12_HFGA_A8_LID,data.frame(median.score_genetic = (cor(x=meta.data.LID_pcw12_HFGA_A8$`-log10(p.val_genetic)`,y=meta.data.LID_pcw12_HFGA_A8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw12_HFGA_A8_LID$trait <- "LID"

data_cor_pcw12_HFGA_A8_all <- rbind(data_cor_pcw12_HFGA_A8_CD,data_cor_pcw12_HFGA_A8_IBD)
data_cor_pcw12_HFGA_A8_all <- rbind(data_cor_pcw12_HFGA_A8_all,data_cor_pcw12_HFGA_A8_LID)
data_cor_pcw12_HFGA_A8_all <- rbind(data_cor_pcw12_HFGA_A8_all,data_cor_pcw12_HFGA_A8_UC)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_pcw12_HFGA_A8_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_pcw12_HFGA_A8_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_pcw12_HFGA_A8_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# pcw19_HFGA_A4
```{r}
# pcw19_HFGA_A4
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw19_HFGA_A4_CD = data.frame(median.genes = (cor(x=meta.data.CD_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.CD_pcw19_HFGA_A4$`median(genes)`,method = "spearman")))
data_cor_pcw19_HFGA_A4_CD = cbind(data_cor_pcw19_HFGA_A4_CD,data.frame(median.umi = (cor(x=meta.data.CD_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.CD_pcw19_HFGA_A4$`median(umi)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_CD = cbind(data_cor_pcw19_HFGA_A4_CD,data.frame(median.score_genetic = (cor(x=meta.data.CD_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.CD_pcw19_HFGA_A4$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_CD$trait <- "CD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw19_HFGA_A4_UC = data.frame(median.genes = (cor(x=meta.data.UC_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.UC_pcw19_HFGA_A4$`median(genes)`,method = "spearman")))
data_cor_pcw19_HFGA_A4_UC = cbind(data_cor_pcw19_HFGA_A4_UC,data.frame(median.umi = (cor(x=meta.data.UC_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.UC_pcw19_HFGA_A4$`median(umi)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_UC = cbind(data_cor_pcw19_HFGA_A4_UC,data.frame(median.score_genetic = (cor(x=meta.data.UC_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.UC_pcw19_HFGA_A4$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_UC$trait <- "UC"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw19_HFGA_A4_IBD = data.frame(median.genes = (cor(x=meta.data.IBD_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.IBD_pcw19_HFGA_A4$`median(genes)`,method = "spearman")))
data_cor_pcw19_HFGA_A4_IBD = cbind(data_cor_pcw19_HFGA_A4_IBD,data.frame(median.umi = (cor(x=meta.data.IBD_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.IBD_pcw19_HFGA_A4$`median(umi)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_IBD = cbind(data_cor_pcw19_HFGA_A4_IBD,data.frame(median.score_genetic = (cor(x=meta.data.IBD_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.IBD_pcw19_HFGA_A4$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_IBD$trait <- "IBD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw19_HFGA_A4_LID = data.frame(median.genes = (cor(x=meta.data.LID_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.LID_pcw19_HFGA_A4$`median(genes)`,method = "spearman")))
data_cor_pcw19_HFGA_A4_LID = cbind(data_cor_pcw19_HFGA_A4_LID,data.frame(median.umi = (cor(x=meta.data.LID_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.LID_pcw19_HFGA_A4$`median(umi)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_LID = cbind(data_cor_pcw19_HFGA_A4_LID,data.frame(median.score_genetic = (cor(x=meta.data.LID_pcw19_HFGA_A4$`-log10(p.val_genetic)`,y=meta.data.LID_pcw19_HFGA_A4$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw19_HFGA_A4_LID$trait <- "LID"

data_cor_pcw19_HFGA_A4_all <- rbind(data_cor_pcw19_HFGA_A4_CD,data_cor_pcw19_HFGA_A4_IBD)
data_cor_pcw19_HFGA_A4_all <- rbind(data_cor_pcw19_HFGA_A4_all,data_cor_pcw19_HFGA_A4_LID)
data_cor_pcw19_HFGA_A4_all <- rbind(data_cor_pcw19_HFGA_A4_all,data_cor_pcw19_HFGA_A4_UC)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_pcw19_HFGA_A4_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_pcw19_HFGA_A4_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_pcw19_HFGA_A4_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# Merge all histogram
```{r}
data_cor_adult_HFGA_A1_all$dataset <- "adult_HFGA_A1"
data_cor_adult_HFGA_A1_all
data_cor_adult_RRST_349_B1_all$dataset <- "adult_RRST_349_B1"
data_cor_adult_RRST_349_B1_all
data_cor_mouse_healing_ctrl_all$dataset <- "mouse_healing_ctrl"
data_cor_mouse_healing_ctrl_all
data_cor_pcw12_HFGA_A8_all$dataset <- "pcw12_HFGA_A8"
data_cor_pcw12_HFGA_A8_all
data_cor_pcw19_HFGA_A4_all$dataset <- "pcw19_HFGA_A4"
data_cor_pcw19_HFGA_A4_all

#Merge
data_cor_intestine_all_traits <- rbind(data_cor_adult_HFGA_A1_all,data_cor_adult_RRST_349_B1_all)
data_cor_intestine_all_traits <- rbind(data_cor_intestine_all_traits,data_cor_mouse_healing_ctrl_all)
data_cor_intestine_all_traits <- rbind(data_cor_intestine_all_traits,data_cor_pcw12_HFGA_A8_all)
data_cor_intestine_all_traits <- rbind(data_cor_intestine_all_traits,data_cor_pcw19_HFGA_A4_all)

#Save data
#saveRDS(data_cor_intestine_all_traits, file = "pval_data_cor_organs_all_traits_spearman/data_cor_intestine_all_traits_spearman.rds")
#write.matrix(data_cor_intestine_all_traits,file="pval_data_cor_organs_all_traits_spearman/data_cor_intestine_all_traits_spearman.csv",sep = ";")

```


## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_intestine_all_traits, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```
Median Genes
```{r}
# basic histogram
data_cor_intestine_all_traits_no_na <- na.exclude(data_cor_intestine_all_traits)

p <- ggplot(data_cor_intestine_all_traits_no_na, aes(x=median.genes)) + 
  geom_histogram(bins = (length(data_cor_intestine_all_traits_no_na$median.genes))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.genes)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_intestine_all_traits_no_na$median.genes)
print("mean")
mean(data_cor_intestine_all_traits_no_na$median.genes)
print("standard deviation")
sd(data_cor_intestine_all_traits_no_na$median.genes)
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_intestine_all_traits, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median UMI
```{r}
# basic histogram
data_cor_intestine_all_traits_no_na <- na.exclude(data_cor_intestine_all_traits)

p <- ggplot(data_cor_intestine_all_traits_no_na, aes(x=median.umi)) + 
  geom_histogram(bins = (length(data_cor_intestine_all_traits_no_na$median.umi))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.umi)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_intestine_all_traits_no_na$median.umi)
print("mean")
mean(data_cor_intestine_all_traits_no_na$median.umi)
print("standard deviation")
sd(data_cor_intestine_all_traits_no_na$median.umi)
```


## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_intestine_all_traits, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median score genetic
```{r}
# basic histogram
data_cor_intestine_all_traits_no_na <- na.exclude(data_cor_intestine_all_traits)

p <- ggplot(data_cor_intestine_all_traits_no_na, aes(x=median.score_genetic)) + 
  geom_histogram(bins = (length(data_cor_intestine_all_traits_no_na$median.score_genetic))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.score_genetic)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_intestine_all_traits_no_na$median.score_genetic)
print("mean")
mean(data_cor_intestine_all_traits_no_na$median.score_genetic)
print("standard deviation")
sd(data_cor_intestine_all_traits_no_na$median.score_genetic)
```


# Merge all Boxplot

## median.genes
```{r}
# Boxplot

data_cor_intestine_all_traits %>%
  ggplot( aes(x=trait, y=median.genes, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")

```


## median.umi
```{r}
# Boxplot

data_cor_intestine_all_traits %>%
  ggplot( aes(x=trait, y=median.umi, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```


## median.score_genetic
```{r}
# Boxplot

data_cor_intestine_all_traits %>%
  ggplot( aes(x=trait, y=median.score_genetic, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```

# Notes
```{r}
sessionInfo()
```

