---
title: "pval_distribution_all_cor_[liver_datasets]_spearman"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Script for calculating Spearman correlations across spatial structures for selected tissue-trait pairs from all genetically associated genes. Comparing p-values and a) genes or b) UMIs. This was done for data generated for each organ and the output summarized in organ specific files. See folder named 'pval_data_cor_organs_all_traits_spearman' for all such files.

# Load libraries
```{r}
library(scales)
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(MASS)
```



# Load data
Load distribution data:
```{r}

# LIVER

##human_JBO0018
meta.data.CAD_human_JBO0018 <- readRDS(file = "Liver/human_JBO0018/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_human_JBO0018 <- readRDS(file = "Liver/human_JBO0018/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.CIRR_human_JBO0018 <- readRDS(file = "Liver/human_JBO0018/p_value_distribution/pval.distribution_CIRR_all_genes.RDS")

meta.data.NAFLD_human_JBO0018 <- readRDS(file = "Liver/human_JBO0018/p_value_distribution/pval.distribution_NAFLD_all_genes.RDS")

meta.data.CHOL_human_JBO0018 <- readRDS(file = "Liver/human_JBO0018/p_value_distribution/pval.distribution_CHOL_all_genes.RDS")

meta.data.LDL_human_JBO0018 <- readRDS(file = "Liver/human_JBO0018/p_value_distribution/pval.distribution_LDL_all_genes.RDS")

meta.data.LD_human_JBO0018 <- readRDS(file = "Liver/human_JBO0018/p_value_distribution/pval.distribution_LD_all_genes.RDS")


##human_JBO0022
meta.data.CAD_human_JBO0022 <- readRDS(file = "Liver/human_JBO0022/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_human_JBO0022 <- readRDS(file = "Liver/human_JBO0022/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.CIRR_human_JBO0022 <- readRDS(file = "Liver/human_JBO0022/p_value_distribution/pval.distribution_CIRR_all_genes.RDS")

meta.data.NAFLD_human_JBO0022 <- readRDS(file = "Liver/human_JBO0022/p_value_distribution/pval.distribution_NAFLD_all_genes.RDS")

meta.data.CHOL_human_JBO0022 <- readRDS(file = "Liver/human_JBO0022/p_value_distribution/pval.distribution_CHOL_all_genes.RDS")

meta.data.LDL_human_JBO0022 <- readRDS(file = "Liver/human_JBO0022/p_value_distribution/pval.distribution_LDL_all_genes.RDS")

meta.data.LD_human_JBO0022 <- readRDS(file = "Liver/human_JBO0022/p_value_distribution/pval.distribution_LD_all_genes.RDS")


##mouse_JBO002
meta.data.CAD_mouse_JBO002 <- readRDS(file = "Liver/mouse_JBO002/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_mouse_JBO002 <- readRDS(file = "Liver/mouse_JBO002/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.CIRR_mouse_JBO002 <- readRDS(file = "Liver/mouse_JBO002/p_value_distribution/pval.distribution_CIRR_all_genes.RDS")

meta.data.NAFLD_mouse_JBO002 <- readRDS(file = "Liver/mouse_JBO002/p_value_distribution/pval.distribution_NAFLD_all_genes.RDS")

meta.data.CHOL_mouse_JBO002 <- readRDS(file = "Liver/mouse_JBO002/p_value_distribution/pval.distribution_CHOL_all_genes.RDS")

meta.data.LDL_mouse_JBO002 <- readRDS(file = "Liver/mouse_JBO002/p_value_distribution/pval.distribution_LDL_all_genes.RDS")

meta.data.LD_mouse_JBO002 <- readRDS(file = "Liver/mouse_JBO002/p_value_distribution/pval.distribution_LD_all_genes.RDS")


##mouse_zonation_C1
meta.data.CAD_mouse_zonation_C1 <- readRDS(file = "Liver/mouse_zonation_C1/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_mouse_zonation_C1 <- readRDS(file = "Liver/mouse_zonation_C1/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.CIRR_mouse_zonation_C1 <- readRDS(file = "Liver/mouse_zonation_C1/p_value_distribution/pval.distribution_CIRR_all_genes.RDS")

meta.data.NAFLD_mouse_zonation_C1 <- readRDS(file = "Liver/mouse_zonation_C1/p_value_distribution/pval.distribution_NAFLD_all_genes.RDS")

meta.data.CHOL_mouse_zonation_C1 <- readRDS(file = "Liver/mouse_zonation_C1/p_value_distribution/pval.distribution_CHOL_all_genes.RDS")

meta.data.LDL_mouse_zonation_C1 <- readRDS(file = "Liver/mouse_zonation_C1/p_value_distribution/pval.distribution_LDL_all_genes.RDS")

meta.data.LD_mouse_zonation_C1 <- readRDS(file = "Liver/mouse_zonation_C1/p_value_distribution/pval.distribution_LD_all_genes.RDS")


```



# human_JBO0018
```{r}
# human_JBO0018
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0018_MI = data.frame(median.genes = (cor(x=meta.data.MI_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.MI_human_JBO0018$`median(genes)`,method = "spearman")))
data_cor_human_JBO0018_MI = cbind(data_cor_human_JBO0018_MI,data.frame(median.umi = (cor(x=meta.data.MI_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.MI_human_JBO0018$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0018_MI = cbind(data_cor_human_JBO0018_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.MI_human_JBO0018$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0018_MI$trait <- "MI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0018_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CAD_human_JBO0018$`median(genes)`,method = "spearman")))
data_cor_human_JBO0018_CAD = cbind(data_cor_human_JBO0018_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CAD_human_JBO0018$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0018_CAD = cbind(data_cor_human_JBO0018_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CAD_human_JBO0018$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0018_CAD$trait <- "CAD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0018_CIRR = data.frame(median.genes = (cor(x=meta.data.CIRR_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CIRR_human_JBO0018$`median(genes)`,method = "spearman")))
data_cor_human_JBO0018_CIRR = cbind(data_cor_human_JBO0018_CIRR,data.frame(median.umi = (cor(x=meta.data.CIRR_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CIRR_human_JBO0018$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0018_CIRR = cbind(data_cor_human_JBO0018_CIRR,data.frame(median.score_genetic = (cor(x=meta.data.CIRR_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CIRR_human_JBO0018$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0018_CIRR$trait <- "CIRR"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0018_NAFLD = data.frame(median.genes = (cor(x=meta.data.NAFLD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.NAFLD_human_JBO0018$`median(genes)`,method = "spearman")))
data_cor_human_JBO0018_NAFLD = cbind(data_cor_human_JBO0018_NAFLD,data.frame(median.umi = (cor(x=meta.data.NAFLD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.NAFLD_human_JBO0018$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0018_NAFLD = cbind(data_cor_human_JBO0018_NAFLD,data.frame(median.score_genetic = (cor(x=meta.data.NAFLD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.NAFLD_human_JBO0018$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0018_NAFLD$trait <- "NAFLD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0018_CHOL = data.frame(median.genes = (cor(x=meta.data.CHOL_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CHOL_human_JBO0018$`median(genes)`,method = "spearman")))
data_cor_human_JBO0018_CHOL = cbind(data_cor_human_JBO0018_CHOL,data.frame(median.umi = (cor(x=meta.data.CHOL_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CHOL_human_JBO0018$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0018_CHOL = cbind(data_cor_human_JBO0018_CHOL,data.frame(median.score_genetic = (cor(x=meta.data.CHOL_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.CHOL_human_JBO0018$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0018_CHOL$trait <- "CHOL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0018_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.LDL_human_JBO0018$`median(genes)`,method = "spearman")))
data_cor_human_JBO0018_LDL = cbind(data_cor_human_JBO0018_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.LDL_human_JBO0018$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0018_LDL = cbind(data_cor_human_JBO0018_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.LDL_human_JBO0018$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0018_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0018_LD = data.frame(median.genes = (cor(x=meta.data.LD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.LD_human_JBO0018$`median(genes)`,method = "spearman")))
data_cor_human_JBO0018_LD = cbind(data_cor_human_JBO0018_LD,data.frame(median.umi = (cor(x=meta.data.LD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.LD_human_JBO0018$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0018_LD = cbind(data_cor_human_JBO0018_LD,data.frame(median.score_genetic = (cor(x=meta.data.LD_human_JBO0018$`-log10(p.val_genetic)`,y=meta.data.LD_human_JBO0018$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0018_LD$trait <- "LD"

data_cor_human_JBO0018_all <- rbind(data_cor_human_JBO0018_CHOL,data_cor_human_JBO0018_CIRR)
data_cor_human_JBO0018_all <- rbind(data_cor_human_JBO0018_all,data_cor_human_JBO0018_LD)
data_cor_human_JBO0018_all <- rbind(data_cor_human_JBO0018_all,data_cor_human_JBO0018_LDL)
data_cor_human_JBO0018_all <- rbind(data_cor_human_JBO0018_all,data_cor_human_JBO0018_NAFLD)
data_cor_human_JBO0018_all <- rbind(data_cor_human_JBO0018_all,data_cor_human_JBO0018_CAD)
data_cor_human_JBO0018_all <- rbind(data_cor_human_JBO0018_all,data_cor_human_JBO0018_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_human_JBO0018_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_human_JBO0018_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_human_JBO0018_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# human_JBO0022
```{r}
# human_JBO0022
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0022_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CAD_human_JBO0022$`median(genes)`,method = "spearman")))
data_cor_human_JBO0022_CAD = cbind(data_cor_human_JBO0022_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CAD_human_JBO0022$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0022_CAD = cbind(data_cor_human_JBO0022_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CAD_human_JBO0022$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0022_CAD$trait <- "CAD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0022_MI = data.frame(median.genes = (cor(x=meta.data.MI_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.MI_human_JBO0022$`median(genes)`,method = "spearman")))
data_cor_human_JBO0022_MI = cbind(data_cor_human_JBO0022_MI,data.frame(median.umi = (cor(x=meta.data.MI_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.MI_human_JBO0022$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0022_MI = cbind(data_cor_human_JBO0022_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.MI_human_JBO0022$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0022_MI$trait <- "MI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0022_CIRR = data.frame(median.genes = (cor(x=meta.data.CIRR_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CIRR_human_JBO0022$`median(genes)`,method = "spearman")))
data_cor_human_JBO0022_CIRR = cbind(data_cor_human_JBO0022_CIRR,data.frame(median.umi = (cor(x=meta.data.CIRR_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CIRR_human_JBO0022$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0022_CIRR = cbind(data_cor_human_JBO0022_CIRR,data.frame(median.score_genetic = (cor(x=meta.data.CIRR_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CIRR_human_JBO0022$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0022_CIRR$trait <- "CIRR"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0022_NAFLD = data.frame(median.genes = (cor(x=meta.data.NAFLD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.NAFLD_human_JBO0022$`median(genes)`,method = "spearman")))
data_cor_human_JBO0022_NAFLD = cbind(data_cor_human_JBO0022_NAFLD,data.frame(median.umi = (cor(x=meta.data.NAFLD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.NAFLD_human_JBO0022$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0022_NAFLD = cbind(data_cor_human_JBO0022_NAFLD,data.frame(median.score_genetic = (cor(x=meta.data.NAFLD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.NAFLD_human_JBO0022$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0022_NAFLD$trait <- "NAFLD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0022_CHOL = data.frame(median.genes = (cor(x=meta.data.CHOL_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CHOL_human_JBO0022$`median(genes)`,method = "spearman")))
data_cor_human_JBO0022_CHOL = cbind(data_cor_human_JBO0022_CHOL,data.frame(median.umi = (cor(x=meta.data.CHOL_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CHOL_human_JBO0022$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0022_CHOL = cbind(data_cor_human_JBO0022_CHOL,data.frame(median.score_genetic = (cor(x=meta.data.CHOL_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.CHOL_human_JBO0022$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0022_CHOL$trait <- "CHOL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0022_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.LDL_human_JBO0022$`median(genes)`,method = "spearman")))
data_cor_human_JBO0022_LDL = cbind(data_cor_human_JBO0022_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.LDL_human_JBO0022$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0022_LDL = cbind(data_cor_human_JBO0022_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.LDL_human_JBO0022$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0022_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_human_JBO0022_LD = data.frame(median.genes = (cor(x=meta.data.LD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.LD_human_JBO0022$`median(genes)`,method = "spearman")))
data_cor_human_JBO0022_LD = cbind(data_cor_human_JBO0022_LD,data.frame(median.umi = (cor(x=meta.data.LD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.LD_human_JBO0022$`median(umi)`,method = "spearman"))))
data_cor_human_JBO0022_LD = cbind(data_cor_human_JBO0022_LD,data.frame(median.score_genetic = (cor(x=meta.data.LD_human_JBO0022$`-log10(p.val_genetic)`,y=meta.data.LD_human_JBO0022$`median(score_genetic)`,method = "spearman"))))
data_cor_human_JBO0022_LD$trait <- "LD"

data_cor_human_JBO0022_all <- rbind(data_cor_human_JBO0022_CHOL,data_cor_human_JBO0022_CIRR)
data_cor_human_JBO0022_all <- rbind(data_cor_human_JBO0022_all,data_cor_human_JBO0022_LD)
data_cor_human_JBO0022_all <- rbind(data_cor_human_JBO0022_all,data_cor_human_JBO0022_LDL)
data_cor_human_JBO0022_all <- rbind(data_cor_human_JBO0022_all,data_cor_human_JBO0022_NAFLD)
data_cor_human_JBO0022_all <- rbind(data_cor_human_JBO0022_all,data_cor_human_JBO0022_CAD)
data_cor_human_JBO0022_all <- rbind(data_cor_human_JBO0022_all,data_cor_human_JBO0022_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_human_JBO0022_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_human_JBO0022_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_human_JBO0022_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# mouse_JBO002
```{r}
# mouse_JBO002
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JBO002_MI = data.frame(median.genes = (cor(x=meta.data.MI_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.MI_mouse_JBO002$`median(genes)`,method = "spearman")))
data_cor_mouse_JBO002_MI = cbind(data_cor_mouse_JBO002_MI,data.frame(median.umi = (cor(x=meta.data.MI_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.MI_mouse_JBO002$`median(umi)`,method = "spearman"))))
data_cor_mouse_JBO002_MI = cbind(data_cor_mouse_JBO002_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.MI_mouse_JBO002$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JBO002_MI$trait <- "MI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JBO002_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CAD_mouse_JBO002$`median(genes)`,method = "spearman")))
data_cor_mouse_JBO002_CAD = cbind(data_cor_mouse_JBO002_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CAD_mouse_JBO002$`median(umi)`,method = "spearman"))))
data_cor_mouse_JBO002_CAD = cbind(data_cor_mouse_JBO002_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CAD_mouse_JBO002$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JBO002_CAD$trait <- "CAD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JBO002_CIRR = data.frame(median.genes = (cor(x=meta.data.CIRR_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CIRR_mouse_JBO002$`median(genes)`,method = "spearman")))
data_cor_mouse_JBO002_CIRR = cbind(data_cor_mouse_JBO002_CIRR,data.frame(median.umi = (cor(x=meta.data.CIRR_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CIRR_mouse_JBO002$`median(umi)`,method = "spearman"))))
data_cor_mouse_JBO002_CIRR = cbind(data_cor_mouse_JBO002_CIRR,data.frame(median.score_genetic = (cor(x=meta.data.CIRR_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CIRR_mouse_JBO002$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JBO002_CIRR$trait <- "CIRR"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JBO002_NAFLD = data.frame(median.genes = (cor(x=meta.data.NAFLD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.NAFLD_mouse_JBO002$`median(genes)`,method = "spearman")))
data_cor_mouse_JBO002_NAFLD = cbind(data_cor_mouse_JBO002_NAFLD,data.frame(median.umi = (cor(x=meta.data.NAFLD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.NAFLD_mouse_JBO002$`median(umi)`,method = "spearman"))))
data_cor_mouse_JBO002_NAFLD = cbind(data_cor_mouse_JBO002_NAFLD,data.frame(median.score_genetic = (cor(x=meta.data.NAFLD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.NAFLD_mouse_JBO002$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JBO002_NAFLD$trait <- "NAFLD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JBO002_CHOL = data.frame(median.genes = (cor(x=meta.data.CHOL_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CHOL_mouse_JBO002$`median(genes)`,method = "spearman")))
data_cor_mouse_JBO002_CHOL = cbind(data_cor_mouse_JBO002_CHOL,data.frame(median.umi = (cor(x=meta.data.CHOL_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CHOL_mouse_JBO002$`median(umi)`,method = "spearman"))))
data_cor_mouse_JBO002_CHOL = cbind(data_cor_mouse_JBO002_CHOL,data.frame(median.score_genetic = (cor(x=meta.data.CHOL_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.CHOL_mouse_JBO002$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JBO002_CHOL$trait <- "CHOL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JBO002_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.LDL_mouse_JBO002$`median(genes)`,method = "spearman")))
data_cor_mouse_JBO002_LDL = cbind(data_cor_mouse_JBO002_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.LDL_mouse_JBO002$`median(umi)`,method = "spearman"))))
data_cor_mouse_JBO002_LDL = cbind(data_cor_mouse_JBO002_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.LDL_mouse_JBO002$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JBO002_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_JBO002_LD = data.frame(median.genes = (cor(x=meta.data.LD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.LD_mouse_JBO002$`median(genes)`,method = "spearman")))
data_cor_mouse_JBO002_LD = cbind(data_cor_mouse_JBO002_LD,data.frame(median.umi = (cor(x=meta.data.LD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.LD_mouse_JBO002$`median(umi)`,method = "spearman"))))
data_cor_mouse_JBO002_LD = cbind(data_cor_mouse_JBO002_LD,data.frame(median.score_genetic = (cor(x=meta.data.LD_mouse_JBO002$`-log10(p.val_genetic)`,y=meta.data.LD_mouse_JBO002$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_JBO002_LD$trait <- "LD"

data_cor_mouse_JBO002_all <- rbind(data_cor_mouse_JBO002_CHOL,data_cor_mouse_JBO002_CIRR)
data_cor_mouse_JBO002_all <- rbind(data_cor_mouse_JBO002_all,data_cor_mouse_JBO002_LD)
data_cor_mouse_JBO002_all <- rbind(data_cor_mouse_JBO002_all,data_cor_mouse_JBO002_LDL)
data_cor_mouse_JBO002_all <- rbind(data_cor_mouse_JBO002_all,data_cor_mouse_JBO002_NAFLD)
data_cor_mouse_JBO002_all <- rbind(data_cor_mouse_JBO002_all,data_cor_mouse_JBO002_CAD)
data_cor_mouse_JBO002_all <- rbind(data_cor_mouse_JBO002_all,data_cor_mouse_JBO002_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_JBO002_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_JBO002_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_JBO002_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# mouse_zonation_C1
```{r}
# mouse_zonation_C1
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_zonation_C1_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CAD_mouse_zonation_C1$`median(genes)`,method = "spearman")))
data_cor_mouse_zonation_C1_CAD = cbind(data_cor_mouse_zonation_C1_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CAD_mouse_zonation_C1$`median(umi)`,method = "spearman"))))
data_cor_mouse_zonation_C1_CAD = cbind(data_cor_mouse_zonation_C1_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CAD_mouse_zonation_C1$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_zonation_C1_CAD$trait <- "CAD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_zonation_C1_MI = data.frame(median.genes = (cor(x=meta.data.MI_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.MI_mouse_zonation_C1$`median(genes)`,method = "spearman")))
data_cor_mouse_zonation_C1_MI = cbind(data_cor_mouse_zonation_C1_MI,data.frame(median.umi = (cor(x=meta.data.MI_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.MI_mouse_zonation_C1$`median(umi)`,method = "spearman"))))
data_cor_mouse_zonation_C1_MI = cbind(data_cor_mouse_zonation_C1_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.MI_mouse_zonation_C1$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_zonation_C1_MI$trait <- "MI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_zonation_C1_CIRR = data.frame(median.genes = (cor(x=meta.data.CIRR_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CIRR_mouse_zonation_C1$`median(genes)`,method = "spearman")))
data_cor_mouse_zonation_C1_CIRR = cbind(data_cor_mouse_zonation_C1_CIRR,data.frame(median.umi = (cor(x=meta.data.CIRR_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CIRR_mouse_zonation_C1$`median(umi)`,method = "spearman"))))
data_cor_mouse_zonation_C1_CIRR = cbind(data_cor_mouse_zonation_C1_CIRR,data.frame(median.score_genetic = (cor(x=meta.data.CIRR_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CIRR_mouse_zonation_C1$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_zonation_C1_CIRR$trait <- "CIRR"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_zonation_C1_NAFLD = data.frame(median.genes = (cor(x=meta.data.NAFLD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.NAFLD_mouse_zonation_C1$`median(genes)`,method = "spearman")))
data_cor_mouse_zonation_C1_NAFLD = cbind(data_cor_mouse_zonation_C1_NAFLD,data.frame(median.umi = (cor(x=meta.data.NAFLD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.NAFLD_mouse_zonation_C1$`median(umi)`,method = "spearman"))))
data_cor_mouse_zonation_C1_NAFLD = cbind(data_cor_mouse_zonation_C1_NAFLD,data.frame(median.score_genetic = (cor(x=meta.data.NAFLD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.NAFLD_mouse_zonation_C1$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_zonation_C1_NAFLD$trait <- "NAFLD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_zonation_C1_CHOL = data.frame(median.genes = (cor(x=meta.data.CHOL_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CHOL_mouse_zonation_C1$`median(genes)`,method = "spearman")))
data_cor_mouse_zonation_C1_CHOL = cbind(data_cor_mouse_zonation_C1_CHOL,data.frame(median.umi = (cor(x=meta.data.CHOL_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CHOL_mouse_zonation_C1$`median(umi)`,method = "spearman"))))
data_cor_mouse_zonation_C1_CHOL = cbind(data_cor_mouse_zonation_C1_CHOL,data.frame(median.score_genetic = (cor(x=meta.data.CHOL_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.CHOL_mouse_zonation_C1$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_zonation_C1_CHOL$trait <- "CHOL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_zonation_C1_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.LDL_mouse_zonation_C1$`median(genes)`,method = "spearman")))
data_cor_mouse_zonation_C1_LDL = cbind(data_cor_mouse_zonation_C1_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.LDL_mouse_zonation_C1$`median(umi)`,method = "spearman"))))
data_cor_mouse_zonation_C1_LDL = cbind(data_cor_mouse_zonation_C1_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.LDL_mouse_zonation_C1$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_zonation_C1_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_mouse_zonation_C1_LD = data.frame(median.genes = (cor(x=meta.data.LD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.LD_mouse_zonation_C1$`median(genes)`,method = "spearman")))
data_cor_mouse_zonation_C1_LD = cbind(data_cor_mouse_zonation_C1_LD,data.frame(median.umi = (cor(x=meta.data.LD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.LD_mouse_zonation_C1$`median(umi)`,method = "spearman"))))
data_cor_mouse_zonation_C1_LD = cbind(data_cor_mouse_zonation_C1_LD,data.frame(median.score_genetic = (cor(x=meta.data.LD_mouse_zonation_C1$`-log10(p.val_genetic)`,y=meta.data.LD_mouse_zonation_C1$`median(score_genetic)`,method = "spearman"))))
data_cor_mouse_zonation_C1_LD$trait <- "LD"

data_cor_mouse_zonation_C1_all <- rbind(data_cor_mouse_zonation_C1_CHOL,data_cor_mouse_zonation_C1_CIRR)
data_cor_mouse_zonation_C1_all <- rbind(data_cor_mouse_zonation_C1_all,data_cor_mouse_zonation_C1_LD)
data_cor_mouse_zonation_C1_all <- rbind(data_cor_mouse_zonation_C1_all,data_cor_mouse_zonation_C1_LDL)
data_cor_mouse_zonation_C1_all <- rbind(data_cor_mouse_zonation_C1_all,data_cor_mouse_zonation_C1_NAFLD)
data_cor_mouse_zonation_C1_all <- rbind(data_cor_mouse_zonation_C1_all,data_cor_mouse_zonation_C1_CAD)
data_cor_mouse_zonation_C1_all <- rbind(data_cor_mouse_zonation_C1_all,data_cor_mouse_zonation_C1_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_zonation_C1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_zonation_C1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_mouse_zonation_C1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# Merge all histogram
```{r}
data_cor_human_JBO0018_all$dataset <- "human_JBO0018"
data_cor_human_JBO0018_all
data_cor_human_JBO0022_all$dataset <- "human_JBO0022"
data_cor_human_JBO0022_all
data_cor_mouse_JBO002_all$dataset <- "mouse_JBO002"
data_cor_mouse_JBO002_all
data_cor_mouse_zonation_C1_all$dataset <- "mouse_zonation_C1"
data_cor_mouse_zonation_C1_all

#Merge
data_cor_liver_all_traits <- rbind(data_cor_human_JBO0018_all,data_cor_human_JBO0022_all)
data_cor_liver_all_traits <- rbind(data_cor_liver_all_traits,data_cor_mouse_JBO002_all)
data_cor_liver_all_traits <- rbind(data_cor_liver_all_traits,data_cor_mouse_zonation_C1_all)

#Save data
#saveRDS(data_cor_liver_all_traits, file = "pval_data_cor_organs_all_traits_spearman/data_cor_liver_all_traits_spearman.rds")
#write.matrix(data_cor_liver_all_traits,file="pval_data_cor_organs_all_traits_spearman/data_cor_liver_all_traits_spearman.csv",sep = ";")

```


## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_liver_all_traits, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```
Median Genes
```{r}
# basic histogram
data_cor_liver_all_traits_no_na <- na.exclude(data_cor_liver_all_traits)

p <- ggplot(data_cor_liver_all_traits_no_na, aes(x=median.genes)) + 
  geom_histogram(bins = (length(data_cor_liver_all_traits_no_na$median.genes))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.genes)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_liver_all_traits_no_na$median.genes)
print("mean")
mean(data_cor_liver_all_traits_no_na$median.genes)
print("standard deviation")
sd(data_cor_liver_all_traits_no_na$median.genes)
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_liver_all_traits, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median UMI
```{r}
# basic histogram
data_cor_liver_all_traits_no_na <- na.exclude(data_cor_liver_all_traits)

p <- ggplot(data_cor_liver_all_traits_no_na, aes(x=median.umi)) + 
  geom_histogram(bins = (length(data_cor_liver_all_traits_no_na$median.umi))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.umi)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_liver_all_traits_no_na$median.umi)
print("mean")
mean(data_cor_liver_all_traits_no_na$median.umi)
print("standard deviation")
sd(data_cor_liver_all_traits_no_na$median.umi)
```


## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_liver_all_traits, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median score genetic
```{r}
# basic histogram
data_cor_liver_all_traits_no_na <- na.exclude(data_cor_liver_all_traits)

p <- ggplot(data_cor_liver_all_traits_no_na, aes(x=median.score_genetic)) + 
  geom_histogram(bins = (length(data_cor_liver_all_traits_no_na$median.score_genetic))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.score_genetic)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_liver_all_traits_no_na$median.score_genetic)
print("mean")
mean(data_cor_liver_all_traits_no_na$median.score_genetic)
print("standard deviation")
sd(data_cor_liver_all_traits_no_na$median.score_genetic)
```


# Merge all Boxplot

## median.genes
```{r}
# Boxplot

data_cor_liver_all_traits %>%
  ggplot( aes(x=trait, y=median.genes, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")

```


## median.umi
```{r}
# Boxplot

data_cor_liver_all_traits %>%
  ggplot( aes(x=trait, y=median.umi, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```


## median.score_genetic
```{r}
# Boxplot

data_cor_liver_all_traits %>%
  ggplot( aes(x=trait, y=median.score_genetic, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```

# Notes
```{r}
sessionInfo()
```

