---
title: "pval_distribution_all_cor_[brain_datasets]_spearman"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Script for calculating Spearman correlations across spatial structures for selected tissue-trait pairs from all genetically associated genes. Comparing p-values and a) genes or b) UMIs. This was done for data generated for each organ and the output summarized in organ specific files. See folder named 'pval_data_cor_organs_all_traits_spearman' for all such files.

# Load libraries
```{r}
library(scales)
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(MASS)
```



# Load data
Load distribution data:
```{r}

# BRAIN

##_Human_brain_DLPFC_151673
meta.data.ADHD_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_ADHD_all_genes.RDS")

meta.data.AHD_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.ALZ_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_ALZ_all_genes.RDS")

meta.data.ASD_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_ASD_all_genes.RDS")

meta.data.BIP_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_BIP_all_genes.RDS")

meta.data.EPI_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_EPI_all_genes.RDS")

meta.data.INS_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_INS_all_genes.RDS")

meta.data.MDD_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_MDD_all_genes.RDS")

meta.data.MS_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_MS_all_genes.RDS")

meta.data.PAR_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_PAR_all_genes.RDS")

meta.data.SCZ_Human_brain_DLPFC_151673 <- readRDS(file = "Brain/Human_brain_DLPFC_151673/p_value_distribution/pval.distribution_SCZ_all_genes.RDS")


##_Human_brain_DLPFC_151509
meta.data.ADHD_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_ADHD_all_genes.RDS")

meta.data.AHD_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.ALZ_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_ALZ_all_genes.RDS")

meta.data.ASD_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_ASD_all_genes.RDS")

meta.data.BIP_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_BIP_all_genes.RDS")

meta.data.EPI_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_EPI_all_genes.RDS")

meta.data.INS_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_INS_all_genes.RDS")

meta.data.MDD_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_MDD_all_genes.RDS")

meta.data.MS_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_MS_all_genes.RDS")

meta.data.PAR_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_PAR_all_genes.RDS")

meta.data.SCZ_Human_brain_DLPFC_151509 <- readRDS(file = "Brain/Human_brain_DLPFC_151509/p_value_distribution/pval.distribution_SCZ_all_genes.RDS")


##_Cell2location_Visium_mouse_brain_coronal_1
meta.data.ADHD_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_ADHD_all_genes.RDS")

meta.data.AHD_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.ALZ_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_ALZ_all_genes.RDS")

meta.data.ASD_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_ASD_all_genes.RDS")

meta.data.BIP_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_BIP_all_genes.RDS")

meta.data.EPI_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_EPI_all_genes.RDS")

meta.data.INS_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_INS_all_genes.RDS")

meta.data.MDD_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_MDD_all_genes.RDS")

meta.data.MS_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_MS_all_genes.RDS")

meta.data.PAR_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_PAR_all_genes.RDS")

meta.data.SCZ_Cell2location_Visium_mouse_brain_coronal_1 <- readRDS(file = "Brain/Cell2location_Visium_mouse_brain_coronal_1/p_value_distribution/pval.distribution_SCZ_all_genes.RDS")


##_10X_Visium_mouse_brain_coronal
meta.data.ADHD_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_ADHD_all_genes.RDS")

meta.data.AHD_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.ALZ_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_ALZ_all_genes.RDS")

meta.data.ASD_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_ASD_all_genes.RDS")

meta.data.BIP_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_BIP_all_genes.RDS")

meta.data.EPI_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_EPI_all_genes.RDS")

meta.data.INS_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_INS_all_genes.RDS")

meta.data.MDD_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_MDD_all_genes.RDS")

meta.data.MS_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_MS_all_genes.RDS")

meta.data.PAR_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_PAR_all_genes.RDS")

meta.data.SCZ_10X_Visium_mouse_brain_coronal <- readRDS(file = "Brain/10X_Visium_mouse_brain_coronal/p_value_distribution/pval.distribution_SCZ_all_genes.RDS")


```



# Human_brain_DLPFC_151673
```{r}
# Human_brain_DLPFC_151673

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_ADHD = data.frame(median.genes = (cor(x=meta.data.ADHD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ADHD_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_ADHD = cbind(data_cor_Human_brain_DLPFC_151673_ADHD,data.frame(median.umi = (cor(x=meta.data.ADHD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ADHD_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ADHD = cbind(data_cor_Human_brain_DLPFC_151673_ADHD,data.frame(median.score_genetic = (cor(x=meta.data.ADHD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ADHD_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ADHD$trait <- "ADHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.AHD_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_AHD = cbind(data_cor_Human_brain_DLPFC_151673_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.AHD_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_AHD = cbind(data_cor_Human_brain_DLPFC_151673_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.AHD_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ALS_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_ALS = cbind(data_cor_Human_brain_DLPFC_151673_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ALS_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ALS = cbind(data_cor_Human_brain_DLPFC_151673_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ALS_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ALS$trait <- "ALS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_ALZ = data.frame(median.genes = (cor(x=meta.data.ALZ_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ALZ_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_ALZ = cbind(data_cor_Human_brain_DLPFC_151673_ALZ,data.frame(median.umi = (cor(x=meta.data.ALZ_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ALZ_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ALZ = cbind(data_cor_Human_brain_DLPFC_151673_ALZ,data.frame(median.score_genetic = (cor(x=meta.data.ALZ_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ALZ_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ALZ$trait <- "ALZ"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_ASD = data.frame(median.genes = (cor(x=meta.data.ASD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ASD_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_ASD = cbind(data_cor_Human_brain_DLPFC_151673_ASD,data.frame(median.umi = (cor(x=meta.data.ASD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ASD_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ASD = cbind(data_cor_Human_brain_DLPFC_151673_ASD,data.frame(median.score_genetic = (cor(x=meta.data.ASD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.ASD_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_ASD$trait <- "ASD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_BIP = data.frame(median.genes = (cor(x=meta.data.BIP_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.BIP_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_BIP = cbind(data_cor_Human_brain_DLPFC_151673_BIP,data.frame(median.umi = (cor(x=meta.data.BIP_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.BIP_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_BIP = cbind(data_cor_Human_brain_DLPFC_151673_BIP,data.frame(median.score_genetic = (cor(x=meta.data.BIP_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.BIP_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_BIP$trait <- "BIP"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_EPI = data.frame(median.genes = (cor(x=meta.data.EPI_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.EPI_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_EPI = cbind(data_cor_Human_brain_DLPFC_151673_EPI,data.frame(median.umi = (cor(x=meta.data.EPI_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.EPI_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_EPI = cbind(data_cor_Human_brain_DLPFC_151673_EPI,data.frame(median.score_genetic = (cor(x=meta.data.EPI_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.EPI_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_EPI$trait <- "EPI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_INS = data.frame(median.genes = (cor(x=meta.data.INS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.INS_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_INS = cbind(data_cor_Human_brain_DLPFC_151673_INS,data.frame(median.umi = (cor(x=meta.data.INS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.INS_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_INS = cbind(data_cor_Human_brain_DLPFC_151673_INS,data.frame(median.score_genetic = (cor(x=meta.data.INS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.INS_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_INS$trait <- "INS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_MDD = data.frame(median.genes = (cor(x=meta.data.MDD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.MDD_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_MDD = cbind(data_cor_Human_brain_DLPFC_151673_MDD,data.frame(median.umi = (cor(x=meta.data.MDD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.MDD_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_MDD = cbind(data_cor_Human_brain_DLPFC_151673_MDD,data.frame(median.score_genetic = (cor(x=meta.data.MDD_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.MDD_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_MDD$trait <- "MDD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_MS = data.frame(median.genes = (cor(x=meta.data.MS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.MS_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_MS = cbind(data_cor_Human_brain_DLPFC_151673_MS,data.frame(median.umi = (cor(x=meta.data.MS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.MS_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_MS = cbind(data_cor_Human_brain_DLPFC_151673_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.MS_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_MS$trait <- "MS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_PAR = data.frame(median.genes = (cor(x=meta.data.PAR_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.PAR_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_PAR = cbind(data_cor_Human_brain_DLPFC_151673_PAR,data.frame(median.umi = (cor(x=meta.data.PAR_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.PAR_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_PAR = cbind(data_cor_Human_brain_DLPFC_151673_PAR,data.frame(median.score_genetic = (cor(x=meta.data.PAR_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.PAR_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_PAR$trait <- "PAR"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151673_SCZ = data.frame(median.genes = (cor(x=meta.data.SCZ_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.SCZ_Human_brain_DLPFC_151673$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151673_SCZ = cbind(data_cor_Human_brain_DLPFC_151673_SCZ,data.frame(median.umi = (cor(x=meta.data.SCZ_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.SCZ_Human_brain_DLPFC_151673$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_SCZ = cbind(data_cor_Human_brain_DLPFC_151673_SCZ,data.frame(median.score_genetic = (cor(x=meta.data.SCZ_Human_brain_DLPFC_151673$`-log10(p.val_genetic)`,y=meta.data.SCZ_Human_brain_DLPFC_151673$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151673_SCZ$trait <- "SCZ"



data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_ADHD,data_cor_Human_brain_DLPFC_151673_AHD)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_ALS)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_ALZ)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_ASD)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_BIP)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_EPI)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_INS)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_MDD)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_MS)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_PAR)
data_cor_Human_brain_DLPFC_151673_all <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151673_SCZ)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_Human_brain_DLPFC_151673_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_Human_brain_DLPFC_151673_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_Human_brain_DLPFC_151673_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# Human_brain_DLPFC_151509
```{r}
# Human_brain_DLPFC_151509

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_ADHD = data.frame(median.genes = (cor(x=meta.data.ADHD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ADHD_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_ADHD = cbind(data_cor_Human_brain_DLPFC_151509_ADHD,data.frame(median.umi = (cor(x=meta.data.ADHD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ADHD_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ADHD = cbind(data_cor_Human_brain_DLPFC_151509_ADHD,data.frame(median.score_genetic = (cor(x=meta.data.ADHD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ADHD_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ADHD$trait <- "ADHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.AHD_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_AHD = cbind(data_cor_Human_brain_DLPFC_151509_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.AHD_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_AHD = cbind(data_cor_Human_brain_DLPFC_151509_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.AHD_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ALS_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_ALS = cbind(data_cor_Human_brain_DLPFC_151509_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ALS_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ALS = cbind(data_cor_Human_brain_DLPFC_151509_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ALS_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ALS$trait <- "ALS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_ALZ = data.frame(median.genes = (cor(x=meta.data.ALZ_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ALZ_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_ALZ = cbind(data_cor_Human_brain_DLPFC_151509_ALZ,data.frame(median.umi = (cor(x=meta.data.ALZ_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ALZ_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ALZ = cbind(data_cor_Human_brain_DLPFC_151509_ALZ,data.frame(median.score_genetic = (cor(x=meta.data.ALZ_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ALZ_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ALZ$trait <- "ALZ"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_ASD = data.frame(median.genes = (cor(x=meta.data.ASD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ASD_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_ASD = cbind(data_cor_Human_brain_DLPFC_151509_ASD,data.frame(median.umi = (cor(x=meta.data.ASD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ASD_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ASD = cbind(data_cor_Human_brain_DLPFC_151509_ASD,data.frame(median.score_genetic = (cor(x=meta.data.ASD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.ASD_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_ASD$trait <- "ASD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_BIP = data.frame(median.genes = (cor(x=meta.data.BIP_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.BIP_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_BIP = cbind(data_cor_Human_brain_DLPFC_151509_BIP,data.frame(median.umi = (cor(x=meta.data.BIP_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.BIP_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_BIP = cbind(data_cor_Human_brain_DLPFC_151509_BIP,data.frame(median.score_genetic = (cor(x=meta.data.BIP_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.BIP_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_BIP$trait <- "BIP"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_EPI = data.frame(median.genes = (cor(x=meta.data.EPI_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.EPI_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_EPI = cbind(data_cor_Human_brain_DLPFC_151509_EPI,data.frame(median.umi = (cor(x=meta.data.EPI_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.EPI_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_EPI = cbind(data_cor_Human_brain_DLPFC_151509_EPI,data.frame(median.score_genetic = (cor(x=meta.data.EPI_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.EPI_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_EPI$trait <- "EPI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_INS = data.frame(median.genes = (cor(x=meta.data.INS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.INS_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_INS = cbind(data_cor_Human_brain_DLPFC_151509_INS,data.frame(median.umi = (cor(x=meta.data.INS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.INS_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_INS = cbind(data_cor_Human_brain_DLPFC_151509_INS,data.frame(median.score_genetic = (cor(x=meta.data.INS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.INS_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_INS$trait <- "INS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_MDD = data.frame(median.genes = (cor(x=meta.data.MDD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.MDD_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_MDD = cbind(data_cor_Human_brain_DLPFC_151509_MDD,data.frame(median.umi = (cor(x=meta.data.MDD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.MDD_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_MDD = cbind(data_cor_Human_brain_DLPFC_151509_MDD,data.frame(median.score_genetic = (cor(x=meta.data.MDD_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.MDD_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_MDD$trait <- "MDD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_MS = data.frame(median.genes = (cor(x=meta.data.MS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.MS_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_MS = cbind(data_cor_Human_brain_DLPFC_151509_MS,data.frame(median.umi = (cor(x=meta.data.MS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.MS_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_MS = cbind(data_cor_Human_brain_DLPFC_151509_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.MS_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_MS$trait <- "MS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_PAR = data.frame(median.genes = (cor(x=meta.data.PAR_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.PAR_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_PAR = cbind(data_cor_Human_brain_DLPFC_151509_PAR,data.frame(median.umi = (cor(x=meta.data.PAR_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.PAR_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_PAR = cbind(data_cor_Human_brain_DLPFC_151509_PAR,data.frame(median.score_genetic = (cor(x=meta.data.PAR_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.PAR_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_PAR$trait <- "PAR"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Human_brain_DLPFC_151509_SCZ = data.frame(median.genes = (cor(x=meta.data.SCZ_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.SCZ_Human_brain_DLPFC_151509$`median(genes)`,method = "spearman")))
data_cor_Human_brain_DLPFC_151509_SCZ = cbind(data_cor_Human_brain_DLPFC_151509_SCZ,data.frame(median.umi = (cor(x=meta.data.SCZ_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.SCZ_Human_brain_DLPFC_151509$`median(umi)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_SCZ = cbind(data_cor_Human_brain_DLPFC_151509_SCZ,data.frame(median.score_genetic = (cor(x=meta.data.SCZ_Human_brain_DLPFC_151509$`-log10(p.val_genetic)`,y=meta.data.SCZ_Human_brain_DLPFC_151509$`median(score_genetic)`,method = "spearman"))))
data_cor_Human_brain_DLPFC_151509_SCZ$trait <- "SCZ"



data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_ADHD,data_cor_Human_brain_DLPFC_151509_AHD)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_ALS)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_ALZ)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_ASD)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_BIP)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_EPI)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_INS)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_MDD)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_MS)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_PAR)
data_cor_Human_brain_DLPFC_151509_all <- rbind(data_cor_Human_brain_DLPFC_151509_all,data_cor_Human_brain_DLPFC_151509_SCZ)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_Human_brain_DLPFC_151509_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_Human_brain_DLPFC_151509_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_Human_brain_DLPFC_151509_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# Cell2location_Visium_mouse_brain_coronal_1
```{r}
# Cell2location_Visium_mouse_brain_coronal_1

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ADHD = data.frame(median.genes = (cor(x=meta.data.ADHD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ADHD_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ADHD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ADHD,data.frame(median.umi = (cor(x=meta.data.ADHD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ADHD_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ADHD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ADHD,data.frame(median.score_genetic = (cor(x=meta.data.ADHD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ADHD_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ADHD$trait <- "ADHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.AHD_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_AHD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.AHD_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_AHD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.AHD_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ALS_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALS = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ALS_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALS = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ALS_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALS$trait <- "ALS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALZ = data.frame(median.genes = (cor(x=meta.data.ALZ_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ALZ_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALZ = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALZ,data.frame(median.umi = (cor(x=meta.data.ALZ_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ALZ_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALZ = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALZ,data.frame(median.score_genetic = (cor(x=meta.data.ALZ_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ALZ_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALZ$trait <- "ALZ"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ASD = data.frame(median.genes = (cor(x=meta.data.ASD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ASD_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ASD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ASD,data.frame(median.umi = (cor(x=meta.data.ASD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ASD_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ASD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ASD,data.frame(median.score_genetic = (cor(x=meta.data.ASD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.ASD_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_ASD$trait <- "ASD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_BIP = data.frame(median.genes = (cor(x=meta.data.BIP_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.BIP_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_BIP = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_BIP,data.frame(median.umi = (cor(x=meta.data.BIP_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.BIP_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_BIP = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_BIP,data.frame(median.score_genetic = (cor(x=meta.data.BIP_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.BIP_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_BIP$trait <- "BIP"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_EPI = data.frame(median.genes = (cor(x=meta.data.EPI_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.EPI_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_EPI = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_EPI,data.frame(median.umi = (cor(x=meta.data.EPI_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.EPI_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_EPI = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_EPI,data.frame(median.score_genetic = (cor(x=meta.data.EPI_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.EPI_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_EPI$trait <- "EPI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_INS = data.frame(median.genes = (cor(x=meta.data.INS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.INS_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_INS = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_INS,data.frame(median.umi = (cor(x=meta.data.INS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.INS_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_INS = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_INS,data.frame(median.score_genetic = (cor(x=meta.data.INS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.INS_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_INS$trait <- "INS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MDD = data.frame(median.genes = (cor(x=meta.data.MDD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.MDD_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MDD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_MDD,data.frame(median.umi = (cor(x=meta.data.MDD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.MDD_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MDD = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_MDD,data.frame(median.score_genetic = (cor(x=meta.data.MDD_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.MDD_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MDD$trait <- "MDD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MS = data.frame(median.genes = (cor(x=meta.data.MS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.MS_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MS = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_MS,data.frame(median.umi = (cor(x=meta.data.MS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.MS_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MS = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.MS_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_MS$trait <- "MS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_PAR = data.frame(median.genes = (cor(x=meta.data.PAR_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.PAR_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_PAR = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_PAR,data.frame(median.umi = (cor(x=meta.data.PAR_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.PAR_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_PAR = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_PAR,data.frame(median.score_genetic = (cor(x=meta.data.PAR_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.PAR_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_PAR$trait <- "PAR"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_SCZ = data.frame(median.genes = (cor(x=meta.data.SCZ_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.SCZ_Cell2location_Visium_mouse_brain_coronal_1$`median(genes)`,method = "spearman")))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_SCZ = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_SCZ,data.frame(median.umi = (cor(x=meta.data.SCZ_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.SCZ_Cell2location_Visium_mouse_brain_coronal_1$`median(umi)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_SCZ = cbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_SCZ,data.frame(median.score_genetic = (cor(x=meta.data.SCZ_Cell2location_Visium_mouse_brain_coronal_1$`-log10(p.val_genetic)`,y=meta.data.SCZ_Cell2location_Visium_mouse_brain_coronal_1$`median(score_genetic)`,method = "spearman"))))
data_cor_Cell2location_Visium_mouse_brain_coronal_1_SCZ$trait <- "SCZ"



data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_ADHD,data_cor_Cell2location_Visium_mouse_brain_coronal_1_AHD)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALS)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_ALZ)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_ASD)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_BIP)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_EPI)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_INS)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_MDD)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_MS)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_PAR)
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all <- rbind(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all,data_cor_Cell2location_Visium_mouse_brain_coronal_1_SCZ)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_Cell2location_Visium_mouse_brain_coronal_1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# 10X_Visium_mouse_brain_coronal
```{r}
# 10X_Visium_mouse_brain_coronal

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_ADHD = data.frame(median.genes = (cor(x=meta.data.ADHD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ADHD_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_ADHD = cbind(data_cor_10X_Visium_mouse_brain_coronal_ADHD,data.frame(median.umi = (cor(x=meta.data.ADHD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ADHD_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ADHD = cbind(data_cor_10X_Visium_mouse_brain_coronal_ADHD,data.frame(median.score_genetic = (cor(x=meta.data.ADHD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ADHD_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ADHD$trait <- "ADHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.AHD_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_AHD = cbind(data_cor_10X_Visium_mouse_brain_coronal_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.AHD_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_AHD = cbind(data_cor_10X_Visium_mouse_brain_coronal_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.AHD_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ALS_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_ALS = cbind(data_cor_10X_Visium_mouse_brain_coronal_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ALS_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ALS = cbind(data_cor_10X_Visium_mouse_brain_coronal_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ALS_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ALS$trait <- "ALS"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_ALZ = data.frame(median.genes = (cor(x=meta.data.ALZ_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ALZ_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_ALZ = cbind(data_cor_10X_Visium_mouse_brain_coronal_ALZ,data.frame(median.umi = (cor(x=meta.data.ALZ_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ALZ_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ALZ = cbind(data_cor_10X_Visium_mouse_brain_coronal_ALZ,data.frame(median.score_genetic = (cor(x=meta.data.ALZ_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ALZ_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ALZ$trait <- "ALZ"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_ASD = data.frame(median.genes = (cor(x=meta.data.ASD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ASD_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_ASD = cbind(data_cor_10X_Visium_mouse_brain_coronal_ASD,data.frame(median.umi = (cor(x=meta.data.ASD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ASD_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ASD = cbind(data_cor_10X_Visium_mouse_brain_coronal_ASD,data.frame(median.score_genetic = (cor(x=meta.data.ASD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.ASD_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_ASD$trait <- "ASD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_BIP = data.frame(median.genes = (cor(x=meta.data.BIP_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.BIP_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_BIP = cbind(data_cor_10X_Visium_mouse_brain_coronal_BIP,data.frame(median.umi = (cor(x=meta.data.BIP_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.BIP_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_BIP = cbind(data_cor_10X_Visium_mouse_brain_coronal_BIP,data.frame(median.score_genetic = (cor(x=meta.data.BIP_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.BIP_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_BIP$trait <- "BIP"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_EPI = data.frame(median.genes = (cor(x=meta.data.EPI_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.EPI_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_EPI = cbind(data_cor_10X_Visium_mouse_brain_coronal_EPI,data.frame(median.umi = (cor(x=meta.data.EPI_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.EPI_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_EPI = cbind(data_cor_10X_Visium_mouse_brain_coronal_EPI,data.frame(median.score_genetic = (cor(x=meta.data.EPI_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.EPI_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_EPI$trait <- "EPI"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_INS = data.frame(median.genes = (cor(x=meta.data.INS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.INS_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_INS = cbind(data_cor_10X_Visium_mouse_brain_coronal_INS,data.frame(median.umi = (cor(x=meta.data.INS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.INS_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_INS = cbind(data_cor_10X_Visium_mouse_brain_coronal_INS,data.frame(median.score_genetic = (cor(x=meta.data.INS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.INS_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_INS$trait <- "INS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_MDD = data.frame(median.genes = (cor(x=meta.data.MDD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.MDD_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_MDD = cbind(data_cor_10X_Visium_mouse_brain_coronal_MDD,data.frame(median.umi = (cor(x=meta.data.MDD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.MDD_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_MDD = cbind(data_cor_10X_Visium_mouse_brain_coronal_MDD,data.frame(median.score_genetic = (cor(x=meta.data.MDD_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.MDD_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_MDD$trait <- "MDD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_MS = data.frame(median.genes = (cor(x=meta.data.MS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.MS_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_MS = cbind(data_cor_10X_Visium_mouse_brain_coronal_MS,data.frame(median.umi = (cor(x=meta.data.MS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.MS_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_MS = cbind(data_cor_10X_Visium_mouse_brain_coronal_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.MS_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_MS$trait <- "MS"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_PAR = data.frame(median.genes = (cor(x=meta.data.PAR_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.PAR_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_PAR = cbind(data_cor_10X_Visium_mouse_brain_coronal_PAR,data.frame(median.umi = (cor(x=meta.data.PAR_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.PAR_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_PAR = cbind(data_cor_10X_Visium_mouse_brain_coronal_PAR,data.frame(median.score_genetic = (cor(x=meta.data.PAR_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.PAR_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_PAR$trait <- "PAR"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_10X_Visium_mouse_brain_coronal_SCZ = data.frame(median.genes = (cor(x=meta.data.SCZ_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.SCZ_10X_Visium_mouse_brain_coronal$`median(genes)`,method = "spearman")))
data_cor_10X_Visium_mouse_brain_coronal_SCZ = cbind(data_cor_10X_Visium_mouse_brain_coronal_SCZ,data.frame(median.umi = (cor(x=meta.data.SCZ_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.SCZ_10X_Visium_mouse_brain_coronal$`median(umi)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_SCZ = cbind(data_cor_10X_Visium_mouse_brain_coronal_SCZ,data.frame(median.score_genetic = (cor(x=meta.data.SCZ_10X_Visium_mouse_brain_coronal$`-log10(p.val_genetic)`,y=meta.data.SCZ_10X_Visium_mouse_brain_coronal$`median(score_genetic)`,method = "spearman"))))
data_cor_10X_Visium_mouse_brain_coronal_SCZ$trait <- "SCZ"



data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_ADHD,data_cor_10X_Visium_mouse_brain_coronal_AHD)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_ALS)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_ALZ)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_ASD)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_BIP)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_EPI)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_INS)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_MDD)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_MS)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_PAR)
data_cor_10X_Visium_mouse_brain_coronal_all <- rbind(data_cor_10X_Visium_mouse_brain_coronal_all,data_cor_10X_Visium_mouse_brain_coronal_SCZ)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_10X_Visium_mouse_brain_coronal_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_10X_Visium_mouse_brain_coronal_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_10X_Visium_mouse_brain_coronal_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# Merge all histogram
```{r}

data_cor_Human_brain_DLPFC_151673_all$dataset <- "Human_brain_DLPFC_151673"
data_cor_Human_brain_DLPFC_151673_all
data_cor_Human_brain_DLPFC_151509_all$dataset <- "Human_brain_DLPFC_151509"
data_cor_Human_brain_DLPFC_151509_all
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all$dataset <- "Cell2location_Visium_mouse_brain_coronal_1"
data_cor_Cell2location_Visium_mouse_brain_coronal_1_all
data_cor_10X_Visium_mouse_brain_coronal_all$dataset <- "10X_Visium_mouse_brain_coronal"
data_cor_10X_Visium_mouse_brain_coronal_all


#Merge
data_cor_brain_all_traits <- rbind(data_cor_Human_brain_DLPFC_151673_all,data_cor_Human_brain_DLPFC_151509_all)
data_cor_brain_all_traits <- rbind(data_cor_brain_all_traits,data_cor_Cell2location_Visium_mouse_brain_coronal_1_all)
data_cor_brain_all_traits <- rbind(data_cor_brain_all_traits,data_cor_10X_Visium_mouse_brain_coronal_all)

#Save data
#saveRDS(data_cor_brain_all_traits, file = "pval_data_cor_organs_all_traits_spearman/data_cor_brain_all_traits_spearman.rds")
#write.matrix(data_cor_brain_all_traits,file="pval_data_cor_organs_all_traits_spearman/data_cor_brain_all_traits_spearman.csv",sep = ";")

```


## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_brain_all_traits, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```
Median Genes
```{r}
# basic histogram
data_cor_brain_all_traits_no_na <- na.exclude(data_cor_brain_all_traits)

p <- ggplot(data_cor_brain_all_traits_no_na, aes(x=median.genes)) + 
  geom_histogram(bins = (length(data_cor_brain_all_traits_no_na$median.genes))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.genes)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_brain_all_traits_no_na$median.genes)
print("mean")
mean(data_cor_brain_all_traits_no_na$median.genes)
print("standard deviation")
sd(data_cor_brain_all_traits_no_na$median.genes)
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_brain_all_traits, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median UMI
```{r}
# basic histogram
data_cor_brain_all_traits_no_na <- na.exclude(data_cor_brain_all_traits)

p <- ggplot(data_cor_brain_all_traits_no_na, aes(x=median.umi)) + 
  geom_histogram(bins = (length(data_cor_brain_all_traits_no_na$median.umi))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.umi)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_brain_all_traits_no_na$median.umi)
print("mean")
mean(data_cor_brain_all_traits_no_na$median.umi)
print("standard deviation")
sd(data_cor_brain_all_traits_no_na$median.umi)
```


## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_brain_all_traits, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median score genetic
```{r}
# basic histogram
data_cor_brain_all_traits_no_na <- na.exclude(data_cor_brain_all_traits)

p <- ggplot(data_cor_brain_all_traits_no_na, aes(x=median.score_genetic)) + 
  geom_histogram(bins = (length(data_cor_brain_all_traits_no_na$median.score_genetic))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.score_genetic)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_brain_all_traits_no_na$median.score_genetic)
print("mean")
mean(data_cor_brain_all_traits_no_na$median.score_genetic)
print("standard deviation")
sd(data_cor_brain_all_traits_no_na$median.score_genetic)
```


# Merge all Boxplot

## median.genes
```{r}
# Boxplot

data_cor_brain_all_traits %>%
  ggplot( aes(x=trait, y=median.genes, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")

```


## median.umi
```{r}
# Boxplot

data_cor_brain_all_traits %>%
  ggplot( aes(x=trait, y=median.umi, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```


## median.score_genetic
```{r}
# Boxplot

data_cor_brain_all_traits %>%
  ggplot( aes(x=trait, y=median.score_genetic, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```

# Notes
```{r}
sessionInfo()
```

