---
title: "pval_distribution_all_cor_[heart_datasets]_spearman"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Script for calculating Spearman correlations across spatial structures for selected tissue-trait pairs from all genetically associated genes. Comparing p-values and a) genes or b) UMIs. This was done for data generated for each organ and the output summarized in organ specific files. See folder named 'pval_data_cor_organs_all_traits_spearman' for all such files.


# Load libraries
```{r}
library(scales)
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(MASS)
```



# Load data
Load distribution data:
```{r}

# HEART

##adult_ACH003
meta.data.CHD_adult_ACH003 <- readRDS(file = "Heart/adult_ACH003/p_value_distribution/pval.distribution_CHD_all_genes.RDS")

meta.data.CAD_adult_ACH003 <- readRDS(file = "Heart/adult_ACH003/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_adult_ACH003 <- readRDS(file = "Heart/adult_ACH003/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.LDL_adult_ACH003 <- readRDS(file = "Heart/adult_ACH003/p_value_distribution/pval.distribution_LDL_all_genes.RDS")


##adult_ACH004
meta.data.CHD_adult_ACH004 <- readRDS(file = "Heart/adult_ACH004/p_value_distribution/pval.distribution_CHD_all_genes.RDS")

meta.data.CAD_adult_ACH004 <- readRDS(file = "Heart/adult_ACH004/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_adult_ACH004 <- readRDS(file = "Heart/adult_ACH004/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.LDL_adult_ACH004 <- readRDS(file = "Heart/adult_ACH004/p_value_distribution/pval.distribution_LDL_all_genes.RDS")


#_pcw6.5_nr8
meta.data.CHD_pcw6.5_nr8 <- readRDS(file = "Heart/pcw6.5_nr8/p_value_distribution/pval.distribution_CHD_all_genes.RDS")

meta.data.CAD_pcw6.5_nr8 <- readRDS(file = "Heart/pcw6.5_nr8/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_pcw6.5_nr8 <- readRDS(file = "Heart/pcw6.5_nr8/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.LDL_pcw6.5_nr8 <- readRDS(file = "Heart/pcw6.5_nr8/p_value_distribution/pval.distribution_LDL_all_genes.RDS")

#_pcw9_nr16
meta.data.CHD_pcw9_nr16 <- readRDS(file = "Heart/pcw9_nr16/p_value_distribution/pval.distribution_CHD_all_genes.RDS")

meta.data.CAD_pcw9_nr16 <- readRDS(file = "Heart/pcw9_nr16/p_value_distribution/pval.distribution_CAD_all_genes.RDS")

meta.data.MI_pcw9_nr16 <- readRDS(file = "Heart/pcw9_nr16/p_value_distribution/pval.distribution_MI_all_genes.RDS")

meta.data.LDL_pcw9_nr16 <- readRDS(file = "Heart/pcw9_nr16/p_value_distribution/pval.distribution_LDL_all_genes.RDS")

```



# adult_ACH003
```{r}
# adult_ACH003
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH003_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.CAD_adult_ACH003$`median(genes)`,method = "spearman")))
data_cor_adult_ACH003_CAD = cbind(data_cor_adult_ACH003_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.CAD_adult_ACH003$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH003_CAD = cbind(data_cor_adult_ACH003_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.CAD_adult_ACH003$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH003_CAD$trait <- "CAD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH003_CHD = data.frame(median.genes = (cor(x=meta.data.CHD_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.CHD_adult_ACH003$`median(genes)`,method = "spearman")))
data_cor_adult_ACH003_CHD = cbind(data_cor_adult_ACH003_CHD,data.frame(median.umi = (cor(x=meta.data.CHD_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.CHD_adult_ACH003$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH003_CHD = cbind(data_cor_adult_ACH003_CHD,data.frame(median.score_genetic = (cor(x=meta.data.CHD_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.CHD_adult_ACH003$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH003_CHD$trait <- "CHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH003_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.LDL_adult_ACH003$`median(genes)`,method = "spearman")))
data_cor_adult_ACH003_LDL = cbind(data_cor_adult_ACH003_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.LDL_adult_ACH003$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH003_LDL = cbind(data_cor_adult_ACH003_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.LDL_adult_ACH003$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH003_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH003_MI = data.frame(median.genes = (cor(x=meta.data.MI_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.MI_adult_ACH003$`median(genes)`,method = "spearman")))
data_cor_adult_ACH003_MI = cbind(data_cor_adult_ACH003_MI,data.frame(median.umi = (cor(x=meta.data.MI_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.MI_adult_ACH003$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH003_MI = cbind(data_cor_adult_ACH003_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_adult_ACH003$`-log10(p.val_genetic)`,y=meta.data.MI_adult_ACH003$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH003_MI$trait <- "MI"

data_cor_adult_ACH003_all <- rbind(data_cor_adult_ACH003_CAD,data_cor_adult_ACH003_CHD)
data_cor_adult_ACH003_all <- rbind(data_cor_adult_ACH003_all,data_cor_adult_ACH003_LDL)
data_cor_adult_ACH003_all <- rbind(data_cor_adult_ACH003_all,data_cor_adult_ACH003_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_adult_ACH003_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_adult_ACH003_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_adult_ACH003_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# adult_ACH004
```{r}
# adult_ACH004
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH004_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.CAD_adult_ACH004$`median(genes)`,method = "spearman")))
data_cor_adult_ACH004_CAD = cbind(data_cor_adult_ACH004_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.CAD_adult_ACH004$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH004_CAD = cbind(data_cor_adult_ACH004_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.CAD_adult_ACH004$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH004_CAD$trait <- "CAD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH004_CHD = data.frame(median.genes = (cor(x=meta.data.CHD_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.CHD_adult_ACH004$`median(genes)`,method = "spearman")))
data_cor_adult_ACH004_CHD = cbind(data_cor_adult_ACH004_CHD,data.frame(median.umi = (cor(x=meta.data.CHD_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.CHD_adult_ACH004$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH004_CHD = cbind(data_cor_adult_ACH004_CHD,data.frame(median.score_genetic = (cor(x=meta.data.CHD_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.CHD_adult_ACH004$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH004_CHD$trait <- "CHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH004_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.LDL_adult_ACH004$`median(genes)`,method = "spearman")))
data_cor_adult_ACH004_LDL = cbind(data_cor_adult_ACH004_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.LDL_adult_ACH004$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH004_LDL = cbind(data_cor_adult_ACH004_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.LDL_adult_ACH004$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH004_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_adult_ACH004_MI = data.frame(median.genes = (cor(x=meta.data.MI_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.MI_adult_ACH004$`median(genes)`,method = "spearman")))
data_cor_adult_ACH004_MI = cbind(data_cor_adult_ACH004_MI,data.frame(median.umi = (cor(x=meta.data.MI_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.MI_adult_ACH004$`median(umi)`,method = "spearman"))))
data_cor_adult_ACH004_MI = cbind(data_cor_adult_ACH004_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_adult_ACH004$`-log10(p.val_genetic)`,y=meta.data.MI_adult_ACH004$`median(score_genetic)`,method = "spearman"))))
data_cor_adult_ACH004_MI$trait <- "MI"

data_cor_adult_ACH004_all <- rbind(data_cor_adult_ACH004_CAD,data_cor_adult_ACH004_CHD)
data_cor_adult_ACH004_all <- rbind(data_cor_adult_ACH004_all,data_cor_adult_ACH004_LDL)
data_cor_adult_ACH004_all <- rbind(data_cor_adult_ACH004_all,data_cor_adult_ACH004_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_adult_ACH004_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_adult_ACH004_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_adult_ACH004_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# pcw9_nr16
```{r}
# pcw9_nr16
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw9_nr16_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.CAD_pcw9_nr16$`median(genes)`,method = "spearman")))
data_cor_pcw9_nr16_CAD = cbind(data_cor_pcw9_nr16_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.CAD_pcw9_nr16$`median(umi)`,method = "spearman"))))
data_cor_pcw9_nr16_CAD = cbind(data_cor_pcw9_nr16_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.CAD_pcw9_nr16$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw9_nr16_CAD$trait <- "CAD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw9_nr16_CHD = data.frame(median.genes = (cor(x=meta.data.CHD_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.CHD_pcw9_nr16$`median(genes)`,method = "spearman")))
data_cor_pcw9_nr16_CHD = cbind(data_cor_pcw9_nr16_CHD,data.frame(median.umi = (cor(x=meta.data.CHD_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.CHD_pcw9_nr16$`median(umi)`,method = "spearman"))))
data_cor_pcw9_nr16_CHD = cbind(data_cor_pcw9_nr16_CHD,data.frame(median.score_genetic = (cor(x=meta.data.CHD_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.CHD_pcw9_nr16$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw9_nr16_CHD$trait <- "CHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw9_nr16_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.LDL_pcw9_nr16$`median(genes)`,method = "spearman")))
data_cor_pcw9_nr16_LDL = cbind(data_cor_pcw9_nr16_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.LDL_pcw9_nr16$`median(umi)`,method = "spearman"))))
data_cor_pcw9_nr16_LDL = cbind(data_cor_pcw9_nr16_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.LDL_pcw9_nr16$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw9_nr16_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw9_nr16_MI = data.frame(median.genes = (cor(x=meta.data.MI_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.MI_pcw9_nr16$`median(genes)`,method = "spearman")))
data_cor_pcw9_nr16_MI = cbind(data_cor_pcw9_nr16_MI,data.frame(median.umi = (cor(x=meta.data.MI_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.MI_pcw9_nr16$`median(umi)`,method = "spearman"))))
data_cor_pcw9_nr16_MI = cbind(data_cor_pcw9_nr16_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_pcw9_nr16$`-log10(p.val_genetic)`,y=meta.data.MI_pcw9_nr16$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw9_nr16_MI$trait <- "MI"

data_cor_pcw9_nr16_all <- rbind(data_cor_pcw9_nr16_CAD,data_cor_pcw9_nr16_CHD)
data_cor_pcw9_nr16_all <- rbind(data_cor_pcw9_nr16_all,data_cor_pcw9_nr16_LDL)
data_cor_pcw9_nr16_all <- rbind(data_cor_pcw9_nr16_all,data_cor_pcw9_nr16_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_pcw9_nr16_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_pcw9_nr16_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_pcw9_nr16_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# pcw6.5_nr8
```{r}
# pcw6.5_nr8
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw6.5_nr8_CAD = data.frame(median.genes = (cor(x=meta.data.CAD_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.CAD_pcw6.5_nr8$`median(genes)`,method = "spearman")))
data_cor_pcw6.5_nr8_CAD = cbind(data_cor_pcw6.5_nr8_CAD,data.frame(median.umi = (cor(x=meta.data.CAD_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.CAD_pcw6.5_nr8$`median(umi)`,method = "spearman"))))
data_cor_pcw6.5_nr8_CAD = cbind(data_cor_pcw6.5_nr8_CAD,data.frame(median.score_genetic = (cor(x=meta.data.CAD_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.CAD_pcw6.5_nr8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw6.5_nr8_CAD$trait <- "CAD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw6.5_nr8_CHD = data.frame(median.genes = (cor(x=meta.data.CHD_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.CHD_pcw6.5_nr8$`median(genes)`,method = "spearman")))
data_cor_pcw6.5_nr8_CHD = cbind(data_cor_pcw6.5_nr8_CHD,data.frame(median.umi = (cor(x=meta.data.CHD_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.CHD_pcw6.5_nr8$`median(umi)`,method = "spearman"))))
data_cor_pcw6.5_nr8_CHD = cbind(data_cor_pcw6.5_nr8_CHD,data.frame(median.score_genetic = (cor(x=meta.data.CHD_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.CHD_pcw6.5_nr8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw6.5_nr8_CHD$trait <- "CHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw6.5_nr8_LDL = data.frame(median.genes = (cor(x=meta.data.LDL_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.LDL_pcw6.5_nr8$`median(genes)`,method = "spearman")))
data_cor_pcw6.5_nr8_LDL = cbind(data_cor_pcw6.5_nr8_LDL,data.frame(median.umi = (cor(x=meta.data.LDL_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.LDL_pcw6.5_nr8$`median(umi)`,method = "spearman"))))
data_cor_pcw6.5_nr8_LDL = cbind(data_cor_pcw6.5_nr8_LDL,data.frame(median.score_genetic = (cor(x=meta.data.LDL_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.LDL_pcw6.5_nr8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw6.5_nr8_LDL$trait <- "LDL"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_pcw6.5_nr8_MI = data.frame(median.genes = (cor(x=meta.data.MI_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.MI_pcw6.5_nr8$`median(genes)`,method = "spearman")))
data_cor_pcw6.5_nr8_MI = cbind(data_cor_pcw6.5_nr8_MI,data.frame(median.umi = (cor(x=meta.data.MI_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.MI_pcw6.5_nr8$`median(umi)`,method = "spearman"))))
data_cor_pcw6.5_nr8_MI = cbind(data_cor_pcw6.5_nr8_MI,data.frame(median.score_genetic = (cor(x=meta.data.MI_pcw6.5_nr8$`-log10(p.val_genetic)`,y=meta.data.MI_pcw6.5_nr8$`median(score_genetic)`,method = "spearman"))))
data_cor_pcw6.5_nr8_MI$trait <- "MI"

data_cor_pcw6.5_nr8_all <- rbind(data_cor_pcw6.5_nr8_CAD,data_cor_pcw6.5_nr8_CHD)
data_cor_pcw6.5_nr8_all <- rbind(data_cor_pcw6.5_nr8_all,data_cor_pcw6.5_nr8_LDL)
data_cor_pcw6.5_nr8_all <- rbind(data_cor_pcw6.5_nr8_all,data_cor_pcw6.5_nr8_MI)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_pcw6.5_nr8_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_pcw6.5_nr8_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_pcw6.5_nr8_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# Merge all histogram
```{r}
data_cor_adult_ACH003_all$dataset <- "adult_ACH003"
data_cor_adult_ACH003_all
data_cor_adult_ACH004_all$dataset <- "adult_ACH004"
data_cor_adult_ACH004_all
data_cor_pcw9_nr16_all$dataset <- "pcw9_nr16"
data_cor_pcw9_nr16_all
data_cor_pcw6.5_nr8_all$dataset <- "pcw6.5_nr8"
data_cor_pcw6.5_nr8_all

#Merge
data_cor_heart_all_traits <- rbind(data_cor_adult_ACH003_all,data_cor_adult_ACH004_all)
data_cor_heart_all_traits <- rbind(data_cor_heart_all_traits,data_cor_pcw9_nr16_all)
data_cor_heart_all_traits <- rbind(data_cor_heart_all_traits,data_cor_pcw6.5_nr8_all)

#Save data
#saveRDS(data_cor_heart_all_traits, file = "pval_data_cor_organs_all_traits_spearman/data_cor_heart_all_traits_spearman.rds")
#write.matrix(data_cor_heart_all_traits,file="pval_data_cor_organs_all_traits_spearman/data_cor_heart_all_traits_spearman.csv",sep = ";")

```


## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_heart_all_traits, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```
Median Genes
```{r}
# basic histogram
data_cor_heart_all_traits_no_na <- na.exclude(data_cor_heart_all_traits)

p <- ggplot(data_cor_heart_all_traits_no_na, aes(x=median.genes)) + 
  geom_histogram(bins = (length(data_cor_heart_all_traits_no_na$median.genes))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.genes)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_heart_all_traits_no_na$median.genes)
print("mean")
mean(data_cor_heart_all_traits_no_na$median.genes)
print("standard deviation")
sd(data_cor_heart_all_traits_no_na$median.genes)
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_heart_all_traits, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median UMI
```{r}
# basic histogram
data_cor_heart_all_traits_no_na <- na.exclude(data_cor_heart_all_traits)

p <- ggplot(data_cor_heart_all_traits_no_na, aes(x=median.umi)) + 
  geom_histogram(bins = (length(data_cor_heart_all_traits_no_na$median.umi))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.umi)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_heart_all_traits_no_na$median.umi)
print("mean")
mean(data_cor_heart_all_traits_no_na$median.umi)
print("standard deviation")
sd(data_cor_heart_all_traits_no_na$median.umi)
```


## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_heart_all_traits, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median score genetic
```{r}
# basic histogram
data_cor_heart_all_traits_no_na <- na.exclude(data_cor_heart_all_traits)

p <- ggplot(data_cor_heart_all_traits_no_na, aes(x=median.score_genetic)) + 
  geom_histogram(bins = (length(data_cor_heart_all_traits_no_na$median.score_genetic))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.score_genetic)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_heart_all_traits_no_na$median.score_genetic)
print("mean")
mean(data_cor_heart_all_traits_no_na$median.score_genetic)
print("standard deviation")
sd(data_cor_heart_all_traits_no_na$median.score_genetic)
```


# Merge all Boxplot

## median.genes
```{r}
# Boxplot

data_cor_heart_all_traits %>%
  ggplot( aes(x=trait, y=median.genes, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")

```


## median.umi
```{r}
# Boxplot

data_cor_heart_all_traits %>%
  ggplot( aes(x=trait, y=median.umi, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```


## median.score_genetic
```{r}
# Boxplot

data_cor_heart_all_traits %>%
  ggplot( aes(x=trait, y=median.score_genetic, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```

# Notes
```{r}
sessionInfo()
```

