---
title: "pval_distribution_all_cor_[spinal_cord_datasets]_spearman"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Script for calculating Spearman correlations across spatial structures for selected tissue-trait pairs from all genetically associated genes. Comparing p-values and a) genes or b) UMIs. This was done for data generated for each organ and the output summarized in organ specific files. See folder named 'pval_data_cor_organs_all_traits_spearman' for all such files.

# Load libraries
```{r}
library(scales)
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(MASS)
```



# Load data
Load distribution data:
```{r}

# Spinal_cord

##w5_V10T03_302B1
meta.data.AHD_w5_V10T03_302B1 <- readRDS(file = "Spinal_cord/w5_V10T03_302B1/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_w5_V10T03_302B1 <- readRDS(file = "Spinal_cord/w5_V10T03_302B1/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.MS_w5_V10T03_302B1 <- readRDS(file = "Spinal_cord/w5_V10T03_302B1/p_value_distribution/pval.distribution_MS_all_genes.RDS")

##w8_V10F24_107B1
meta.data.AHD_w8_V10F24_107B1 <- readRDS(file = "Spinal_cord/w8_V10F24_107B1/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_w8_V10F24_107B1 <- readRDS(file = "Spinal_cord/w8_V10F24_107B1/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.MS_w8_V10F24_107B1 <- readRDS(file = "Spinal_cord/w8_V10F24_107B1/p_value_distribution/pval.distribution_MS_all_genes.RDS")

##w9_V10T03_288A1
meta.data.AHD_w9_V10T03_288A1 <- readRDS(file = "Spinal_cord/w9_V10T03_288A1/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_w9_V10T03_288A1 <- readRDS(file = "Spinal_cord/w9_V10T03_288A1/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.MS_w9_V10T03_288A1 <- readRDS(file = "Spinal_cord/w9_V10T03_288A1/p_value_distribution/pval.distribution_MS_all_genes.RDS")

##w12_V10T03_290D1
meta.data.AHD_w12_V10T03_290D1 <- readRDS(file = "Spinal_cord/w12_V10T03_290D1/p_value_distribution/pval.distribution_AHD_all_genes.RDS")

meta.data.ALS_w12_V10T03_290D1 <- readRDS(file = "Spinal_cord/w12_V10T03_290D1/p_value_distribution/pval.distribution_ALS_all_genes.RDS")

meta.data.MS_w12_V10T03_290D1 <- readRDS(file = "Spinal_cord/w12_V10T03_290D1/p_value_distribution/pval.distribution_MS_all_genes.RDS")

```



# w5_V10T03_302B1
```{r}
# w5_V10T03_302B1
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w5_V10T03_302B1_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.AHD_w5_V10T03_302B1$`median(genes)`,method = "spearman")))
data_cor_w5_V10T03_302B1_AHD = cbind(data_cor_w5_V10T03_302B1_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.AHD_w5_V10T03_302B1$`median(umi)`,method = "spearman"))))
data_cor_w5_V10T03_302B1_AHD = cbind(data_cor_w5_V10T03_302B1_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.AHD_w5_V10T03_302B1$`median(score_genetic)`,method = "spearman"))))
data_cor_w5_V10T03_302B1_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w5_V10T03_302B1_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.ALS_w5_V10T03_302B1$`median(genes)`,method = "spearman")))
data_cor_w5_V10T03_302B1_ALS = cbind(data_cor_w5_V10T03_302B1_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.ALS_w5_V10T03_302B1$`median(umi)`,method = "spearman"))))
data_cor_w5_V10T03_302B1_ALS = cbind(data_cor_w5_V10T03_302B1_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.ALS_w5_V10T03_302B1$`median(score_genetic)`,method = "spearman"))))
data_cor_w5_V10T03_302B1_ALS$trait <- "ALS"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w5_V10T03_302B1_MS = data.frame(median.genes = (cor(x=meta.data.MS_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.MS_w5_V10T03_302B1$`median(genes)`,method = "spearman")))
data_cor_w5_V10T03_302B1_MS = cbind(data_cor_w5_V10T03_302B1_MS,data.frame(median.umi = (cor(x=meta.data.MS_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.MS_w5_V10T03_302B1$`median(umi)`,method = "spearman"))))
data_cor_w5_V10T03_302B1_MS = cbind(data_cor_w5_V10T03_302B1_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_w5_V10T03_302B1$`-log10(p.val_genetic)`,y=meta.data.MS_w5_V10T03_302B1$`median(score_genetic)`,method = "spearman"))))
data_cor_w5_V10T03_302B1_MS$trait <- "MS"


data_cor_w5_V10T03_302B1_all <- rbind(data_cor_w5_V10T03_302B1_AHD,data_cor_w5_V10T03_302B1_ALS)
data_cor_w5_V10T03_302B1_all <- rbind(data_cor_w5_V10T03_302B1_all,data_cor_w5_V10T03_302B1_MS)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_w5_V10T03_302B1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_w5_V10T03_302B1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_w5_V10T03_302B1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# w8_V10F24_107B1
```{r}
# w8_V10F24_107B1
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w8_V10F24_107B1_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.AHD_w8_V10F24_107B1$`median(genes)`,method = "spearman")))
data_cor_w8_V10F24_107B1_AHD = cbind(data_cor_w8_V10F24_107B1_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.AHD_w8_V10F24_107B1$`median(umi)`,method = "spearman"))))
data_cor_w8_V10F24_107B1_AHD = cbind(data_cor_w8_V10F24_107B1_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.AHD_w8_V10F24_107B1$`median(score_genetic)`,method = "spearman"))))
data_cor_w8_V10F24_107B1_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w8_V10F24_107B1_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.ALS_w8_V10F24_107B1$`median(genes)`,method = "spearman")))
data_cor_w8_V10F24_107B1_ALS = cbind(data_cor_w8_V10F24_107B1_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.ALS_w8_V10F24_107B1$`median(umi)`,method = "spearman"))))
data_cor_w8_V10F24_107B1_ALS = cbind(data_cor_w8_V10F24_107B1_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.ALS_w8_V10F24_107B1$`median(score_genetic)`,method = "spearman"))))
data_cor_w8_V10F24_107B1_ALS$trait <- "ALS"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w8_V10F24_107B1_MS = data.frame(median.genes = (cor(x=meta.data.MS_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.MS_w8_V10F24_107B1$`median(genes)`,method = "spearman")))
data_cor_w8_V10F24_107B1_MS = cbind(data_cor_w8_V10F24_107B1_MS,data.frame(median.umi = (cor(x=meta.data.MS_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.MS_w8_V10F24_107B1$`median(umi)`,method = "spearman"))))
data_cor_w8_V10F24_107B1_MS = cbind(data_cor_w8_V10F24_107B1_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_w8_V10F24_107B1$`-log10(p.val_genetic)`,y=meta.data.MS_w8_V10F24_107B1$`median(score_genetic)`,method = "spearman"))))
data_cor_w8_V10F24_107B1_MS$trait <- "MS"


data_cor_w8_V10F24_107B1_all <- rbind(data_cor_w8_V10F24_107B1_AHD,data_cor_w8_V10F24_107B1_ALS)
data_cor_w8_V10F24_107B1_all <- rbind(data_cor_w8_V10F24_107B1_all,data_cor_w8_V10F24_107B1_MS)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_w8_V10F24_107B1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_w8_V10F24_107B1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_w8_V10F24_107B1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# w9_V10T03_288A1
```{r}
# w9_V10T03_288A1
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w9_V10T03_288A1_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.AHD_w9_V10T03_288A1$`median(genes)`,method = "spearman")))
data_cor_w9_V10T03_288A1_AHD = cbind(data_cor_w9_V10T03_288A1_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.AHD_w9_V10T03_288A1$`median(umi)`,method = "spearman"))))
data_cor_w9_V10T03_288A1_AHD = cbind(data_cor_w9_V10T03_288A1_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.AHD_w9_V10T03_288A1$`median(score_genetic)`,method = "spearman"))))
data_cor_w9_V10T03_288A1_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w9_V10T03_288A1_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.ALS_w9_V10T03_288A1$`median(genes)`,method = "spearman")))
data_cor_w9_V10T03_288A1_ALS = cbind(data_cor_w9_V10T03_288A1_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.ALS_w9_V10T03_288A1$`median(umi)`,method = "spearman"))))
data_cor_w9_V10T03_288A1_ALS = cbind(data_cor_w9_V10T03_288A1_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.ALS_w9_V10T03_288A1$`median(score_genetic)`,method = "spearman"))))
data_cor_w9_V10T03_288A1_ALS$trait <- "ALS"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w9_V10T03_288A1_MS = data.frame(median.genes = (cor(x=meta.data.MS_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.MS_w9_V10T03_288A1$`median(genes)`,method = "spearman")))
data_cor_w9_V10T03_288A1_MS = cbind(data_cor_w9_V10T03_288A1_MS,data.frame(median.umi = (cor(x=meta.data.MS_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.MS_w9_V10T03_288A1$`median(umi)`,method = "spearman"))))
data_cor_w9_V10T03_288A1_MS = cbind(data_cor_w9_V10T03_288A1_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_w9_V10T03_288A1$`-log10(p.val_genetic)`,y=meta.data.MS_w9_V10T03_288A1$`median(score_genetic)`,method = "spearman"))))
data_cor_w9_V10T03_288A1_MS$trait <- "MS"


data_cor_w9_V10T03_288A1_all <- rbind(data_cor_w9_V10T03_288A1_AHD,data_cor_w9_V10T03_288A1_ALS)
data_cor_w9_V10T03_288A1_all <- rbind(data_cor_w9_V10T03_288A1_all,data_cor_w9_V10T03_288A1_MS)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_w9_V10T03_288A1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_w9_V10T03_288A1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_w9_V10T03_288A1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# w12_V10T03_290D1
```{r}
# w12_V10T03_290D1
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w12_V10T03_290D1_AHD = data.frame(median.genes = (cor(x=meta.data.AHD_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.AHD_w12_V10T03_290D1$`median(genes)`,method = "spearman")))
data_cor_w12_V10T03_290D1_AHD = cbind(data_cor_w12_V10T03_290D1_AHD,data.frame(median.umi = (cor(x=meta.data.AHD_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.AHD_w12_V10T03_290D1$`median(umi)`,method = "spearman"))))
data_cor_w12_V10T03_290D1_AHD = cbind(data_cor_w12_V10T03_290D1_AHD,data.frame(median.score_genetic = (cor(x=meta.data.AHD_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.AHD_w12_V10T03_290D1$`median(score_genetic)`,method = "spearman"))))
data_cor_w12_V10T03_290D1_AHD$trait <- "AHD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w12_V10T03_290D1_ALS = data.frame(median.genes = (cor(x=meta.data.ALS_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.ALS_w12_V10T03_290D1$`median(genes)`,method = "spearman")))
data_cor_w12_V10T03_290D1_ALS = cbind(data_cor_w12_V10T03_290D1_ALS,data.frame(median.umi = (cor(x=meta.data.ALS_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.ALS_w12_V10T03_290D1$`median(umi)`,method = "spearman"))))
data_cor_w12_V10T03_290D1_ALS = cbind(data_cor_w12_V10T03_290D1_ALS,data.frame(median.score_genetic = (cor(x=meta.data.ALS_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.ALS_w12_V10T03_290D1$`median(score_genetic)`,method = "spearman"))))
data_cor_w12_V10T03_290D1_ALS$trait <- "ALS"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_w12_V10T03_290D1_MS = data.frame(median.genes = (cor(x=meta.data.MS_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.MS_w12_V10T03_290D1$`median(genes)`,method = "spearman")))
data_cor_w12_V10T03_290D1_MS = cbind(data_cor_w12_V10T03_290D1_MS,data.frame(median.umi = (cor(x=meta.data.MS_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.MS_w12_V10T03_290D1$`median(umi)`,method = "spearman"))))
data_cor_w12_V10T03_290D1_MS = cbind(data_cor_w12_V10T03_290D1_MS,data.frame(median.score_genetic = (cor(x=meta.data.MS_w12_V10T03_290D1$`-log10(p.val_genetic)`,y=meta.data.MS_w12_V10T03_290D1$`median(score_genetic)`,method = "spearman"))))
data_cor_w12_V10T03_290D1_MS$trait <- "MS"


data_cor_w12_V10T03_290D1_all <- rbind(data_cor_w12_V10T03_290D1_AHD,data_cor_w12_V10T03_290D1_ALS)
data_cor_w12_V10T03_290D1_all <- rbind(data_cor_w12_V10T03_290D1_all,data_cor_w12_V10T03_290D1_MS)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_w12_V10T03_290D1_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_w12_V10T03_290D1_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_w12_V10T03_290D1_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# Merge all histogram
```{r}
data_cor_w5_V10T03_302B1_all$dataset <- "w5_V10T03_302B1"
data_cor_w5_V10T03_302B1_all
data_cor_w8_V10F24_107B1_all$dataset <- "w8_V10F24_107B1"
data_cor_w8_V10F24_107B1_all
data_cor_w9_V10T03_288A1_all$dataset <- "w9_V10T03_288A1"
data_cor_w9_V10T03_288A1_all
data_cor_w12_V10T03_290D1_all$dataset <- "w12_V10T03_290D1"
data_cor_w12_V10T03_290D1_all

#Merge
data_cor_spinal_cord_all_traits <- rbind(data_cor_w5_V10T03_302B1_all,data_cor_w8_V10F24_107B1_all)
data_cor_spinal_cord_all_traits <- rbind(data_cor_spinal_cord_all_traits,data_cor_w9_V10T03_288A1_all)
data_cor_spinal_cord_all_traits <- rbind(data_cor_spinal_cord_all_traits,data_cor_w12_V10T03_290D1_all)

#Save data
saveRDS(data_cor_spinal_cord_all_traits, file = "pval_data_cor_organs_all_traits_spearman/data_cor_spinal_cord_all_traits_spearman.rds")
write.matrix(data_cor_spinal_cord_all_traits,file="pval_data_cor_organs_all_traits_spearman/data_cor_spinal_cord_all_traits_spearman.csv",sep = ";")

```


## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_spinal_cord_all_traits, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```
Median Genes
```{r}
# basic histogram
data_cor_spinal_cord_all_traits_no_na <- na.exclude(data_cor_spinal_cord_all_traits)

p <- ggplot(data_cor_spinal_cord_all_traits_no_na, aes(x=median.genes)) + 
  geom_histogram(bins = (length(data_cor_spinal_cord_all_traits_no_na$median.genes))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.genes)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_spinal_cord_all_traits_no_na$median.genes)
print("mean")
mean(data_cor_spinal_cord_all_traits_no_na$median.genes)
print("standard deviation")
sd(data_cor_spinal_cord_all_traits_no_na$median.genes)
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_spinal_cord_all_traits, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median UMI
```{r}
# basic histogram
data_cor_spinal_cord_all_traits_no_na <- na.exclude(data_cor_spinal_cord_all_traits)

p <- ggplot(data_cor_spinal_cord_all_traits_no_na, aes(x=median.umi)) + 
  geom_histogram(bins = (length(data_cor_spinal_cord_all_traits_no_na$median.umi))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.umi)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_spinal_cord_all_traits_no_na$median.umi)
print("mean")
mean(data_cor_spinal_cord_all_traits_no_na$median.umi)
print("standard deviation")
sd(data_cor_spinal_cord_all_traits_no_na$median.umi)
```


## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_spinal_cord_all_traits, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median score genetic
```{r}
# basic histogram
data_cor_spinal_cord_all_traits_no_na <- na.exclude(data_cor_spinal_cord_all_traits)

p <- ggplot(data_cor_spinal_cord_all_traits_no_na, aes(x=median.score_genetic)) + 
  geom_histogram(bins = (length(data_cor_spinal_cord_all_traits_no_na$median.score_genetic))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.score_genetic)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_spinal_cord_all_traits_no_na$median.score_genetic)
print("mean")
mean(data_cor_spinal_cord_all_traits_no_na$median.score_genetic)
print("standard deviation")
sd(data_cor_spinal_cord_all_traits_no_na$median.score_genetic)
```


# Merge all Boxplot

## median.genes
```{r}
# Boxplot

data_cor_spinal_cord_all_traits %>%
  ggplot( aes(x=trait, y=median.genes, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")

```


## median.umi
```{r}
# Boxplot

data_cor_spinal_cord_all_traits %>%
  ggplot( aes(x=trait, y=median.umi, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```


## median.score_genetic
```{r}
# Boxplot

data_cor_spinal_cord_all_traits %>%
  ggplot( aes(x=trait, y=median.score_genetic, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```

# Notes
```{r}
sessionInfo()
```

