---
title: "pval_distribution_all_cor_[lung_datasets]_spearman"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Script for calculating Spearman correlations across spatial structures for selected tissue-trait pairs from all genetically associated genes. Comparing p-values and a) genes or b) UMIs. This was done for data generated for each organ and the output summarized in organ specific files. See folder named 'pval_data_cor_organs_all_traits_spearman' for all such files.

# Load libraries
```{r}
library(scales)
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(MASS)
```



# Load data
Load distribution data:
```{r}

# LUNG

##HLA_Parenchyma_A37_347
meta.data.AST_HLA_Parenchyma_A37_347 <- readRDS(file = "Lung/HLA_Parenchyma_A37_347/p_value_distribution/pval.distribution_AST_all_genes.RDS")

meta.data.BRD_HLA_Parenchyma_A37_347 <- readRDS(file = "Lung/HLA_Parenchyma_A37_347/p_value_distribution/pval.distribution_BRD_all_genes.RDS")

meta.data.COPD_HLA_Parenchyma_A37_347 <- readRDS(file = "Lung/HLA_Parenchyma_A37_347/p_value_distribution/pval.distribution_COPD_all_genes.RDS")

meta.data.LUD_HLA_Parenchyma_A37_347 <- readRDS(file = "Lung/HLA_Parenchyma_A37_347/p_value_distribution/pval.distribution_LUD_all_genes.RDS")


##HLA_Parenchyma_A48_345
meta.data.AST_HLA_Parenchyma_A48_345 <- readRDS(file = "Lung/HLA_Parenchyma_A48_345/p_value_distribution/pval.distribution_AST_all_genes.RDS")

meta.data.BRD_HLA_Parenchyma_A48_345 <- readRDS(file = "Lung/HLA_Parenchyma_A48_345/p_value_distribution/pval.distribution_BRD_all_genes.RDS")

meta.data.COPD_HLA_Parenchyma_A48_345 <- readRDS(file = "Lung/HLA_Parenchyma_A48_345/p_value_distribution/pval.distribution_COPD_all_genes.RDS")

meta.data.LUD_HLA_Parenchyma_A48_345 <- readRDS(file = "Lung/HLA_Parenchyma_A48_345/p_value_distribution/pval.distribution_LUD_all_genes.RDS")


##HLA_Bronchi_A50_467
meta.data.AST_HLA_Bronchi_A50_467 <- readRDS(file = "Lung/HLA_Bronchi_A50_467/p_value_distribution/pval.distribution_AST_all_genes.RDS")

meta.data.BRD_HLA_Bronchi_A50_467 <- readRDS(file = "Lung/HLA_Bronchi_A50_467/p_value_distribution/pval.distribution_BRD_all_genes.RDS")

meta.data.COPD_HLA_Bronchi_A50_467 <- readRDS(file = "Lung/HLA_Bronchi_A50_467/p_value_distribution/pval.distribution_COPD_all_genes.RDS")

meta.data.LUD_HLA_Bronchi_A50_467 <- readRDS(file = "Lung/HLA_Bronchi_A50_467/p_value_distribution/pval.distribution_LUD_all_genes.RDS")


##HLA_Bronchi_A42_311
meta.data.AST_HLA_Bronchi_A42_311 <- readRDS(file = "Lung/HLA_Bronchi_A42_311/p_value_distribution/pval.distribution_AST_all_genes.RDS")

meta.data.BRD_HLA_Bronchi_A42_311 <- readRDS(file = "Lung/HLA_Bronchi_A42_311/p_value_distribution/pval.distribution_BRD_all_genes.RDS")

meta.data.COPD_HLA_Bronchi_A42_311 <- readRDS(file = "Lung/HLA_Bronchi_A42_311/p_value_distribution/pval.distribution_COPD_all_genes.RDS")

meta.data.LUD_HLA_Bronchi_A42_311 <- readRDS(file = "Lung/HLA_Bronchi_A42_311/p_value_distribution/pval.distribution_LUD_all_genes.RDS")


```



# HLA_Parenchyma_A37_347
```{r}
# HLA_Parenchyma_A37_347
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A37_347_AST = data.frame(median.genes = (cor(x=meta.data.AST_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Parenchyma_A37_347$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A37_347_AST = cbind(data_cor_HLA_Parenchyma_A37_347_AST,data.frame(median.umi = (cor(x=meta.data.AST_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Parenchyma_A37_347$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_AST = cbind(data_cor_HLA_Parenchyma_A37_347_AST,data.frame(median.score_genetic = (cor(x=meta.data.AST_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Parenchyma_A37_347$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_AST$trait <- "AST"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A37_347_BRD = data.frame(median.genes = (cor(x=meta.data.BRD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Parenchyma_A37_347$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A37_347_BRD = cbind(data_cor_HLA_Parenchyma_A37_347_BRD,data.frame(median.umi = (cor(x=meta.data.BRD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Parenchyma_A37_347$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_BRD = cbind(data_cor_HLA_Parenchyma_A37_347_BRD,data.frame(median.score_genetic = (cor(x=meta.data.BRD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Parenchyma_A37_347$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_BRD$trait <- "BRD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A37_347_COPD = data.frame(median.genes = (cor(x=meta.data.COPD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Parenchyma_A37_347$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A37_347_COPD = cbind(data_cor_HLA_Parenchyma_A37_347_COPD,data.frame(median.umi = (cor(x=meta.data.COPD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Parenchyma_A37_347$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_COPD = cbind(data_cor_HLA_Parenchyma_A37_347_COPD,data.frame(median.score_genetic = (cor(x=meta.data.COPD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Parenchyma_A37_347$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_COPD$trait <- "COPD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A37_347_LUD = data.frame(median.genes = (cor(x=meta.data.LUD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Parenchyma_A37_347$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A37_347_LUD = cbind(data_cor_HLA_Parenchyma_A37_347_LUD,data.frame(median.umi = (cor(x=meta.data.LUD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Parenchyma_A37_347$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_LUD = cbind(data_cor_HLA_Parenchyma_A37_347_LUD,data.frame(median.score_genetic = (cor(x=meta.data.LUD_HLA_Parenchyma_A37_347$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Parenchyma_A37_347$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A37_347_LUD$trait <- "LUD"

data_cor_HLA_Parenchyma_A37_347_all <- rbind(data_cor_HLA_Parenchyma_A37_347_AST,data_cor_HLA_Parenchyma_A37_347_BRD)
data_cor_HLA_Parenchyma_A37_347_all <- rbind(data_cor_HLA_Parenchyma_A37_347_all,data_cor_HLA_Parenchyma_A37_347_COPD)
data_cor_HLA_Parenchyma_A37_347_all <- rbind(data_cor_HLA_Parenchyma_A37_347_all,data_cor_HLA_Parenchyma_A37_347_LUD)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Parenchyma_A37_347_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Parenchyma_A37_347_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Parenchyma_A37_347_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```





# HLA_Parenchyma_A48_345
```{r}
# HLA_Parenchyma_A48_345
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A48_345_AST = data.frame(median.genes = (cor(x=meta.data.AST_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Parenchyma_A48_345$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A48_345_AST = cbind(data_cor_HLA_Parenchyma_A48_345_AST,data.frame(median.umi = (cor(x=meta.data.AST_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Parenchyma_A48_345$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_AST = cbind(data_cor_HLA_Parenchyma_A48_345_AST,data.frame(median.score_genetic = (cor(x=meta.data.AST_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Parenchyma_A48_345$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_AST$trait <- "AST"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A48_345_BRD = data.frame(median.genes = (cor(x=meta.data.BRD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Parenchyma_A48_345$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A48_345_BRD = cbind(data_cor_HLA_Parenchyma_A48_345_BRD,data.frame(median.umi = (cor(x=meta.data.BRD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Parenchyma_A48_345$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_BRD = cbind(data_cor_HLA_Parenchyma_A48_345_BRD,data.frame(median.score_genetic = (cor(x=meta.data.BRD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Parenchyma_A48_345$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_BRD$trait <- "BRD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A48_345_COPD = data.frame(median.genes = (cor(x=meta.data.COPD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Parenchyma_A48_345$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A48_345_COPD = cbind(data_cor_HLA_Parenchyma_A48_345_COPD,data.frame(median.umi = (cor(x=meta.data.COPD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Parenchyma_A48_345$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_COPD = cbind(data_cor_HLA_Parenchyma_A48_345_COPD,data.frame(median.score_genetic = (cor(x=meta.data.COPD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Parenchyma_A48_345$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_COPD$trait <- "COPD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Parenchyma_A48_345_LUD = data.frame(median.genes = (cor(x=meta.data.LUD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Parenchyma_A48_345$`median(genes)`,method = "spearman")))
data_cor_HLA_Parenchyma_A48_345_LUD = cbind(data_cor_HLA_Parenchyma_A48_345_LUD,data.frame(median.umi = (cor(x=meta.data.LUD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Parenchyma_A48_345$`median(umi)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_LUD = cbind(data_cor_HLA_Parenchyma_A48_345_LUD,data.frame(median.score_genetic = (cor(x=meta.data.LUD_HLA_Parenchyma_A48_345$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Parenchyma_A48_345$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Parenchyma_A48_345_LUD$trait <- "LUD"

data_cor_HLA_Parenchyma_A48_345_all <- rbind(data_cor_HLA_Parenchyma_A48_345_AST,data_cor_HLA_Parenchyma_A48_345_BRD)
data_cor_HLA_Parenchyma_A48_345_all <- rbind(data_cor_HLA_Parenchyma_A48_345_all,data_cor_HLA_Parenchyma_A48_345_COPD)
data_cor_HLA_Parenchyma_A48_345_all <- rbind(data_cor_HLA_Parenchyma_A48_345_all,data_cor_HLA_Parenchyma_A48_345_LUD)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Parenchyma_A48_345_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Parenchyma_A48_345_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Parenchyma_A48_345_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# HLA_Bronchi_A50_467
```{r}
# HLA_Bronchi_A50_467
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A50_467_AST = data.frame(median.genes = (cor(x=meta.data.AST_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Bronchi_A50_467$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A50_467_AST = cbind(data_cor_HLA_Bronchi_A50_467_AST,data.frame(median.umi = (cor(x=meta.data.AST_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Bronchi_A50_467$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_AST = cbind(data_cor_HLA_Bronchi_A50_467_AST,data.frame(median.score_genetic = (cor(x=meta.data.AST_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Bronchi_A50_467$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_AST$trait <- "AST"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A50_467_BRD = data.frame(median.genes = (cor(x=meta.data.BRD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Bronchi_A50_467$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A50_467_BRD = cbind(data_cor_HLA_Bronchi_A50_467_BRD,data.frame(median.umi = (cor(x=meta.data.BRD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Bronchi_A50_467$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_BRD = cbind(data_cor_HLA_Bronchi_A50_467_BRD,data.frame(median.score_genetic = (cor(x=meta.data.BRD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Bronchi_A50_467$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_BRD$trait <- "BRD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A50_467_COPD = data.frame(median.genes = (cor(x=meta.data.COPD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Bronchi_A50_467$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A50_467_COPD = cbind(data_cor_HLA_Bronchi_A50_467_COPD,data.frame(median.umi = (cor(x=meta.data.COPD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Bronchi_A50_467$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_COPD = cbind(data_cor_HLA_Bronchi_A50_467_COPD,data.frame(median.score_genetic = (cor(x=meta.data.COPD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Bronchi_A50_467$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_COPD$trait <- "COPD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A50_467_LUD = data.frame(median.genes = (cor(x=meta.data.LUD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Bronchi_A50_467$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A50_467_LUD = cbind(data_cor_HLA_Bronchi_A50_467_LUD,data.frame(median.umi = (cor(x=meta.data.LUD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Bronchi_A50_467$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_LUD = cbind(data_cor_HLA_Bronchi_A50_467_LUD,data.frame(median.score_genetic = (cor(x=meta.data.LUD_HLA_Bronchi_A50_467$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Bronchi_A50_467$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A50_467_LUD$trait <- "LUD"

data_cor_HLA_Bronchi_A50_467_all <- rbind(data_cor_HLA_Bronchi_A50_467_AST,data_cor_HLA_Bronchi_A50_467_BRD)
data_cor_HLA_Bronchi_A50_467_all <- rbind(data_cor_HLA_Bronchi_A50_467_all,data_cor_HLA_Bronchi_A50_467_COPD)
data_cor_HLA_Bronchi_A50_467_all <- rbind(data_cor_HLA_Bronchi_A50_467_all,data_cor_HLA_Bronchi_A50_467_LUD)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Bronchi_A50_467_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Bronchi_A50_467_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Bronchi_A50_467_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```



# HLA_Bronchi_A42_311
```{r}
# HLA_Bronchi_A42_311
# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A42_311_AST = data.frame(median.genes = (cor(x=meta.data.AST_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Bronchi_A42_311$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A42_311_AST = cbind(data_cor_HLA_Bronchi_A42_311_AST,data.frame(median.umi = (cor(x=meta.data.AST_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Bronchi_A42_311$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_AST = cbind(data_cor_HLA_Bronchi_A42_311_AST,data.frame(median.score_genetic = (cor(x=meta.data.AST_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.AST_HLA_Bronchi_A42_311$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_AST$trait <- "AST"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A42_311_BRD = data.frame(median.genes = (cor(x=meta.data.BRD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Bronchi_A42_311$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A42_311_BRD = cbind(data_cor_HLA_Bronchi_A42_311_BRD,data.frame(median.umi = (cor(x=meta.data.BRD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Bronchi_A42_311$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_BRD = cbind(data_cor_HLA_Bronchi_A42_311_BRD,data.frame(median.score_genetic = (cor(x=meta.data.BRD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.BRD_HLA_Bronchi_A42_311$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_BRD$trait <- "BRD"

# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A42_311_COPD = data.frame(median.genes = (cor(x=meta.data.COPD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Bronchi_A42_311$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A42_311_COPD = cbind(data_cor_HLA_Bronchi_A42_311_COPD,data.frame(median.umi = (cor(x=meta.data.COPD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Bronchi_A42_311$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_COPD = cbind(data_cor_HLA_Bronchi_A42_311_COPD,data.frame(median.score_genetic = (cor(x=meta.data.COPD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.COPD_HLA_Bronchi_A42_311$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_COPD$trait <- "COPD"


# spearman: between -log10(p.val_genetic) & median(genes), median(umi), median(score_genetic)
data_cor_HLA_Bronchi_A42_311_LUD = data.frame(median.genes = (cor(x=meta.data.LUD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Bronchi_A42_311$`median(genes)`,method = "spearman")))
data_cor_HLA_Bronchi_A42_311_LUD = cbind(data_cor_HLA_Bronchi_A42_311_LUD,data.frame(median.umi = (cor(x=meta.data.LUD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Bronchi_A42_311$`median(umi)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_LUD = cbind(data_cor_HLA_Bronchi_A42_311_LUD,data.frame(median.score_genetic = (cor(x=meta.data.LUD_HLA_Bronchi_A42_311$`-log10(p.val_genetic)`,y=meta.data.LUD_HLA_Bronchi_A42_311$`median(score_genetic)`,method = "spearman"))))
data_cor_HLA_Bronchi_A42_311_LUD$trait <- "LUD"

data_cor_HLA_Bronchi_A42_311_all <- rbind(data_cor_HLA_Bronchi_A42_311_AST,data_cor_HLA_Bronchi_A42_311_BRD)
data_cor_HLA_Bronchi_A42_311_all <- rbind(data_cor_HLA_Bronchi_A42_311_all,data_cor_HLA_Bronchi_A42_311_COPD)
data_cor_HLA_Bronchi_A42_311_all <- rbind(data_cor_HLA_Bronchi_A42_311_all,data_cor_HLA_Bronchi_A42_311_LUD)
```

## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Bronchi_A42_311_all, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Bronchi_A42_311_all, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_HLA_Bronchi_A42_311_all, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```




# Merge all histogram
```{r}
data_cor_HLA_Parenchyma_A37_347_all$dataset <- "HLA_Parenchyma_A37_347"
data_cor_HLA_Parenchyma_A37_347_all
data_cor_HLA_Parenchyma_A48_345_all$dataset <- "HLA_Parenchyma_A48_345"
data_cor_HLA_Parenchyma_A48_345_all
data_cor_HLA_Bronchi_A50_467_all$dataset <- "HLA_Bronchi_A50_467"
data_cor_HLA_Bronchi_A50_467_all
data_cor_HLA_Bronchi_A42_311_all$dataset <- "HLA_Bronchi_A42_311"
data_cor_HLA_Bronchi_A42_311_all

#Merge
data_cor_lung_all_traits <- rbind(data_cor_HLA_Parenchyma_A37_347_all,data_cor_HLA_Parenchyma_A48_345_all)
data_cor_lung_all_traits <- rbind(data_cor_lung_all_traits,data_cor_HLA_Bronchi_A50_467_all)
data_cor_lung_all_traits <- rbind(data_cor_lung_all_traits,data_cor_HLA_Bronchi_A42_311_all)

#Save data
#saveRDS(data_cor_lung_all_traits, file = "pval_data_cor_organs_all_traits_spearman/data_cor_lung_all_traits_spearman.rds")
#write.matrix(data_cor_lung_all_traits,file="pval_data_cor_organs_all_traits_spearman/data_cor_lung_all_traits_spearman.csv",sep = ";")

```


## median.genes
```{r}

# basic histogram
p <- ggplot(data_cor_lung_all_traits, aes(x=median.genes)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```
Median Genes
```{r}
# basic histogram
data_cor_lung_all_traits_no_na <- na.exclude(data_cor_lung_all_traits)

p <- ggplot(data_cor_lung_all_traits_no_na, aes(x=median.genes)) + 
  geom_histogram(bins = (length(data_cor_lung_all_traits_no_na$median.genes))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.genes)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_lung_all_traits_no_na$median.genes)
print("mean")
mean(data_cor_lung_all_traits_no_na$median.genes)
print("standard deviation")
sd(data_cor_lung_all_traits_no_na$median.genes)
```


## median.umi
```{r}

# basic histogram
p <- ggplot(data_cor_lung_all_traits, aes(x=median.umi)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median UMI
```{r}
# basic histogram
data_cor_lung_all_traits_no_na <- na.exclude(data_cor_lung_all_traits)

p <- ggplot(data_cor_lung_all_traits_no_na, aes(x=median.umi)) + 
  geom_histogram(bins = (length(data_cor_lung_all_traits_no_na$median.umi))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.umi)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_lung_all_traits_no_na$median.umi)
print("mean")
mean(data_cor_lung_all_traits_no_na$median.umi)
print("standard deviation")
sd(data_cor_lung_all_traits_no_na$median.umi)
```


## median.score_genetic
```{r}

# basic histogram
p <- ggplot(data_cor_lung_all_traits, aes(x=median.score_genetic)) + 
  geom_histogram(binwidth=0.05,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()

p
```

Median score genetic
```{r}
# basic histogram
data_cor_lung_all_traits_no_na <- na.exclude(data_cor_lung_all_traits)

p <- ggplot(data_cor_lung_all_traits_no_na, aes(x=median.score_genetic)) + 
  geom_histogram(bins = (length(data_cor_lung_all_traits_no_na$median.score_genetic))*2,color="black", fill="grey") + 
  xlim(-2,2) +
  theme_minimal()+
  geom_vline(aes(xintercept=median(median.score_genetic)),color="blue", linetype="dashed", size=1)

p

print("median")
median(data_cor_lung_all_traits_no_na$median.score_genetic)
print("mean")
mean(data_cor_lung_all_traits_no_na$median.score_genetic)
print("standard deviation")
sd(data_cor_lung_all_traits_no_na$median.score_genetic)
```


# Merge all Boxplot

## median.genes
```{r}
# Boxplot

data_cor_lung_all_traits %>%
  ggplot( aes(x=trait, y=median.genes, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")

```


## median.umi
```{r}
# Boxplot

data_cor_lung_all_traits %>%
  ggplot( aes(x=trait, y=median.umi, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```


## median.score_genetic
```{r}
# Boxplot

data_cor_lung_all_traits %>%
  ggplot( aes(x=trait, y=median.score_genetic, fill=trait)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_point(color="black", size=2, alpha=0.9) +
    theme_classic() +
    ggtitle("Spearman cor. with -log10(p-value)")
```

# Notes
```{r}
sessionInfo()
```

