---
title: "Step2. Human-to-Mouse file"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: readable
vignette: >
  %\VignetteIndexEntry{My Standalone Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this vignette we generate a file to convert human gene names to mouse.

# Download data

```{r, message=FALSE, warning=FALSE}
library(biomaRt)
library(dplyr)
library(tidyverse)
library(data.table)
```


Download annotations for converting gene symbols between human and mouse. Download latest annotation of the human and mouse gene names. (Does not have Ensembl annotation).
```{r, eval=FALSE}
url2 <- "https://www.informatics.jax.org/downloads/reports/HMD_HumanPhenotype.rpt"
raw.file2 <- "data/Human_to_mouse_genes/mouse_human_genes_HMD_HumanPhenotype.tsv"

download.file(url2, raw.file2 )
```

Or load annotations if already downloaded.
```{r, message=FALSE, warning=FALSE}
raw.file2 <- read.table("data/Human_to_mouse_genes/mouse_human_genes_HMD_HumanPhenotype.tsv", sep ="\t", header = F)
```


# Filter

Pre-process and format data.
```{r, read table}
df2 <- raw.file2
df2$V6 <- NULL
df2$V5 <- NULL
columns <- c("hgnc_symbol",	"h_entrez_id", "mgi_symbol", "mgi_accession_id")
colnames(df2) <- columns
mts <- df2[df2$mgi_symbol %like% "mt-",]
df2[rownames(mts),]$hgnc_symbol <- paste0("MT-",df2[rownames(mts),]$hgnc_symbol)
df2[rownames(mts),]$hgnc_symbol
df2[df2$mgi_symbol %like% "mt-",]
```

# Ensembl gene IDs

Get the Ensembl gene IDs.
```{r, biomaRt for ensembl gene ids}
human <- useMart('ensembl',dataset='hsapiens_gene_ensembl')
mouse <- useMart('ensembl',dataset='mmusculus_gene_ensembl')
human_genes <- getBM(attributes = c("ensembl_gene_id","hgnc_symbol"), mart = human)
mouse_genes <- getBM(attributes = c("ensembl_gene_id","mgi_symbol"), mart = mouse)
listEnsemblArchives()
```


Add the Ensembl gene IDs. Note that the dataset increases because the same hgnc symbol can have multiple Ensembl gene IDs.
```{r, merge symbols and ensembl gene ids}
dim(df2)
head(df2)

df2 <- df2 %>%
  left_join(human_genes) %>%
  left_join(mouse_genes) %>%
  distinct()

dim(df2)
head(df2)
```


Save.
```{r, eval=FALSE}
write.table(df2, file = "data/Human_to_mouse_genes/mouse_human_genes_20250826.tsv", row.names = F,  sep ="\t")
```


<details>
  <summary>Click to show Session Info</summary>

```{r}
sessionInfo()
```

</details>









