---
title: "OpenTarget_gene_sets_sliding_window_selection_brain_mouse_10X"
author: "Aaron Kollotzek and Linda Kvastad"
output: html_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---

NOTE: This is an example script of how to create gene list and sliding windows from these Open Targets versions .tsv files, it includes some but not all brain traits. The mouse coronal dataset can be found for download at 10X Genomics homepage, using their SpaceRanger pipeline version 1.1.0.


Load libraries
```{r}
library(STutility)
library(dplyr)
library(tidyverse)
```


Load ST data:
```{r}

infoTable <- read.csv("seurat_objects/brain_mouse_10X/infoTable_mouse_coronal.csv", sep = ";")


se <- InputFromTable(infotable = infoTable, 
                      minUMICountsPerGene = 100, 
                      minSpotsPerGene = 5,
                      minUMICountsPerSpot = 500,
                      platform =  "Visium")

```

Load OpenTarget files: OBS! Update file location for relevant OpenTargets files
```{r}
get_opentarget <- function (opentarget_dir = paste0(getwd(),"/OpenTargets/brain_mouse_10X"), mouse_genes = NULL ){
  OT.files <- list()
  disease.names <- character()
  i <- 1
  column.names <- c("Gene_symbol","Overall_assoc.score","Genetic_assoc.","Somatic_mutation","Drugs","Pathways_system_biology","Text_mining","RNA_expression","Animal_models","Target_name")
  
  if (!is.null(mouse_genes)){
    

      conversion.table <- read.table(mouse_genes,
                                     sep = "\t",
                                     header = TRUE) 
      #if mouse_genes dataframe is specified, load it

  }
  
  for (OT.file in list.files(opentarget_dir)){
    if (grepl("diseases_", OT.file)){
      print(OT.file)
  
      df <- read.table(paste(opentarget_dir, OT.file, sep= "/"),
                     sep= "\t",
                     header=TRUE,
                     quote = "")
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
    
      
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
      
      if (!is.null(mouse_genes)){
        df$Gene_symbol <- conversion.table[match(df$Gene_symbol,conversion.table$hgnc_symbol),]$mgi_symbol #convert human to mouse annotation
        OT.files[[i]] <- df
        } else {
          OT.files[[i]] <- df
        }
      i <- i+1
      disease.name <- sub(".*diseases_","", OT.file)
      disease.name <- gsub(".tsv", "", disease.name)
      disease.names <- append(disease.names, disease.name)
    }
  }

  names(OT.files) <-  disease.names
  OT.files <- map(OT.files, ~.x %>%
                    distinct())
  return(OT.files)
}
```

OBS! Update file location for relevant OpenTargets files
```{r}
OpenTargets.path <- "OpenTargets/brain_mouse_10X"
OT.files <- get_opentarget( opentarget_dir = OpenTargets.path ,mouse_genes = "mouse_human_genes_feb_23.tsv")
#OT.files.human <-get_opentarget(opentarget_dir = OpenTargets.path)

```

#Clean out genes not present in the Seurat object AND removes duplicates
```{r, clean OT.files from duplicates}
OT.files <- map(OT.files, ~.x %>%
  dplyr::select(Gene_symbol, Overall_assoc.score, Genetic_assoc.,Drugs, Animal_models)%>%
  distinct() %>%
  filter(!is.na(Gene_symbol)&Gene_symbol %in% rownames(se)) %>%
    group_by(Gene_symbol)%>%
  slice(which.max(Overall_assoc.score))%>% #==> when there is a gene mentioned twice, only keep the row where the overall association score is the highest ==> reason for duplicates is that multiple human genes have the same mouse homolog etc...
    ungroup())

# saveRDS(OT.files, file = paste("OpenTargets", sample,"OT_files_list.rds", sep = "/"))


```

Gene sets for MOUSE
```{r, create gene sets from the }
all_gene_sets <- list()
list.names <- character()
i <- 1
j <- 1
for (df in OT.files){
  ## Genes overall association score
  GWAS_OpenTarget_Overall_assoc.score_xxx <- arrange(df, desc(Overall_assoc.score))
  GWAS_OpenTarget_Overall_assoc.score_xxx <- GWAS_OpenTarget_Overall_assoc.score_xxx[!is.na(GWAS_OpenTarget_Overall_assoc.score_xxx$Overall_assoc.score),]$Gene_symbol
  ## Genes genetic association score
  GWAS_OpenTarget_Genetic_assoc._xxx <- arrange(df, desc(Genetic_assoc.))
  GWAS_OpenTarget_Genetic_assoc._xxx <- GWAS_OpenTarget_Genetic_assoc._xxx[!is.na(GWAS_OpenTarget_Genetic_assoc._xxx$Genetic_assoc.),]$Gene_symbol
  print(length(GWAS_OpenTarget_Genetic_assoc._xxx))
  ## Genes drug target
  GWAS_OpenTarget_Drugs_xxx <- arrange(df, desc(Drugs))
  # print(dim(GWAS_OpenTarget_Drugs_xxx_top100_[!is.na("Drugs"),]))
  GWAS_OpenTarget_Drugs_xxx <- GWAS_OpenTarget_Drugs_xxx[!is.na(GWAS_OpenTarget_Drugs_xxx$Drugs),]$Gene_symbol
  all_gene_sets[[i]] <- unique(GWAS_OpenTarget_Overall_assoc.score_xxx)
  all_gene_sets[[i+1]] <- unique(GWAS_OpenTarget_Genetic_assoc._xxx)
  all_gene_sets[[i+2]] <- unique(GWAS_OpenTarget_Drugs_xxx)
  list.names <- append(list.names,(c(gsub("xxx", names(OT.files[j]),"GWAS_OpenTarget_Overall_assoc.score_xxx"),
                            gsub("xxx", names(OT.files[j]),"GWAS_OpenTarget_Genetic_assoc._xxx"),
                            gsub("xxx", names(OT.files[j]),"GWAS_OpenTarget_Drugs_xxx"))))
  j <- j+1
  i <- i+3
}
names(all_gene_sets) <- list.names
```


```{r, overlapping windows function}

splitWithOverlap <- function(vec, seg.length, move) {
  starts = seq(1, length(vec), by=move)
  ends   = starts + seg.length - 1
  ends[ends > length(vec)] = length(vec)

  lapply(1:length(starts), function(i) vec[starts[i]:ends[i]])
}
```


```{r, apply the splitWithOverlap function}
win.size <- 50
move.size <- 10
windows.list <- lapply(all_gene_sets, splitWithOverlap, seg.length = win.size, move = move.size)
```


BRAIN (Mouse): EPI
```{r, Subset and name}

#All
OpenTargets_EPI_Genetic <- unlist(all_gene_sets[2])
OpenTargets_EPI_Drugs <- unlist(all_gene_sets[3])

#Subset
window50_rank_list_EPI_Genetic <- windows.list[[2]]

#Re-name
Rank_names <- rep("EPI_Genetic_Rank", length(window50_rank_list_EPI_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_EPI_Genetic) <- Rank_names

#Subset
window50_rank_list_EPI_Drugs <- windows.list[[3]]

#Re-name
Rank_names <- rep("EPI_Drugs_Rank", length(window50_rank_list_EPI_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_EPI_Drugs) <- Rank_names


```


BRAIN (Mouse): ASD
```{r, Subset and name}

#All
OpenTargets_ASD_Genetic <- unlist(all_gene_sets[5])
OpenTargets_ASD_Drugs <- unlist(all_gene_sets[6])

#Subset
window50_rank_list_ASD_Genetic <- windows.list[[5]]

#Re-name
Rank_names <- rep("ASD_Genetic_Rank", length(window50_rank_list_ASD_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ASD_Genetic) <- Rank_names

#Subset
window50_rank_list_ASD_Drugs <- windows.list[[6]]

#Re-name
Rank_names <- rep("ASD_Drugs_Rank", length(window50_rank_list_ASD_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ASD_Drugs) <- Rank_names


```


BRAIN (Mouse): ADHD
```{r, Subset and name}

#All
OpenTargets_ADHD_Genetic <- unlist(all_gene_sets[8])
OpenTargets_ADHD_Drugs <- unlist(all_gene_sets[9])

#Subset
window50_rank_list_ADHD_Genetic <- windows.list[[8]]

#Re-name
Rank_names <- rep("ADHD_Genetic_Rank", length(window50_rank_list_ADHD_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ADHD_Genetic) <- Rank_names

#Subset
window50_rank_list_ADHD_Drugs <- windows.list[[9]]

#Re-name
Rank_names <- rep("ADHD_Drugs_Rank", length(window50_rank_list_ADHD_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ADHD_Drugs) <- Rank_names


```

BRAIN (Mouse): INS
```{r, Subset and name}

#All
OpenTargets_INS_Genetic <- unlist(all_gene_sets[11])
OpenTargets_INS_Drugs <- unlist(all_gene_sets[12])

#Subset
window50_rank_list_INS_Genetic <- windows.list[[11]]

#Re-name
Rank_names <- rep("INS_Genetic_Rank", length(window50_rank_list_INS_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_INS_Genetic) <- Rank_names

#Subset
window50_rank_list_INS_Drugs <- windows.list[[12]]

#Re-name
Rank_names <- rep("INS_Drugs_Rank", length(window50_rank_list_INS_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_INS_Drugs) <- Rank_names


```

BRAIN (Mouse): MDD
```{r, Subset and name}

#All
OpenTargets_MDD_Genetic <- unlist(all_gene_sets[14])
OpenTargets_MDD_Drugs <- unlist(all_gene_sets[15])

#Subset
window50_rank_list_MDD_Genetic <- windows.list[[14]]

#Re-name
Rank_names <- rep("MDD_Genetic_Rank", length(window50_rank_list_MDD_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_MDD_Genetic) <- Rank_names

#Subset
window50_rank_list_MDD_Drugs <- windows.list[[15]]

#Re-name
Rank_names <- rep("MDD_Drugs_Rank", length(window50_rank_list_MDD_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_MDD_Drugs) <- Rank_names


```


BRAIN (Mouse): ALZ
```{r, Subset and name}

#All
OpenTargets_ALZ_Genetic <- unlist(all_gene_sets[17])
OpenTargets_ALZ_Drugs <- unlist(all_gene_sets[18])

#Subset
window50_rank_list_ALZ_Genetic <- windows.list[[17]]

#Re-name
Rank_names <- rep("ALZ_Genetic_Rank", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ALZ_Genetic) <- Rank_names

#Subset
window50_rank_list_ALZ_Drugs <- windows.list[[18]]

#Re-name
Rank_names <- rep("ALZ_Drugs_Rank", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ALZ_Drugs) <- Rank_names


```

BRAIN (Mouse): BIP
```{r, Subset and name}

#All
OpenTargets_BIP_Genetic <- unlist(all_gene_sets[20])
OpenTargets_BIP_Drugs <- unlist(all_gene_sets[21])

#Subset
window50_rank_list_BIP_Genetic <- windows.list[[20]]

#Re-name
Rank_names <- rep("BIP_Genetic_Rank", length(window50_rank_list_BIP_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_BIP_Genetic) <- Rank_names

#Subset
window50_rank_list_BIP_Drugs <- windows.list[[21]]

#Re-name
Rank_names <- rep("BIP_Drugs_Rank", length(window50_rank_list_BIP_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_BIP_Drugs) <- Rank_names


```


BRAIN (Mouse): SCZ
```{r, Subset and name}

#All
OpenTargets_SCZ_Genetic <- unlist(all_gene_sets[23])
OpenTargets_SCZ_Drugs <- unlist(all_gene_sets[24])

#Subset
window50_rank_list_SCZ_Genetic <- windows.list[[23]]

#Re-name
Rank_names <- rep("SCZ_Genetic_Rank", length(window50_rank_list_SCZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_SCZ_Genetic) <- Rank_names

#Subset
window50_rank_list_SCZ_Drugs <- windows.list[[24]]

#Re-name
Rank_names <- rep("SCZ_Drugs_Rank", length(window50_rank_list_SCZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_SCZ_Drugs) <- Rank_names


```

BRAIN (Mouse): PAR
```{r, Subset and name}

#All
OpenTargets_PAR_Genetic <- unlist(all_gene_sets[26])
OpenTargets_PAR_Drugs <- unlist(all_gene_sets[27])

#Subset
window50_rank_list_PAR_Genetic <- windows.list[[26]]

#Re-name
Rank_names <- rep("PAR_Genetic_Rank", length(window50_rank_list_PAR_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_PAR_Genetic) <- Rank_names

#Subset
window50_rank_list_PAR_Drugs <- windows.list[[27]]

#Re-name
Rank_names <- rep("PAR_Drugs_Rank", length(window50_rank_list_PAR_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_PAR_Drugs) <- Rank_names


```


BRAIN (Mouse): MS
```{r, Subset and name}

#All
OpenTargets_MS_Genetic <- unlist(all_gene_sets[29])
OpenTargets_MS_Drugs <- unlist(all_gene_sets[30])

#Subset
window50_rank_list_MS_Genetic <- windows.list[[29]]

#Re-name
Rank_names <- rep("MS_Genetic_Rank", length(window50_rank_list_MS_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_MS_Genetic) <- Rank_names

#Subset
window50_rank_list_MS_Drugs <- windows.list[[30]]

#Re-name
Rank_names <- rep("MS_Drugs_Rank", length(window50_rank_list_MS_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_MS_Drugs) <- Rank_names


```


Save: OBS OBS OBS!!! Make sure to update the name. If Human "OpenTargets_..." If Mouse "Mouse_OpenTargets_..."
```{r, eval=FALSE}

#EPI
write.table(OpenTargets_EPI_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_EPI_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_EPI_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_EPI_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_EPI_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_EPI_Genetic.RDS")

saveRDS(window50_rank_list_EPI_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_EPI_Drugs.RDS")


#ASD
write.table(OpenTargets_ASD_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ASD_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ASD_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ASD_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ASD_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_ASD_Genetic.RDS")

saveRDS(window50_rank_list_ASD_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_ASD_Drugs.RDS")


#ADHD
write.table(OpenTargets_ADHD_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ADHD_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ADHD_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ADHD_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ADHD_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_ADHD_Genetic.RDS")

saveRDS(window50_rank_list_ADHD_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_ADHD_Drugs.RDS")

#INS
write.table(OpenTargets_INS_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_INS_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_INS_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_INS_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_INS_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_INS_Genetic.RDS")

saveRDS(window50_rank_list_INS_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_INS_Drugs.RDS")


#MDD
write.table(OpenTargets_MDD_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_MDD_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_MDD_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_MDD_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_MDD_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_MDD_Genetic.RDS")

saveRDS(window50_rank_list_MDD_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_MDD_Drugs.RDS")



#ALZ
write.table(OpenTargets_ALZ_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ALZ_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ALZ_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_ALZ_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ALZ_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_ALZ_Genetic.RDS")

saveRDS(window50_rank_list_ALZ_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_ALZ_Drugs.RDS")


#BIP
write.table(OpenTargets_BIP_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_BIP_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_BIP_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_BIP_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_BIP_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_BIP_Genetic.RDS")

saveRDS(window50_rank_list_BIP_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_BIP_Drugs.RDS")


#SCZ
write.table(OpenTargets_SCZ_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_SCZ_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_SCZ_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_SCZ_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_SCZ_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_SCZ_Genetic.RDS")

saveRDS(window50_rank_list_SCZ_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_SCZ_Drugs.RDS")

#PAR
write.table(OpenTargets_PAR_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_PAR_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_PAR_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_PAR_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_PAR_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_PAR_Genetic.RDS")

saveRDS(window50_rank_list_PAR_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_PAR_Drugs.RDS")

#MS
write.table(OpenTargets_MS_Genetic,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_MS_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_MS_Drugs,file = "OpenTargets_gene_sets/brain_mouse_10X/Mouse_OpenTargets_MS_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_MS_Genetic,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_MS_Genetic.RDS")

saveRDS(window50_rank_list_MS_Drugs,file = "OpenTargets_windowLists/brain_mouse_10X/Mouse_window50_rank_list_MS_Drugs.RDS")

```


SessionInfo
```{r}
sessionInfo()
```

