---
title: "Visium_HD_dataset_16um_seurat_object_DEGs_STEAM_MetaSpots_ASD"
output: html_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---


# Load libraries

```{r}
library(Seurat)
library(arrow)
library(dplyr)
library(STEAM)
library(ggplot2)
library(viridis)
library(readr)
```


# Load data

```{r}
se <- readRDS(file="MetasSpot_objects/metaspot_seurat_normalized.rds")
se
```


```{r}
VlnPlot(se, features = "nCount_RNA", pt.size = 0, group.by = "cluster_anno")
VlnPlot(se, features = "nFeature_RNA", pt.size = 0, group.by = "cluster_anno")
```



```{r}
table(se$cluster_anno)
```


# Prepare data for STEAM analysis


Load ranked gene lists (here from Open Targets).
```{r}
OpenTargets_ASD_Genetic_ <- as.character(t(read.table(file = "Open_Target_gene_list/OT-EFO_0003756-associated-targets-5_15_2026-v26_03_ASD_genetic_mouse.csv")))
length(OpenTargets_ASD_Genetic_)
```


Filter out genes not present in the Seurat object.
```{r}
# Extract gene names from the Seurat object
gene_names <- rownames(se)
length(gene_names)

# Check gene list size before filtering
length(OpenTargets_ASD_Genetic_)

# Remove genes not present in the Seurat object from the gene lists
OpenTargets_ASD_Genetic_ <- unique(OpenTargets_ASD_Genetic_[OpenTargets_ASD_Genetic_ %in% gene_names])

# Check gene list size after filtering
length(OpenTargets_ASD_Genetic_)
```


Generate sliding window gene sets from gene lists. Select your choice of trait abbreviation (disease_abbr) and a gene list descriptive term (ot_gene_set_label). We select a window size of 50 genes, moving by 10 genes for each window.
```{r}
window_rank_list_ASD_Genetic <- generate_sliding_windows(OpenTargets_ASD_Genetic_, window_size = 50, step_size = 10, disease_abbr = "ASD", ot_gene_set_label = "Genetic")
```


Add gene sets to a list.
```{r}
all_gene_sets_OpenTargets <- list(OpenTargets_ASD_Genetic_=OpenTargets_ASD_Genetic_)
```


Merge all gene sets into one list.
```{r}
all_gene_sets <- all_gene_sets_OpenTargets
all_gene_sets <- append(all_gene_sets,window_rank_list_ASD_Genetic)
```


Calculate the average gene expression per gene list and check the percentage of genes present in the Seurat object. It is important that all genes used are present in the Seurat object, otherwise the downstream statistic assumptions are invalid.
```{r}
score.mat <- matrix(data = NA, nrow = length(all_gene_sets), ncol = 1, dimnames = list(names(all_gene_sets), "% of genes present"))

for (i in 1:length(all_gene_sets)) {
  genes <- unlist(all_gene_sets[i]) 
  score.mat[i] <- mean(genes %in% rownames(se))
  se <- AddModuleScore(se,list(genes), ctrl = 100, name = list(names(all_gene_sets[i])))
}

score.mat*100
```


```{r}
VlnPlot(se, features = c("OpenTargets_ASD_Genetic_1"), ncol = 1, group.by = "cluster_anno")
VlnPlot(se, features = c("ASD_Genetic_Rank1_1"), ncol = 1, group.by = "cluster_anno")
VlnPlot(se, features = c("ASD_Genetic_Rank2_1"), ncol = 1, group.by = "cluster_anno")
```


Load permutation matrices for your selected window size and genetic gene list.
```{r}
perm_files <- c(
  "permutation_matrices_MetaSpots/perm.mat.par_p10000_g50.rds"
)

perm_matrices <- load_permutation_matrices(perm_files)
perm.mat.window.data <- as.data.frame(perm_matrices[[1]])

perm.mat.window.data[1:5,1:5]
```


# Empirical selection of top genetic genes


Derive an empirical threshold for top genes of a ranked gene list by comparing the ranked window gene set signal to a null gene set of equal size.
```{r}
window_results.g <- window_rank_enrichment_analysis(
   se = se,
   perm.mat.window.data = perm.mat.window.data,
   window_rank_list = window_rank_list_ASD_Genetic,
   ot_gene_set_label = "Genetic",
   disease_abbr = "ASD",
   cluster_anno = "cluster_anno",
   imputation = "all"#,
   #log_file = "data/human_brain_cortex/log_files/log_file_pval_mat_genetic_window_ASD.txt"
 )

head(window_results.g)
```


Plot median scores for each window in each cluster. Use these to identify sets of top genes. 
```{r}
rank_plot_for_clusters(
   window_results = window_results.g,
   perm.mat.window = perm.mat.window.data,
   ylim = c(-0.3, 0.6)
 )
```

Subset to select the top ranked genes.
```{r}
OpenTargets_ASD_Genetic_topGenes_ <- OpenTargets_ASD_Genetic_[1:130]
length(OpenTargets_ASD_Genetic_topGenes_)
```


Add the top gene set to a list.
```{r}
all_gene_sets_OpenTargets_top <- list(OpenTargets_ASD_Genetic_topGenes_=OpenTargets_ASD_Genetic_topGenes_)
```


Calculate the average gene expression in the top gene list and check the percentage of genes present in the Seurat object.
```{r}
score.mat.top <- matrix(data = NA, nrow = length(all_gene_sets_OpenTargets_top), ncol = 1, dimnames = list(names(all_gene_sets_OpenTargets_top), "% of genes present"))

for (i in 1:length(all_gene_sets_OpenTargets_top)) {
  genes <- unlist(all_gene_sets_OpenTargets_top[i]) 
  score.mat.top[i] <- mean(genes %in% rownames(se))
  se <- AddModuleScore(se,list(genes), ctrl = 100, name = list(names(all_gene_sets_OpenTargets_top[i])))
}

score.mat.top*100
```


```{r}
se$cluster_anno_plot <- factor(
  se$cluster_anno,
  levels = as.character(0:23)
)

se <- SetIdent(se, value = "cluster_anno_plot")
p_metaspots <- VlnPlot(se, features = "OpenTargets_ASD_Genetic_topGenes_1",alpha = 1)
p_metaspots
```

Save
```{r, fig.width=6, fig.height=12}
pdf("STEAM_plots/spatial_enrichment_score_topGenes_ASD_Vlnplot_metaspots.pdf")

p_metaspots

dev.off()
```


# DEGs and Fisher’s exact test


```{r, eval=F}
DefaultAssay(se) <- "RNA"
se

se <- se %>%
  NormalizeData() %>%
  ScaleData() 

se

se <- SetIdent(se, value = "cluster_anno")


DEG_genes_all_tested <- FindAllMarkers(se, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25,slot = "data", return.thresh = 1)

DEG_genes <- subset(DEG_genes_all_tested, subset = p_val_adj <= 0.05) # using only significant DEG
```

Save DEG results.
```{r, eval=F}
write.table(DEG_genes_all_tested,file="DEG_output/DEG_genes_all_tested_MetaSpots_ASD.csv", col.names = T, row.names = F,quote = FALSE,sep = ";")

saveRDS(DEG_genes_all_tested, file="DEG_output/DEG_genes_all_tested_MetaSpots_ASD.rds")
```

Load DEGs.
```{r}
DEG_genes_all_tested <- readRDS(file="DEG_output/DEG_genes_all_tested_MetaSpots_ASD.rds")
DEG_genes <- subset(DEG_genes_all_tested, subset = p_val_adj <= 0.05) # using only significant DEG
```




Subset to select the top ranked genes.
```{r}
OpenTargets_ASD_Genetic_top <- OpenTargets_ASD_Genetic_[1:130]
length(OpenTargets_ASD_Genetic_top)
```


Run Fisher’s exact test.
```{r}
fisher_results <- run_fisher_test_degs(se, DEG_genes = DEG_genes, OT_genes = OpenTargets_ASD_Genetic_top)
fisher_results
```


Plot results.
```{r, fig.width=10}
# Ensure clusters are ordered by significance
fisher_results$cluster <- factor(fisher_results$cluster, 
                                 levels = fisher_results$cluster[order(fisher_results$adj_p_value)])

# Create the updated plot with viridis scale
p1 <- ggplot(fisher_results, aes(x = cluster, color = -log10(p_value), y = -log10(adj_p_value), size = odds_ratio)) +
  geom_point() +  
  geom_hline(yintercept = -log10(0.05), linetype = "dashed", color = "gray50") +  
  scale_color_viridis(option = "D", direction = 1, name = "-log10(p-value)") +  # Use Viridis color scale
  scale_size_continuous(range = c(2, 8), name = "Odds ratio") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1,size = 14),axis.text.y = element_text(size = 14),axis.title.x = element_text(size = 16, face = "bold"),axis.title.y = element_text(size = 16, face = "bold"),plot.title = element_text(size = 18, face = "bold"),legend.title = element_text(size = 14),legend.text = element_text(size = 12)) +  
  labs(title = "Top ASD genes (MetaSpots)",
       x = "Spatial clusters",
       y = "-log10(adj p-value)") +
  guides(color = guide_colorbar(order = 1), size = guide_legend(order = 2))

p1
```

Save
```{r, fig.height=6, fig.width=12}
pdf("STEAM_plots/spatial_enrichment_topGenes_ASD_dotplot.pdf")

p1

dev.off()
```


```{r}
fisher_results_save <- fisher_results[
  order(as.numeric(as.character(fisher_results$cluster))), 
]

fisher_results_save
```

Save
```{r}
write_csv(fisher_results_save, file = "STEAM_results/fisher_test_ASD_topGenes.csv")
```



All genes.
```{r}
length(OpenTargets_ASD_Genetic_)
```


Run Fisher’s exact test.
```{r}
fisher_results_all <- run_fisher_test_degs(se, DEG_genes = DEG_genes, OT_genes = OpenTargets_ASD_Genetic_)
fisher_results_all
```


Plot results.
```{r, fig.width=10}
# Ensure clusters are ordered by significance
fisher_results_all$cluster <- factor(fisher_results_all$cluster, 
                                 levels = fisher_results_all$cluster[order(fisher_results_all$adj_p_value)])

# Create the updated plot with viridis scale
p2 <- ggplot(fisher_results_all, aes(x = cluster, color = -log10(p_value), y = -log10(adj_p_value), size = odds_ratio)) +
  geom_point() +  
  geom_hline(yintercept = -log10(0.05), linetype = "dashed", color = "gray50") +  
  scale_color_viridis(option = "D", direction = 1, name = "-log10(p-value)") +  # Use Viridis color scale
  scale_size_continuous(range = c(2, 8), name = "Odds ratio") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1,size = 14),axis.text.y = element_text(size = 14),axis.title.x = element_text(size = 16, face = "bold"),axis.title.y = element_text(size = 16, face = "bold"),plot.title = element_text(size = 18, face = "bold"),legend.title = element_text(size = 14),legend.text = element_text(size = 12)) +  
  labs(title = "All ASD genes (MetaSpots)",
       x = "Spatial clusters",
       y = "-log10(adj p-value)") +
  guides(color = guide_colorbar(order = 1), size = guide_legend(order = 2))

p2
```


Save
```{r, fig.height=6, fig.width=12}
pdf("STEAM_plots/spatial_enrichment_allGenes_ASD_dotplot.pdf")

p2

dev.off()
```


```{r}
fisher_results_all_save <- fisher_results_all[
  order(as.numeric(as.character(fisher_results_all$cluster))), 
]

fisher_results_all_save
```

Save
```{r}
write_csv(fisher_results_all_save, file = "STEAM_results/fisher_test_ASD_allGenes.csv")
```



# Plot spatial enrichments


```{r}
se_plot <- readRDS(file = "Seurat_objects/mouse_coronal_HD_016um_Clusters_filtered.rds")
se_plot
```

```{r}
se_spatial_clusters <- readRDS(file = "spatial_clusters/mouse_coronal_HD_016um_spatial_clusters.rds")
head(se_spatial_clusters)
```


```{r}
se_plot$seurat_cluster.016um <- se_spatial_clusters$seurat_cluster.016um
head(se_plot[[]])
```



```{r}
se_plot <- SetIdent(se_plot, value = "seurat_cluster.016um")
SpatialDimPlot(se_plot)
```


```{r}
SpatialDimPlot(se_plot, cells.highlight = CellsByIdentities(object = se_plot, idents = c(5)), facet.highlight = TRUE, ncol = 1)
SpatialDimPlot(se_plot, cells.highlight = CellsByIdentities(object = se_plot, idents = c(17)), facet.highlight = TRUE, ncol = 1)
```


```{r}
# Oligodendrocytes
SpatialFeaturePlot(object = se_plot, features = "Mbp", pt.size.factor = 1.5)

# Microglia
SpatialFeaturePlot(object = se_plot, features = "P2ry12", pt.size.factor = 1.5)

# Astrocytes
SpatialFeaturePlot(object = se_plot, features = "Gfap", pt.size.factor = 1.5)

# Hypothalamus
SpatialFeaturePlot(object = se_plot, features = "Ghrh", pt.size.factor = 1.5)
SpatialFeaturePlot(object = se_plot, features = "Oxt", pt.size.factor = 1.5)
SpatialFeaturePlot(object = se_plot, features = "Avp", pt.size.factor = 1.5)
```


```{r}
VlnPlot(se_plot, features = "Mbp",alpha = 0)
VlnPlot(se_plot, features = "P2ry12",alpha = 0)
VlnPlot(se_plot, features = "Gfap",alpha = 0)
```


```{r}
# Ensure cluster column is character or factor
fisher_results$cluster <- as.character(fisher_results$cluster)


# Convert cluster to factor to match Seurat metadata
#fisher_results$cluster <- factor(fisher_results$cluster, levels = all_clusters)

# Create a data frame for metadata mapping
meta_to_add <- fisher_results[, c("cluster", "p_value", "odds_ratio", "adj_p_value")]

# Map metadata to each cell in the Seurat object
cluster_ids <- as.character(se_plot$seurat_cluster.016um)
meta_matched <- meta_to_add[match(cluster_ids, meta_to_add$cluster), -1]

# Add the metadata columns to the Seurat object
se_plot$p_value_fisher <- meta_matched$p_value
se_plot$odds_ratio_fisher <- meta_matched$odds_ratio
se_plot$adj_p_value_fisher <- meta_matched$adj_p_value

# Compute -log10(p_value) and add as metadata
se_plot$neg.log.10.p_value_fisher <- -log10(meta_matched$p_value)
se_plot$neg.log.10.p_value_fisher[is.infinite(meta_matched$neg.log.10.p_value_fisher)] <- NA
se_plot$neg.log.10.adj_p_value_fisher <- -log10(meta_matched$adj_p_value)
se_plot$neg.log.10.adj_p_value_fisher[is.infinite(meta_matched$neg.log.10.adj_p_value_fisher)] <- NA
```


Plot the adjusted p-values
```{r}
p3 <- SpatialFeaturePlot(se_plot,features = "neg.log.10.adj_p_value_fisher") + scale_fill_viridis_c()
p3
```

Save
```{r, fig.width=5, fig.height=5}
pdf("STEAM_plots/spatial_enrichment_topGenes_ASD.pdf")

p3

dev.off()
```


Plot the adjusted p-values
```{r}
p3b <- SpatialFeaturePlot(se_plot,features = "neg.log.10.adj_p_value_fisher", image.alpha = 0) + scale_fill_viridis_c()
p3b
```

Save
```{r, fig.width=5, fig.height=5}
pdf("STEAM_plots/spatial_enrichment_topGenes_ASD_noHE.pdf")

p3b

dev.off()
```


```{r}
se_score <- readRDS(file = "Seurat_objects/mouse_coronal_HD_016um_SCTransform_filtered_clusters.rds")
se_score
```



Subset to select the top ranked genes.
```{r}
OpenTargets_ASD_Genetic_topGenes_ <- OpenTargets_ASD_Genetic_[1:130]
length(OpenTargets_ASD_Genetic_topGenes_)
```


Add the top gene set to a list.
```{r}
all_gene_sets_OpenTargets_top <- list(OpenTargets_ASD_Genetic_topGenes_=OpenTargets_ASD_Genetic_topGenes_)
```


Calculate the average gene expression in the top gene list and check the percentage of genes present in the Seurat object.
```{r}
score.mat.top <- matrix(data = NA, nrow = length(all_gene_sets_OpenTargets_top), ncol = 1, dimnames = list(names(all_gene_sets_OpenTargets_top), "% of genes present"))

for (i in 1:length(all_gene_sets_OpenTargets_top)) {
  genes <- unlist(all_gene_sets_OpenTargets_top[i]) 
  score.mat.top[i] <- mean(genes %in% rownames(se_score))
  se_score <- AddModuleScore(se_score,list(genes), ctrl = 100, name = list(names(all_gene_sets_OpenTargets_top[i])))
}

score.mat.top*100
```


```{r}
p4 <- SpatialFeaturePlot(object = se_score, features = "OpenTargets_ASD_Genetic_topGenes_1", pt.size.factor = 1.5)

p4
```


Save
```{r, fig.width=5, fig.height=5}
pdf("STEAM_plots/spatial_enrichment_score_topGenes_ASD.pdf")

p4

dev.off()
```


```{r}
se_score <- SetIdent(se_score, value = "seurat_cluster.016um")
p5 <- VlnPlot(se_score, features = "OpenTargets_ASD_Genetic_topGenes_1",alpha = 0)
p5
```


Save
```{r, fig.width=6, fig.height=12}
pdf("STEAM_plots/spatial_enrichment_score_topGenes_ASD_Vlnplot.pdf")

p5

dev.off()
```


# Notes
```{r}
sessionInfo()
```

