---
title: "Visium_HD_dataset_16um_seurat_object_filtered_MetaSpots"
output: html_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---


# Load libraries


```{r}
library(Seurat)
library(arrow)
library(dplyr)
library(STEAM)
library(future)
```


# Load data


```{r}
se <- readRDS(file = "Seurat_objects/mouse_coronal_HD_016um_filtered.rds")
se
```


```{r}
se_spatial_clusters <- readRDS(file = "spatial_clusters/mouse_coronal_HD_016um_spatial_clusters.rds")
head(se_spatial_clusters)
```


```{r}
se$seurat_cluster.016um <- se_spatial_clusters$seurat_cluster.016um
head(se[[]])
```



```{r}
se <- SetIdent(se, value = "seurat_cluster.016um")
SpatialDimPlot(se)
```


```{r}
VlnPlot(se, features = "nCount_Spatial.016um", pt.size = 0, group.by = "seurat_cluster.016um")
VlnPlot(se, features = "nFeature_Spatial.016um", pt.size = 0, group.by = "seurat_cluster.016um")
```


# Generate MetaSpot clusters


Check number of cell per cell type of the cluster annotation you want to create MetaSpots from.
```{r}
table(se$seurat_cluster.016um)
```

```{r}
se$cluster_anno <- se$seurat_cluster.016um
table(se$cluster_anno)
```

```{r, warning=FALSE}
plan("sequential")

metaspots <- generate_metacell_clusters(
   se = se,
   cluster_anno = "cluster_anno",
   num_cells_per_metacell = 50,
   pca_dims = 10,
   initial_resolution = 0.1
 )
```


Save MetaSpot object
```{r}
saveRDS(metaspots, file = "MetasSpot_objects/metaspots.rds")
```


Sort the MetaSpots alphabetically.
```{r}
metaspots <- sort_metacells(se, metacells = metaspots, cluster_anno = "cluster_anno")
```


Plot the MetaCluster distribution
```{r}
plot_metaclusters(metaspots, show_mean = T, show_median = T)
```


# Aggregrate MetaSpot clusters


Aggregates the expression data across clusters (MetaSpots) by summing counts within each cluster of each cell type, and create a MetaSpot Seurat object.
```{r, warning=FALSE}
metaspot_seurat <- aggregate_metacells(cell_type_clusters = metaspots$metacells, cluster_col = "cluster_anno")
table(metaspot_seurat$cluster_anno)
```

```{r}
metaspot_seurat
```


```{r}
VlnPlot(metaspot_seurat, features = c("nFeature_RNA", "nCount_RNA"), ncol = 1, group.by = "cluster_anno")
```


Save the MetaSpot Seurat object for downstream analysis!
```{r}
saveRDS(metaspot_seurat, file = "MetasSpot_objects/metaspot_seurat.rds")
```


Normalize data with SCTransform.
```{r}
options(future.globals.maxSize = 4 * 1024^3)
metaspot_seurat <- JoinLayers(metaspot_seurat)
metaspot_seurat_normalized <- SCTransform(metaspot_seurat,assay = "RNA",return.only.var.genes = T)
```

```{r}
metaspot_seurat_normalized
```

Save the normalized MetaSpot Seurat object for downstream analysis!
```{r}
saveRDS(metaspot_seurat_normalized, file = "MetasSpot_objects/metaspot_seurat_normalized.rds")
```


# Notes
```{r}
sessionInfo()
```

