---
title: "AllNonNeurons_Adult_human_seurat_object_random_250_cells_Supercluster_h5ad"
output: html_document
date: "2025-01-06"
---

Note: Downsamples AllNonNeurons to 250 cells per supercluster.

Load libraries:
```{r, message=FALSE}
library(Seurat)
library(zellkonverter)
library(SingleCellExperiment)
library(HDF5Array)
library(dplyr)
library(biomaRt)
library(MASS)
```


Load metadata
```{r}
sce_object <- readH5AD("99f27be8-9fac-451e-9723-9e4c7191589e.h5ad",use_hdf5 = TRUE)
head(sce_object) 
colnames(colData(sce_object))# View cell metadata
```


```{r}
# Convert metadata to a DataFrame for easy filtering
metadata <- as.data.frame(colData(sce_object))
head(metadata)
table(metadata$supercluster_term)
```

```{r}
metadata$cell_id <- rownames(metadata)  # Preserve row names

# Sample up to 250 cells per supercluster_term
set.seed(123)
sampled_cells <- metadata %>%
  group_by(supercluster_term) %>%
  slice_sample(n = 250) %>%
  ungroup()

# Restore rownames
sampled_cells <- as.data.frame(sampled_cells)
rownames(sampled_cells) <- sampled_cells$cell_id
sampled_cells$cell_id <- NULL  # Remove temporary column

# Get selected cell names
selected_cells <- rownames(sampled_cells)

table(sampled_cells$supercluster_term)
```

```{r}
# Subset the SingleCellExperiment object by selected cell names
sce_subset <- sce_object[, colnames(sce_object) %in% selected_cells]
dim(sce_object)
dim(sce_subset)
```

Extract the subsetted counts and metadata
```{r}
counts_sub <- assay(sce_subset, "X")
counts_sub[1:5,1:5]
```


```{r}
# Convert metadata_sub to a DataFrame for easy filtering
metadata_sub <- as.data.frame(colData(sce_subset))
head(metadata_sub)
table(metadata_sub$supercluster_term)
```


Convert from ENSG to HGNC symbols Ensembl version 113: listEnsemblArchives()
```{r}
# Connect to Ensembl database
ensembl <- useMart("ensembl", dataset = "hsapiens_gene_ensembl")

# Query for mapping ENSG to HGNC symbols
gene_mapping <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                      filters = "ensembl_gene_id",
                      values = rownames(counts_sub),
                      mart = ensembl)

# Inspect the first few rows of the mapping
head(gene_mapping)
```


```{r}
# Create a vector of the corresponding HGNC symbols for each ENSG ID
gene_names <- gene_mapping$hgnc_symbol
names(gene_names) <- gene_mapping$ensembl_gene_id
#gene_names[is.na(gene_names)] <- names(gene_names)[is.na(gene_names)]  # Keep ENSG IDs if HGNC is missing

head(gene_names)

# check before update
head(rownames(counts_sub))
counts_sub[1:5,1:5]

# Replace ENSG IDs with HGNC symbols in the Seurat object
rownames(counts_sub) <- gene_names[rownames(counts_sub)]

# Check the result
head(rownames(counts_sub))
counts_sub[1:5,1:5]
```


Some ENSG are no longer in the database (n=994)
```{r}
sum(is.na(rownames(counts_sub)))
na_indices <- which(is.na(rownames(counts_sub)))
```

Re-extract counts_sub to check which indices does not have ENSG
```{r}
# re-extract counts_sub and save as counts_sub_check
counts_sub_check <- assay(sce_object, "X")

# Extract the ENSG IDs (row names) for those rows
na_ensg_ids <- rownames(counts_sub_check)[na_indices]

# Display the first few ENSG IDs that have missing HGNC symbols
length(na_ensg_ids)
head(na_ensg_ids)
```

Put back ENSG for that did not have a replacement gene symbol
```{r}
# Ensure that you are only replacing rows that had NA values in their rownames
rownames(counts_sub)[na_indices] <- na_ensg_ids

# Check the result to ensure that ENSG IDs have been added back to the missing rows
head(rownames(counts_sub))

sum(is.na(rownames(counts_sub)))
```

For some this did not work, checking manually in Ensembl database, these are 'novel transcripts' (n=17914)
```{r}
# Identify which rows have empty row names
empty_row_indices <- which(rownames(counts_sub) == "")
length(empty_row_indices)

# Check the first few empty row names
empty_row_names <- rownames(counts_sub)[empty_row_indices]
head(empty_row_names)
tail(empty_row_names)
```

```{r}
# Replace empty row names with a unique placeholder or ENSG IDs
rownames(counts_sub)[empty_row_indices] <- paste0("UnknownNovelTranscript_", seq_along(empty_row_indices))

# Check again if there are any remaining empty row names
sum(rownames(counts_sub) == "")  # Should now return 0

```



```{r}
# Convert sparse matrix to dense matrix
counts_matrix <- as.matrix(counts_sub)

# Now, let's create a Seurat object using this matrix
se <- CreateSeuratObject(counts = counts_matrix)
se

# Add metadata_sub to the Seurat object
se <- AddMetaData(se, metadata = metadata_sub)
head(se[[]])
```



```{r}
table(se$supercluster_term)
```


Save Seurat Object
```{r}
saveRDS(se, file = "se_250_cells.RDS")
```

Save gene_mapping
```{r, eval=FALSE}
saveRDS(gene_mapping, file = "gene_mapping.RDS")
write.matrix(gene_mapping, file=paste0("gene_mapping.csv"), sep = ";")
```




