---
title: "Compare_steam_gsMap_spatial_pval"
output: html_document
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---

Load libraries:
```{r, message=FALSE}
library(STutility)
library(dplyr)
library(RColorBrewer)
library(scales)
library(reshape2)
library(viridis)
```


Load ST data:
```{r}

infoTable <- read.csv("spatial_data/infoTable.csv", sep = ";")


se <- InputFromTable(infotable = infoTable, 
                      minUMICountsPerGene = 100, 
                      minSpotsPerGene = 5,
                      minUMICountsPerSpot = 500,
                      platform =  "Visium")

```


Load image:
```{r}
se <- LoadImages(se, time.resolve = FALSE)
```

View image:
```{r, fig.height=4, fig.width=5}
ImagePlot(se, method = "raster", annotate = FALSE)
```


Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE, eval=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```

Load cluster annotations
```{r}
seurat_clusters <- read.csv(file = "spatial_structures/seurat_clusters.csv", sep = ";")
```

Add annotations to seurat object
```{r}
rownames(seurat_clusters) <- seurat_clusters$Barcode
seurat_clusters$Barcode <- NULL
se$seurat_clusters <- seurat_clusters
se$seurat_clusters_plot <- as.factor(se$seurat_clusters) # For plotting of spatial structures
head(se[[]])
```

Plot seurat_clusters
```{r, fig.height=4, fig.width=5}
n <- 7
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
col_vector[7] <- "deepskyblue"
  
col_vector <- col_vector[1:7]

se <- SetIdent(se, value = "seurat_clusters_plot")
ST.FeaturePlot(object = se, features = "seurat_clusters_plot", pt.size = 1, cols = col_vector)
```


FeatureOverlay seurat_clusters
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1

FeatureOverlay(se, 
               features = c("seurat_clusters_plot"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = col_vector)
```



Function to read files
```{r}
read_disorder_files <- function(disorder, steam_path = "p_value_distribution/", gsMap_path = "human_heart_cauchy/") {
  
  # Base filenames
  steam_all_file <- file.path(steam_path, paste0("pval.distribution_", disorder, "_all_genes.csv"))
  gsMap_file     <- file.path(gsMap_path, paste0("human_heart_", disorder, ".Cauchy.csv"))
  
  # Load gsMap (always present)
  gsMap_df <- read.csv(gsMap_file)
  
  # --- STEAM files ---
  steam_list <- list()
  
  # Always load the all_genes file
  steam_all <- read.csv2(steam_all_file)
  steam_all$set <- "all_genes"
  steam_list[["all_genes"]] <- steam_all
  
  # Look for all "topXXX" versions (regex match)
  top_files <- list.files(steam_path, pattern = paste0("pval\\.distribution_", disorder, "_top[0-9]+_genes\\.csv"), full.names = TRUE)
  
  if (length(top_files) > 0) {
    for (f in top_files) {
      # Extract the "topXXX" part
      set_name <- sub(paste0("pval\\.distribution_", disorder, "_(top[0-9]+)_genes\\.csv"), "\\1", basename(f))
      tmp <- read.csv2(f)
      tmp$set <- set_name
      steam_list[[set_name]] <- tmp
    }
  }
  
  # Combine all STEAM sets into one data.frame
  steam_df <- do.call(rbind, steam_list)
  
  return(list(steam = steam_df, gsMap = gsMap_df))
}

```


Function to process data
```{r, eval=FALSE}
process_disorder_data <- function(steam_df, gsMap_df) {
  library(dplyr)
  
  # --- Clean STEAM ---
  steam_df$cluster <- trimws(sub("cluster_", "", as.character(steam_df$cluster)))
  
  # Convert main -log10 p-value
  steam_df$steam_pval <- 10^(-as.numeric(as.character(steam_df$X.log10.p.val_genetic.)))
  
  # Detect top-gene columns (e.g., X.log10.p.val_topXX)
  top_cols <- grep("X.log10.p.val.*top", colnames(steam_df), value = TRUE)
  for (col in top_cols) {
    new_col <- sub("X.log10.p.val\\.", "steam_pval_", col)
    steam_df[[new_col]] <- 10^(-as.numeric(as.character(steam_df[[col]])))
  }
  
  # --- Bonferroni adjustment for all STEAM columns, per set ---
  steam_pval_cols <- c("steam_pval", grep("steam_pval_top", colnames(steam_df), value = TRUE))
  steam_df <- steam_df %>%
    group_by(set) %>%
    mutate(across(all_of(steam_pval_cols), ~ ., .names = "{.col}")) %>%  # placeholder to keep grouping
    ungroup()
  
  # Adjust main steam_pval and top sets separately
  for (col in steam_pval_cols) {
    steam_df[[paste0(col, "_adj")]] <- steam_df %>%
      group_by(set) %>%
      mutate(tmp = p.adjust(.data[[col]], method = "bonferroni")) %>%
      pull(tmp)
  }
  
  # --- Collapse per set + cluster (average p-values if duplicates exist) ---
  steam_df <- steam_df %>%
    group_by(set, cluster) %>%
    summarise(across(all_of(c(steam_pval_cols, paste0(steam_pval_cols, "_adj"))), ~ mean(.x, na.rm = TRUE)),
              .groups = "drop")
  
  # --- Prepare gsMap (only for all_genes) ---
  gsMap_df$cluster <- trimws(as.character(gsMap_df$annotation))
  gsMap_df <- gsMap_df[, c("cluster", "p_cauchy")]
  colnames(gsMap_df) <- c("cluster", "gsMap_pval")
  
  # Merge gsMap only with all_genes
  merged_all <- merge(steam_df[steam_df$set == "all_genes", ],
                      gsMap_df, by = "cluster", all.x = TRUE)
  
  # Bonferroni adjustment for gsMap
  merged_all <- merged_all %>%
    group_by(set) %>%
    mutate(gsMap_pval_adj = p.adjust(gsMap_pval, method = "bonferroni")) %>%
    ungroup()
  
  # Bind top sets back (gsMap columns are NA for top sets)
  top_sets <- steam_df[steam_df$set != "all_genes", ]
  merged_df <- bind_rows(merged_all, top_sets) %>%
    arrange(set, as.numeric(cluster))
  
  return(merged_df)
}

```

```{r}
process_disorder_data <- function(steam_df, gsMap_df) {
  library(dplyr)
  
  # --- Clean STEAM ---
  steam_df$cluster <- trimws(sub("cluster_", "", as.character(steam_df$cluster)))
  
  # Convert main -log10 p-value
  steam_df$steam_pval <- 10^(-as.numeric(as.character(steam_df$X.log10.p.val_genetic.)))
  
  # Detect top-gene columns (e.g., X.log10.p.val_topXX)
  top_cols <- grep("X.log10.p.val.*top", colnames(steam_df), value = TRUE)
  for (col in top_cols) {
    new_col <- sub("X.log10.p.val\\.", "steam_pval_", col)
    steam_df[[new_col]] <- 10^(-as.numeric(as.character(steam_df[[col]])))
  }
  
  # --- Bonferroni adjustment for all STEAM columns, per set ---
  steam_pval_cols <- c("steam_pval", grep("steam_pval_top", colnames(steam_df), value = TRUE))
  
  for (col in steam_pval_cols) {
    steam_df[[paste0(col, "_adj")]] <- steam_df %>%
      group_by(set) %>%
      mutate(tmp = p.adjust(.data[[col]], method = "bonferroni")) %>%
      pull(tmp)
  }
  
  # --- Collapse per set + cluster ---
  steam_df <- steam_df %>%
    group_by(set, cluster) %>%
    summarise(across(all_of(c(steam_pval_cols, paste0(steam_pval_cols, "_adj"))), ~ mean(.x, na.rm = TRUE)),
              .groups = "drop")
  
  # --- Prepare gsMap (only for all_genes) ---
  gsMap_df$cluster <- trimws(as.character(gsMap_df$annotation))
  gsMap_df <- gsMap_df[, c("cluster", "p_cauchy")]
  colnames(gsMap_df) <- c("cluster", "gsMap_pval")
  
  # Merge gsMap only with all_genes
  merged_all <- merge(steam_df[steam_df$set == "all_genes", ],
                      gsMap_df, by = "cluster", all.x = TRUE)
  
  # Bonferroni adjustment for gsMap
  merged_all <- merged_all %>%
    group_by(set) %>%
    mutate(gsMap_pval_adj = p.adjust(gsMap_pval, method = "bonferroni")) %>%
    ungroup()
  
  # --- Handle NA top sets ---
  # If STEAM had only "all_genes" (no top sets), create placeholder rows
  top_sets <- steam_df[steam_df$set != "all_genes", ]
  if (nrow(top_sets) == 0) {
    # Identify all clusters present in steam (for consistency)
    clusters <- unique(steam_df$cluster[steam_df$set == "all_genes"])
    
    # Create a placeholder top set with NAs
    top_sets <- data.frame(
      set = "top_NA",
      cluster = clusters,
      steam_pval = NA,
      steam_pval_adj = NA,
      gsMap_pval = NA,
      gsMap_pval_adj = NA
    )
  }
  
  # Combine all_genes and top sets
  merged_df <- bind_rows(merged_all, top_sets) %>%
    arrange(set, as.numeric(cluster))
  
  return(merged_df)
}

```


Process multiple disorders
```{r}
disorders <- c("ADHD", "ASD", "BIP", "ALZ", "SCZ")
merged_results <- list()

for (dis in disorders) {
  files <- read_disorder_files(dis)
  merged_results[[dis]] <- process_disorder_data(files$steam, files$gsMap)
}
```


```{r}
merged_results$ALZ
```

Save
```{r}
write.csv2(merged_results, file = "merged_results_human_heart_[ACH003].csv", row.names = F)
```



Convert to -log10 values
```{r}
# Loop over all disorders
for (dis in names(merged_results)) {
  df <- merged_results[[dis]]
  
  # Identify all p-value columns (raw or adjusted)
  pval_cols <- grep("pval", colnames(df), value = TRUE)
  
  # Convert to numeric and then to -log10
  df[pval_cols] <- lapply(df[pval_cols], function(x) {
    x_num <- as.numeric(as.character(x))        # ensure numeric
    x_num[x_num <= 0] <- NA                     # avoid -log10(0)
    -log10(x_num)
  })
  
  # Update merged_results
  merged_results[[dis]] <- df
}

```


```{r}
merged_results$ALZ
```

Add the merged_results as metadata to the seurat object
```{r}
# Make sure cluster in metadata is character
se$cluster_char <- as.character(se$seurat_clusters)

# Loop over all disorders
for (dis in names(merged_results)) {
  
  df <- merged_results[[dis]]
  
  # Ensure cluster is character
  df$cluster <- as.character(df$cluster)
  
  # Get unique sets (all_genes, top60, top100, etc.)
  sets <- unique(df$set)
  
  for (s in sets) {
    
    # Subset the df for this set
    df_set <- df[df$set == s, ]
    
    # Identify all p-value columns
    pval_cols <- grep("_pval", colnames(df_set), value = TRUE)
    
    for (col in pval_cols) {
      # Name of the new metadata column: include disorder + set + column
      meta_col <- paste(dis, col, s, sep = "_")
      
      # Map values based on cluster
      se[[meta_col]] <- df_set[[col]][match(se$cluster_char, df_set$cluster)]
    }
  }
}

# Clean up helper column
se$cluster_char <- NULL

head(se[[]])
colnames(se@meta.data)
```


Add zero values for plot structure of non-existing steam top genes results
```{r}
se$ADHD_steam_pval_adj_topX <- se$seurat_clusters
se$ADHD_steam_pval_adj_topX[] <- 0

se$ASD_steam_pval_adj_topX <- se$seurat_clusters
se$ASD_steam_pval_adj_topX[] <- 0

se$BIP_steam_pval_adj_topX <- se$seurat_clusters
se$BIP_steam_pval_adj_topX[] <- 0

se$SCZ_steam_pval_adj_topX <- se$seurat_clusters
se$SCZ_steam_pval_adj_topX[] <- 0
```


Plot metadata
```{r, fig.width=15, fig.height=20}
p <- ST.FeaturePlot(se, features = c("ALZ_steam_pval_adj_all_genes","ALZ_steam_pval_adj_top60","ALZ_gsMap_pval_adj_all_genes","ADHD_steam_pval_adj_all_genes","ADHD_steam_pval_adj_topX","ADHD_gsMap_pval_adj_all_genes","ASD_steam_pval_adj_all_genes","ASD_steam_pval_adj_topX","ASD_gsMap_pval_adj_all_genes","BIP_steam_pval_adj_all_genes","BIP_steam_pval_adj_topX","BIP_gsMap_pval_adj_all_genes","SCZ_steam_pval_adj_all_genes","SCZ_steam_pval_adj_topX","SCZ_gsMap_pval_adj_all_genes"), pt.size = 1, value.scale = "samplewise",grid.ncol =3, cols = viridis(9))

p
```

Save
```{r}
pdf(file = "plots/human_heart_[ACH003].pdf", height = 20, width = 15)

p

dev.off()
```



Note
```{r}
sessionInfo()
```

