---
title: "Spearman_gene_gene_correlation_genetic_top_T1D[pancreas_human_20PCW_S1]"
output: html_document
author: "Linda Kvastad"
date: "2024-03-27"
---

NOTE: Plots part of Figure 3 c and d.

Load libraries:
```{r, message=FALSE}
library(STutility)
library(dplyr)
library(readr)
library(tibble)
library(stringr)
library(scales)
library(reshape2)
library(RColorBrewer)
library(ComplexHeatmap)
library(viridis)
```

Load ST data:
```{r}

infoTable <- read.csv("spatial_data/infoTable.csv", sep = ";")


se <- InputFromTable(infotable = infoTable, 
                      minUMICountsPerGene = 100, 
                      minSpotsPerGene = 5,
                      minUMICountsPerSpot = 500,
                      platform =  "Visium")

```

Load image:
```{r}
se <- LoadImages(se, time.resolve = FALSE)
```

View image:
```{r, fig.width=5, fig.height=4}
ImagePlot(se, method = "raster", annotate = FALSE)
```



QC metrics se:
```{r}
# Collect all genes coded on the mitochondrial genome
mt.genes <- grep(pattern = "^MT-", x = rownames(se), value = TRUE)
se$percent.mito <- (Matrix::colSums(se@assays$RNA@counts[mt.genes, ])/Matrix::colSums(se@assays$RNA@counts))*100

# Collect all genes coding for ribosomal proteins
rp.genes <- grep(pattern = "^^RPL|^RPS", x = rownames(se), value = TRUE)
se$percent.ribo <- (Matrix::colSums(se@assays$RNA@counts[rp.genes, ])/Matrix::colSums(se@assays$RNA@counts))*100
```

percent.mito
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "percent.mito", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 2)

```

percent.ribo
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "percent.ribo", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 2)
```

nFeature_RNA
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "nFeature_RNA", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 2)
```

nCount_RNA
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "nCount_RNA", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 2)
```


Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```

Load OpenTargets gene sets
```{r class.source = 'fold-show'}
OpenTargets_T1D_Genetic_ <- as.character(t(read.table(file = "OpenTargets_gene_sets/Human_OpenTargets_T1DM_Genetic.csv")))

OpenTargets_T1D_Genetic_ <- OpenTargets_T1D_Genetic_[1:130]

all_genes <- unique(c(OpenTargets_T1D_Genetic_))

```


Select data from OT gene list
```{r}
mydata <- FetchData(se,vars=all_genes)
```


Create spearman correlation heat map
```{r}
cormat <- cor(mydata,method = c("spearman"))
melted_cormat <- reshape2::melt(cormat)
melted_cormat$value <- ifelse(melted_cormat$Var1 == melted_cormat$Var2, NA, melted_cormat$value)

```


```{r}
library(circlize)
col_fun = colorRamp2(c(-0.4, 0, 0.4), c("blue","white","red"))
col_fun(seq(-3, 3))
```


Complex Heatmaps
```{r, fig.height=20,fig.width=20}
set.seed(123)

myheatmap <-  Heatmap(cormat,name="Spearman\nCorrelation",row_names_gp = gpar(fontsize = 4),column_names_gp = gpar(fontsize = 4),clustering_method_columns = "complete",clustering_method_rows = "complete",show_row_dend = F,show_column_names = T,row_split = 3, column_split = 3,col = col_fun)

myheatmap
```



PDF
```{r, eval=FALSE}
pdf(file = "Spearman_gene_gene_correlation_genetic_top_T1D[pancreas_human_20PCW_S1].pdf", height = 20, width = 20)

myheatmap

dev.off()
```


Dendogram group 1/3
```{r, fig.height=4,fig.width=5}
ST.FeaturePlot(se, features = c("DLK1"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)

ST.FeaturePlot(se, features = c("CTRB1"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)

ST.FeaturePlot(se, features = c("CTRB2"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```


PDF
```{r, eval=FALSE}
pdf(file = "gene_expression_[pancreas_human_20PCW_S1]_INS.pdf", height = 4, width = 5)

ST.FeaturePlot(se, features = c("INS"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)

dev.off()
```


PDF
```{r, eval=FALSE}
pdf(file = "gene_expression_[pancreas_human_20PCW_S1]_CTRB1.pdf", height = 4, width = 5)

ST.FeaturePlot(se, features = c("CTRB1"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)

dev.off()
```


PDF
```{r, eval=FALSE}
pdf(file = "gene_expression_[pancreas_human_20PCW_S1]_CTRB2.pdf", height = 4, width = 5)

ST.FeaturePlot(se, features = c("CTRB2"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)

dev.off()
```



Dendogram group 2/3
```{r, fig.height=4,fig.width=5}
ST.FeaturePlot(se, features = c("INS"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("CPE"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```

Dendogram group 3/3
```{r, fig.height=4,fig.width=5}
ST.FeaturePlot(se, features = c("UBE2G1"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("HLA-DMB"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("LRRC32"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("ARHGAP12"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("NOTCH2"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("SMAD3"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("KLF3"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("ATM"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("MAPK1"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("HBP1"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("SLC25A37"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("C1QTNF6"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("RBPJ"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("ERBB3"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
ST.FeaturePlot(se, features = c("CCDC88B"), cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```


SessionInfo
```{r}
sessionInfo()
```

