---
title: "gsMap_STEAM_window50_SCZ_[adult_ACH003]"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

# Load and Normalize data

Load libraries:
```{r, message=FALSE}
library(STutility)
library(dplyr)
library(RColorBrewer)
library(scales)
library(reshape2)
library(corrplot)
library(lawstat)
library(MASS)
library(viridis)
library(STEAM)
```

Load ST data:
```{r}

infoTable <- read.csv("spatial_data/infoTable.csv", sep = ";")


se <- InputFromTable(infotable = infoTable, 
                      minUMICountsPerGene = 100, 
                      minSpotsPerGene = 5,
                      minUMICountsPerSpot = 500,
                      platform =  "Visium")

```


Load image:
```{r}
se <- LoadImages(se, time.resolve = FALSE)
```

View image:
```{r, fig.height=4, fig.width=5}
ImagePlot(se, method = "raster", annotate = FALSE)
```


# Spatial clusters  {.tabset}

Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```

Load cluster annotations
```{r}
seurat_clusters <- read.csv(file = "spatial_structures/seurat_clusters.csv", sep = ";")
```

Add annotations to seurat object
```{r}
rownames(seurat_clusters) <- seurat_clusters$Barcode
seurat_clusters$Barcode <- NULL
se$seurat_clusters <- seurat_clusters
se$seurat_clusters_plot <- as.factor(se$seurat_clusters) # For plotting of spatial structures
head(se[[]])
```

## Plot seurat_clusters
```{r, fig.height=4, fig.width=5}
n <- 7
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
col_vector[7] <- "deepskyblue"
  
col_vector <- col_vector[1:7]

se <- SetIdent(se, value = "seurat_clusters_plot")
ST.FeaturePlot(object = se, features = "seurat_clusters_plot", pt.size = 1, cols = col_vector)
```

## FeatureOverlay seurat_clusters
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1

FeatureOverlay(se, 
               features = c("seurat_clusters_plot"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = col_vector)
```




# OpenTargets gene sets

Load OpenTargets gene sets
```{r class.source = 'fold-show'}

gsMap_gene_list <- read.csv(file = "gsMap_diagnostic_info_human_heart_ACH003/human_heart_SCZ_Gene_Diagnostic_Info.csv")
gsMap_gene_list <- gsMap_gene_list[1:500,]
```


```{r}
OpenTargets_SCZ_Genetic_ <- gsMap_gene_list$Gene
head(OpenTargets_SCZ_Genetic_)
```



```{r}
# Extract gene names from the Seurat object
gene_names <- rownames(se)
length(gene_names)

# Check gene list size before filtering
length(OpenTargets_SCZ_Genetic_)

# Remove genes not present in the Seurat object from the gene lists
OpenTargets_SCZ_Genetic_ <- unique(OpenTargets_SCZ_Genetic_[OpenTargets_SCZ_Genetic_ %in% gene_names])

# Check gene list size after filtering
length(OpenTargets_SCZ_Genetic_)
```



# STEAM


```{r}
window_rank_list_SCZ_Genetic <- generate_sliding_windows(OpenTargets_SCZ_Genetic_, window_size = 50, step_size = 10, disease_abbr = "SCZ", ot_gene_set_label = "Genetic")
```


```{r}
all_gene_sets_OpenTargets <- list(OpenTargets_SCZ_Genetic_=OpenTargets_SCZ_Genetic_)
```


```{r}
all_gene_sets <- all_gene_sets_OpenTargets
all_gene_sets <- append(all_gene_sets,window_rank_list_SCZ_Genetic)
```


```{r}
score.mat <- matrix(data = NA, nrow = length(all_gene_sets), ncol = 1, dimnames = list(names(all_gene_sets), "% of genes present"))

for (i in 1:length(all_gene_sets)) {
  genes <- unlist(all_gene_sets[i]) 
  score.mat[i] <- mean(genes %in% rownames(se))
  se <- AddModuleScore(se,list(genes), ctrl = 100, name = list(names(all_gene_sets[i])))
}

score.mat*100
```



Load perm.mat from NULL gene sets
```{r class.source = 'fold-show'}
perm.mat.window.data <- readRDS(file = "Permutation_matrices/perm.mat_p10000_g50.RDS")
```


```{r}
#Example code on how to update cluster names if needed
cluster_names <- rep("", length(table(se$seurat_clusters)))
cluster_names <- paste0(cluster_names,as.character(0:(length(table(se$seurat_clusters))-1)))

colnames(perm.mat.window.data) <- cluster_names

perm.mat.window.data[1:5,1:5]
```


```{r}
perm.mat.window.data <- as.data.frame(perm.mat.window.data)

perm.mat.window.data <- setNames(
  lapply(as.list(perm.mat.window.data), identity),
  colnames(perm.mat.window.data)
)
```



```{r}
window_results.g <- window_rank_enrichment_analysis(
   se = se,
   perm.mat.window.data = perm.mat.window.data,
   window_rank_list = window_rank_list_SCZ_Genetic,
   ot_gene_set_label = "Genetic",
   disease_abbr = "SCZ",
   cluster_anno = "seurat_clusters",
   imputation = "dynamic"#,
   #log_file = "data/mouse_coronal/log_files/log_file_pval_mat_genetic_windows.txt"
 )

head(window_results.g)
```


```{r}
rank_plot_for_clusters(
   window_results = window_results.g,
   perm.mat.window = perm.mat.window.data,
   ylim = c(-0.3, 0.3)
 )
```


```{r}
rank_plot_for_clusters(
   window_results = window_results.g,
   perm.mat.window = perm.mat.window.data,
   clusters_to_plot = 1,
   ylim = c(-0.3, 0.3)
 )

```


```{r, eval=T}

pdf("STEAM_plots/gsMap_window50_top120genes_SCZ_cluster1.pdf", width = 5, height = 4)

rank_plot_for_clusters(
   window_results = window_results.g,
   perm.mat.window = perm.mat.window.data,
   clusters_to_plot = 1,
   ylim = c(-0.3, 0.3)
 )


dev.off()

```



```{r}
OpenTargets_SCZ_Genetic_topGenes_ <- OpenTargets_SCZ_Genetic_[1:120]
```


```{r}
all_gene_sets_OpenTargets_top <- list(OpenTargets_SCZ_Genetic_topGenes_=OpenTargets_SCZ_Genetic_topGenes_)
```


```{r}
score.mat.top <- matrix(data = NA, nrow = length(all_gene_sets_OpenTargets_top), ncol = 1, dimnames = list(names(all_gene_sets_OpenTargets_top), "% of genes present"))

for (i in 1:length(all_gene_sets_OpenTargets_top)) {
  genes <- unlist(all_gene_sets_OpenTargets_top[i]) 
  score.mat.top[i] <- mean(genes %in% rownames(se))
  se <- AddModuleScore(se,list(genes), ctrl = 100, name = list(names(all_gene_sets_OpenTargets_top[i])))
}

score.mat.top*100
```



Load perm.mat from NULL gene sets
```{r class.source = 'fold-show'}
perm.mat.genetic.top.data <- readRDS(file = "Permutation_matrices/perm.mat_p10000_g120.RDS")
```


```{r}
#Example code on how to update cluster names if needed
cluster_names <- rep("", length(table(se$seurat_clusters)))
cluster_names <- paste0(cluster_names,as.character(0:(length(table(se$seurat_clusters))-1)))
#cluster_names <- paste0("cluster_", cluster_names)

colnames(perm.mat.genetic.top.data) <- cluster_names

perm.mat.genetic.top.data[1:5,1:5]
```


```{r}
perm.mat.genetic.top.data <- as.data.frame(perm.mat.genetic.top.data)
perm.mat.genetic.top.data[1:5,1:5]
perm.mat.window.data <- as.data.frame(perm.mat.window.data)
perm.mat.window.data[1:5,1:5]
```

```{r}
colnames(perm.mat.window.data) <- cluster_names
perm.mat.window.data[1:5,1:5]
```



```{r}
pval_mat.top <- spatial_trait_enrichment_analysis(
   se = se,
   perm.mat.label.data = perm.mat.genetic.top.data,
   perm.mat.window.data = perm.mat.window.data,
   window_rank_list_abr_label = window_rank_list_SCZ_Genetic,
   gene_list = "OpenTargets_SCZ_Genetic_topGenes_1",
   cluster_anno = "seurat_clusters",
   imputation = "dynamic"#,
   #log_file = "data/mouse_coronal/log_files/log_file_pval_mat_genetic_top.txt"
 )

head(pval_mat.top)
```


```{r}
pval_mat.top <- as.data.frame(t(pval_mat.top$p_val_mat))
pval_mat.top$p.val.adj <- p.adjust(pval_mat.top$p.val, method = "bonferroni")
pval_mat.top <- t(pval_mat.top)

head(pval_mat.top)
```

```{r}
write.csv(pval_mat.top, file = "STEAM_plots/pval_mat.top120_window50_SCZ.csv")
```


```{r}
se$seurat_clusters <- as.numeric(as.character(se$seurat_clusters))
se$p.val.g.top <- se$seurat_clusters
se$p.val.adj.g.top <- se$seurat_clusters

clusters <- sort(unique(se$seurat_clusters))

for (i in clusters) {
  idx <- as.integer(i) + 1
  se$p.val.g.top[se$seurat_clusters == i] <- as.numeric(pval_mat.top[1, idx])
  se$p.val.adj.g.top[se$seurat_clusters == i] <- as.numeric(pval_mat.top[2, idx])
}
```


```{r}
se$seurat_clusters <- as.numeric(as.character(se$seurat_clusters))
se$neg.log10.p.val.g.top <- se$seurat_clusters
se$neg.log10.p.val.adj.g.top <- se$seurat_clusters

clusters <- sort(unique(se$seurat_clusters))

for (i in clusters) {
  idx <- as.integer(i) + 1
  se$neg.log10.p.val.g.top[se$seurat_clusters == i] <- -log10(as.numeric(pval_mat.top[1, idx]))
  se$neg.log10.p.val.adj.g.top[se$seurat_clusters == i] <- -log10(as.numeric(pval_mat.top[2, idx]))
}
```


```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(
  object = se,
  features = "neg.log10.p.val.adj.g.top",
  pt.size.factor = 2
) + scale_fill_viridis_c()
```



```{r, eval=T}

pdf("STEAM_plots/gsMap_Spatial_p.adj_SCZ_window50_top120genes.pdf", width = 5, height = 4)

ST.FeaturePlot(
  object = se,
  features = "neg.log10.p.val.adj.g.top",
  pt.size.factor = 2
) + scale_fill_viridis_c()

dev.off()

```


```{r}
library(ggplot2)
library(viridis)

# Convert matrix to data frame
df <- data.frame(
  cluster = colnames(pval_mat.top),
  p.val = as.numeric(pval_mat.top["p.val", ]),
  p.val.adj = as.numeric(pval_mat.top["p.val.adj", ])
)

# Transform p-values
df$log10_pval <- -log10(df$p.val)
df$log10_padj <- -log10(df$p.val.adj)

# Order clusters by significance (most significant = leftmost)
df$cluster <- factor(
  df$cluster,
  levels = df$cluster[order(df$p.val.adj, decreasing = FALSE)]
)

# Lollipop plot
p <- ggplot(df, aes(x = cluster, y = log10_padj, fill = log10_padj)) +
  
  # stems
  geom_segment(
    aes(
      x = cluster,
      xend = cluster,
      y = 0,
      yend = log10_padj
    ),
    color = "grey70",
    linewidth = 1
  ) +
  
  # points
  geom_point(
    shape = 21,
    size = 5,
    color = "black"
  ) +
  
  # significance threshold line at adjusted p = 0.05
  geom_hline(
    yintercept = -log10(0.05),
    color = "grey40",
    linetype = "dashed",
    linewidth = 1
  ) +
  
  scale_fill_viridis_c(
    option = "viridis",
    direction = 1,
    name = expression(-log[10]("p.adj"))
  ) +
  
  labs(
    x = "Spatial clusters",
    y = expression(-log[10]("p.adj")),
    title = "Spatial trait enrichment: SCZ"
  ) +
  
  theme_classic() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1
    )
  )

p
```



```{r, eval=T}

pdf("STEAM_plots/gsMap_Spatial_p.adj_SCZ_window50_top120genes_lollipop.pdf", width = 7, height = 4)

p

dev.off()

```


# Notes

Session info
```{r}
sessionInfo()
```

