---
title: "OpenTarget_gene_sets_sliding_window_selection_adult_brain_all_supercluster_term"
output: html_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---

Notes: Loads the Metacell dataset, runs SCTransform, and reads in the Open Targets trait data, and filter to only include genes present in the dataset.

Load libraries
```{r}
library(Seurat)
library(SeuratObject)
library(dplyr)
library(tidyverse)
```


Load SC se object:
```{r}
se <- readRDS("Seurat_objects/MetaCell.rds")
se
table(se$supercluster_term)
```


Collect QC metrics
```{r}
se[["percent.mt"]] <- PercentageFeatureSet(se, pattern = "^MT-")
se[["percent.rb"]] <- PercentageFeatureSet(se, pattern = "^RPL|^RPS")
```


Plot QC metrics
```{r, fig.width=10, fig.height=20}
VlnPlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "supercluster_term")
```


```{r, fig.width=10, fig.height=20}
RidgePlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "supercluster_term")
```



Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```


Save filtered and normalized se object
```{r, eval=FALSE}
saveRDS(se,file = "Seurat_objects/MetaCell_normalized.RDS")
```


Load normalized SC se object:
```{r}
se <- readRDS("Seurat_objects/MetaCell_normalized.RDS")
se
table(se$supercluster_term)
```


Load OpenTarget files: OBS! Update file location for relevant OpenTargets files
```{r}
get_opentarget <- function (opentarget_dir = paste0(getwd(),"/OpenTargets"), mouse_genes = NULL ){
  OT.files <- list()
  disease.names <- character()
  i <- 1
  column.names <- c("Gene_symbol","Overall_assoc.score","Genetic_assoc.","Somatic_mutation","Drugs","Pathways_system_biology","Text_mining","RNA_expression","Animal_models","Target_name")
  
  if (!is.null(mouse_genes)){
    

      conversion.table <- read.table(mouse_genes,
                                     sep = "\t",
                                     header = TRUE) 
      #if mouse_genes dataframe is specified, load it

  }
  
  for (OT.file in list.files(opentarget_dir)){
    if (grepl("diseases_", OT.file)){
      print(OT.file)
  
      df <- read.table(paste(opentarget_dir, OT.file, sep= "/"),
                     sep= "\t",
                     header=TRUE,
                     quote = "")
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
    
      
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
      
      if (!is.null(mouse_genes)){
        df$Gene_symbol <- conversion.table[match(df$Gene_symbol,conversion.table$hgnc_symbol),]$mgi_symbol #convert human to mouse annotation
        OT.files[[i]] <- df
        } else {
          OT.files[[i]] <- df
        }
      i <- i+1
      disease.name <- sub(".*diseases_","", OT.file)
      disease.name <- gsub(".tsv", "", disease.name)
      disease.names <- append(disease.names, disease.name)
    }
  }

  names(OT.files) <-  disease.names
  OT.files <- map(OT.files, ~.x %>%
                    distinct())
  return(OT.files)
}
```

OBS! Update file location for relevant OpenTargets files
```{r}
OpenTargets.path <- "OpenTargets/"
OT.files.human <-get_opentarget(opentarget_dir = OpenTargets.path)

```

#Clean out genes not present in the Seurat object AND removes duplicates
```{r, clean OT.files.human from duplicates}
OT.files.human <- map(OT.files.human, ~.x %>%
  dplyr::select(Gene_symbol, Overall_assoc.score, Genetic_assoc.,Drugs, Animal_models)%>%
  distinct() %>%
  filter(!is.na(Gene_symbol)&Gene_symbol %in% rownames(se)) %>%
    group_by(Gene_symbol)%>%
  slice(which.max(Overall_assoc.score))%>% #==> when there is a gene mentioned twice, only keep the row where the overall association score is the highest ==> reason for duplicates is that multiple human genes have the same mouse homolog etc...
    ungroup())

# saveRDS(OT.files.human, file = paste("OpenTargets", sample,"OT_files_list.rds", sep = "/"))


```


Gene sets for HUMAN
```{r, create gene sets from the }
all_gene_sets <- list()
list.names <- character()
i <- 1
j <- 1
for (df in OT.files.human){
  ## Genes overall association score
  GWAS_OpenTarget_Overall_assoc.score_xxx <- arrange(df, desc(Overall_assoc.score))
  GWAS_OpenTarget_Overall_assoc.score_xxx <- GWAS_OpenTarget_Overall_assoc.score_xxx[!is.na(GWAS_OpenTarget_Overall_assoc.score_xxx$Overall_assoc.score),]$Gene_symbol
  ## Genes genetic association score
  GWAS_OpenTarget_Genetic_assoc._xxx <- arrange(df, desc(Genetic_assoc.))
  GWAS_OpenTarget_Genetic_assoc._xxx <- GWAS_OpenTarget_Genetic_assoc._xxx[!is.na(GWAS_OpenTarget_Genetic_assoc._xxx$Genetic_assoc.),]$Gene_symbol
  print(length(GWAS_OpenTarget_Genetic_assoc._xxx))
  ## Genes drug target
  GWAS_OpenTarget_Drugs_xxx <- arrange(df, desc(Drugs))
  # print(dim(GWAS_OpenTarget_Drugs_xxx_top100_[!is.na("Drugs"),]))
  GWAS_OpenTarget_Drugs_xxx <- GWAS_OpenTarget_Drugs_xxx[!is.na(GWAS_OpenTarget_Drugs_xxx$Drugs),]$Gene_symbol
  all_gene_sets[[i]] <- unique(GWAS_OpenTarget_Overall_assoc.score_xxx)
  all_gene_sets[[i+1]] <- unique(GWAS_OpenTarget_Genetic_assoc._xxx)
  all_gene_sets[[i+2]] <- unique(GWAS_OpenTarget_Drugs_xxx)
  list.names <- append(list.names,(c(gsub("xxx", names(OT.files.human[j]),"GWAS_OpenTarget_Overall_assoc.score_xxx"),
                            gsub("xxx", names(OT.files.human[j]),"GWAS_OpenTarget_Genetic_assoc._xxx"),
                            gsub("xxx", names(OT.files.human[j]),"GWAS_OpenTarget_Drugs_xxx"))))
  j <- j+1
  i <- i+3
}
names(all_gene_sets) <- list.names
```


```{r, overlapping windows function}

splitWithOverlap <- function(vec, seg.length, move) {
  starts = seq(1, length(vec), by=move)
  ends   = starts + seg.length - 1
  ends[ends > length(vec)] = length(vec)

  lapply(1:length(starts), function(i) vec[starts[i]:ends[i]])
}
```


```{r, apply the splitWithOverlap function}
win.size <- 50
move.size <- 10
windows.list <- lapply(all_gene_sets, splitWithOverlap, seg.length = win.size, move = move.size)
```

BRAIN (Human): ASD
```{r}

#All
OpenTargets_ASD_Genetic <- unlist(all_gene_sets[2])
OpenTargets_ASD_Drugs <- unlist(all_gene_sets[3])

#Subset
window50_rank_list_ASD_Genetic <- windows.list[[2]]

#Re-name
Rank_names <- rep("ASD_Genetic_Rank", length(window50_rank_list_ASD_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ASD_Genetic) <- Rank_names

#Subset
window50_rank_list_ASD_Drugs <- windows.list[[3]]

#Re-name
Rank_names <- rep("ASD_Drugs_Rank", length(window50_rank_list_ASD_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ASD_Drugs) <- Rank_names


```


BRAIN (Human): ADHD
```{r}

#All
OpenTargets_ADHD_Genetic <- unlist(all_gene_sets[5])
OpenTargets_ADHD_Drugs <- unlist(all_gene_sets[6])

#Subset
window50_rank_list_ADHD_Genetic <- windows.list[[5]]

#Re-name
Rank_names <- rep("ADHD_Genetic_Rank", length(window50_rank_list_ADHD_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ADHD_Genetic) <- Rank_names

#Subset
window50_rank_list_ADHD_Drugs <- windows.list[[6]]

#Re-name
Rank_names <- rep("ADHD_Drugs_Rank", length(window50_rank_list_ADHD_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ADHD_Drugs) <- Rank_names


```


BRAIN (Human): ALZ
```{r}

#All
OpenTargets_ALZ_Genetic <- unlist(all_gene_sets[8])
OpenTargets_ALZ_Drugs <- unlist(all_gene_sets[9])

#Subset
window50_rank_list_ALZ_Genetic <- windows.list[[8]]

#Re-name
Rank_names <- rep("ALZ_Genetic_Rank", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ALZ_Genetic) <- Rank_names

#Subset
window50_rank_list_ALZ_Drugs <- windows.list[[9]]

#Re-name
Rank_names <- rep("ALZ_Drugs_Rank", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ALZ_Drugs) <- Rank_names


```

BRAIN (Human): BIP
```{r}

#All
OpenTargets_BIP_Genetic <- unlist(all_gene_sets[11])
OpenTargets_BIP_Drugs <- unlist(all_gene_sets[12])

#Subset
window50_rank_list_BIP_Genetic <- windows.list[[11]]

#Re-name
Rank_names <- rep("BIP_Genetic_Rank", length(window50_rank_list_BIP_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_BIP_Genetic) <- Rank_names

#Subset
window50_rank_list_BIP_Drugs <- windows.list[[12]]

#Re-name
Rank_names <- rep("BIP_Drugs_Rank", length(window50_rank_list_BIP_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_BIP_Drugs) <- Rank_names


```


BRAIN (Human): SCZ
```{r}

#All
OpenTargets_SCZ_Genetic <- unlist(all_gene_sets[14])
OpenTargets_SCZ_Drugs <- unlist(all_gene_sets[15])

#Subset
window50_rank_list_SCZ_Genetic <- windows.list[[14]]

#Re-name
Rank_names <- rep("SCZ_Genetic_Rank", length(window50_rank_list_SCZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_SCZ_Genetic) <- Rank_names

#Subset
window50_rank_list_SCZ_Drugs <- windows.list[[15]]

#Re-name
Rank_names <- rep("SCZ_Drugs_Rank", length(window50_rank_list_SCZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_SCZ_Drugs) <- Rank_names


```


Save: OBS OBS OBS!!! Make sure to update the name. If Human "OpenTargets_..." If Human "Human_OpenTargets_..."
```{r, eval=FALSE}

#ASD
write.table(OpenTargets_ASD_Genetic,file = "OpenTargets_gene_sets/Human_OpenTargets_ASD_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ASD_Drugs,file = "OpenTargets_gene_sets/Human_OpenTargets_ASD_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ASD_Genetic,file = "OpenTargets_windowLists/Human_window50_rank_list_ASD_Genetic.RDS")

saveRDS(window50_rank_list_ASD_Drugs,file = "OpenTargets_windowLists/Human_window50_rank_list_ASD_Drugs.RDS")


#ADHD
write.table(OpenTargets_ADHD_Genetic,file = "OpenTargets_gene_sets/Human_OpenTargets_ADHD_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ADHD_Drugs,file = "OpenTargets_gene_sets/Human_OpenTargets_ADHD_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ADHD_Genetic,file = "OpenTargets_windowLists/Human_window50_rank_list_ADHD_Genetic.RDS")

saveRDS(window50_rank_list_ADHD_Drugs,file = "OpenTargets_windowLists/Human_window50_rank_list_ADHD_Drugs.RDS")



#ALZ
write.table(OpenTargets_ALZ_Genetic,file = "OpenTargets_gene_sets/Human_OpenTargets_ALZ_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ALZ_Drugs,file = "OpenTargets_gene_sets/Human_OpenTargets_ALZ_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ALZ_Genetic,file = "OpenTargets_windowLists/Human_window50_rank_list_ALZ_Genetic.RDS")

saveRDS(window50_rank_list_ALZ_Drugs,file = "OpenTargets_windowLists/Human_window50_rank_list_ALZ_Drugs.RDS")


#BIP
write.table(OpenTargets_BIP_Genetic,file = "OpenTargets_gene_sets/Human_OpenTargets_BIP_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_BIP_Drugs,file = "OpenTargets_gene_sets/Human_OpenTargets_BIP_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_BIP_Genetic,file = "OpenTargets_windowLists/Human_window50_rank_list_BIP_Genetic.RDS")

saveRDS(window50_rank_list_BIP_Drugs,file = "OpenTargets_windowLists/Human_window50_rank_list_BIP_Drugs.RDS")


#SCZ
write.table(OpenTargets_SCZ_Genetic,file = "OpenTargets_gene_sets/Human_OpenTargets_SCZ_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_SCZ_Drugs,file = "OpenTargets_gene_sets/Human_OpenTargets_SCZ_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_SCZ_Genetic,file = "OpenTargets_windowLists/Human_window50_rank_list_SCZ_Genetic.RDS")

saveRDS(window50_rank_list_SCZ_Drugs,file = "OpenTargets_windowLists/Human_window50_rank_list_SCZ_Drugs.RDS")



```


SessionInfo
```{r}
sessionInfo()
```

