---
title: "pval_distribution_[significant_top_genes_and_drug_pvalues]_selected_tissue_trait_pairs"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Creates the plot for supplementary figure 8f, and calculates the pi1 statistics (nominal p-value distribution) for selected trait-tissue pairs, by calculating the proportion of the significant genetically enriched structures (based on the Open Targets top ranked genes) that are also enriched for drug targets


#Load libraries
```{r}
library(dplyr)
library(ggplot2)
```


#Load data
```{r}
pval_data <- read.csv(file="pval_distribution_[all_datasets]_summary_selected_tissue_trait_pairs.csv",sep = ";")
```


Subset to significant top Genes
```{r}
#subset top genes data
data_topGenes <- pval_data[grep("top", pval_data$gene_list),]

#subset to significant top genes (based on p.val.adj)
data_topGenes <- subset(data_topGenes, neg.log10.p.val.adj_genetic >= -log10(0.05))

#remove columns with drug data
data_topGenes <- data_topGenes[, !names(data_topGenes) %in% c("median.score_drugs","neg.log10.p.val_drugs","neg.log10.p.val.adj_drugs")]

```

Subset to drug data for the significant top Genes
```{r}
# select traits to get drug data from
patterns <- names(table(data_topGenes$trait))

# Combine patterns into a single regular expression
pattern_string <- paste(patterns, collapse = "|")

# Subset rows from pval_data where trait matches any of the patterns
data_topGenes_drugs <- pval_data[grepl(pattern_string, pval_data$trait), ]

# Remove row with topX_genes, the drug data was only computed for all_genes
data_topGenes_drugs <- data_topGenes_drugs[!grepl("top", data_topGenes_drugs$gene_list), ]

# Prepare for merging: remove columns and only save drug data and identifiers
data_topGenes_drugs <- data_topGenes_drugs[, names(data_topGenes_drugs) %in% c("dataset","trait","cluster","median.score_drugs","neg.log10.p.val_drugs","neg.log10.p.val.adj_drugs")]
```

Merge and remove N/A
```{r}
# Merge the data
pval_data_drugs_of_topGenes <- merge(data_topGenes,data_topGenes_drugs)

# Remove rows with N/A (some traits did not have drug associated genes on Open Targets)
pval_data_drugs_of_topGenes[pval_data_drugs_of_topGenes == "N/A"] <- NA
pval_data_drugs_of_topGenes <- na.omit(pval_data_drugs_of_topGenes)

```

Change p-value scale
```{r}
# change from character to numeric
pval_data_drugs_of_topGenes$neg.log10.p.val_drugs <- as.numeric(pval_data_drugs_of_topGenes$neg.log10.p.val_drugs)

# change/add new p-value scale to dataframe
pval_data_drugs_of_topGenes$p.val_drugs <- 10^(-pval_data_drugs_of_topGenes$neg.log10.p.val_drugs)
```

Plot
```{r}
theme_set(theme_classic())

# Color by groups
p1 <- ggplot(pval_data_drugs_of_topGenes, aes(x=p.val_drugs)) + 
                geom_histogram(alpha=1, color="black",position="identity", fill="grey") +
                ylab("trait-structure pairs")+
                xlab("p-values Drug targets") +
                ggtitle("Significant Genetic top") +
                ylim(0,200)+
                #coord_cartesian(ylim = c(0, 10))+
                theme_classic(base_size = 25)+
                theme(plot.title = element_text(size = 25))+
                geom_vline(xintercept = 0.05, linetype = "dashed", color = "red", size = 1)

p1
```

PDF
```{r, eval=FALSE}
pdf(file = "Fig_traits_with_significant_top_Genes_drug_targets_selected_tissue_trait_pairs.pdf", width=5,height=5)

p1

dev.off()
```


Estimate π1 with pi0est function from the qvalue package
```{r}
pi0_estimate <- pi0est(p=pval_data_drugs_of_topGenes$p.val_drugs, pi0.method = c("bootstrap"))
pi0_estimate

pi0 <- pi0_estimate$pi0
pi1 <- 1-pi0

pi1
```



#Notes
```{r}
sessionInfo()
```

