---
title: "OpenTarget_gene_sets_sliding_window_selection_brain_mouse_SC_allen_brain_atlas_random_250_subclass_label"
output: html_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---

Note: This script takes the downsampled mouse scRNA-seq dataset from allen brain atlas, filter out cells based on below gene, UMI, mitochondrial and ribosomal thresholds. Then reads in the Open Targets trait data, updates gene symbols from human to mouse and filter to only include genes present in the dataset.

Load libraries
```{r}
library(Seurat)
library(SeuratObject)
library(dplyr)
library(tidyverse)
```


Load SC se object:
```{r}
se <- readRDS("Seurat_objects/se_allen_brain_atlas_random_250_subclass_label.rds")
se
table(se$subclass_label)
```


Collect QC metrics
```{r}
se[["percent.mt"]] <- PercentageFeatureSet(se, pattern = "^mt-")
se[["percent.rb"]] <- PercentageFeatureSet(se, pattern = "^Rpl|^Rps")
```


Plot QC metrics
```{r, fig.width=10, fig.height=20}
VlnPlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "subclass_label")
```


```{r, fig.width=10, fig.height=20}
RidgePlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "subclass_label")
```


Filtering cells
```{r}
se
se <- subset(se, subset = nFeature_RNA > 200 & nFeature_RNA < 8000 & 
                    nCount_RNA > 500 & nCount_RNA < 35000 & 
                    percent.mt <= 10 & percent.rb <= 15)
se
```

Plot QC metrics
```{r, fig.width=10, fig.height=20}
VlnPlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "subclass_label")
```

```{r, fig.width=10, fig.height=20}
RidgePlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "subclass_label")
```

Filtering genes
```{r}
se
# Define a threshold for the total UMI count
min_umi <- 100

# Calculate the total UMIs per gene
gene_totals <- Matrix::rowSums(GetAssayData(se, slot = "counts"))

# Subset genes with total UMIs above the threshold
se <- subset(se, features = rownames(se)[gene_totals >= min_umi])
se
```


Plot QC metrics
```{r, fig.width=10, fig.height=20}
VlnPlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "subclass_label")
```

```{r, fig.width=10, fig.height=20}
RidgePlot(se, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 1, group.by = "subclass_label")
```


```{r}
table(se$subclass_label)
```




Save cluster annotations
```{r, eval=FALSE}
seurat_clusters <- as.data.frame(se$subclass_label)
seurat_clusters$Barcode <- colnames(se)
seurat_clusters$seurat_clusters <- seurat_clusters$`se$subclass_label`
seurat_clusters$`se$subclass_label` <- NULL

write.table(seurat_clusters,file="Seurat_objects/seurat_clusters.csv", col.names = T, row.names = F,quote = FALSE,sep = ";")
```

Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```


Save filtered and normalized se object
```{r, eval=FALSE}
saveRDS(se,file = "Seurat_objects/se_250_cells_filtered_normalized.RDS")
```


Load OpenTarget files: OBS! Update file location for relevant OpenTargets files
```{r}
get_opentarget <- function (opentarget_dir = paste0(getwd(),"/OpenTargets/"), mouse_genes = NULL ){
  OT.files <- list()
  disease.names <- character()
  i <- 1
  column.names <- c("Gene_symbol","Overall_assoc.score","Genetic_assoc.","Somatic_mutation","Drugs","Pathways_system_biology","Text_mining","RNA_expression","Animal_models","Target_name")
  
  if (!is.null(mouse_genes)){
    

      conversion.table <- read.table(mouse_genes,
                                     sep = "\t",
                                     header = TRUE) 
      #if mouse_genes dataframe is specified, load it

  }
  
  for (OT.file in list.files(opentarget_dir)){
    if (grepl("diseases_", OT.file)){
      print(OT.file)
  
      df <- read.table(paste(opentarget_dir, OT.file, sep= "/"),
                     sep= "\t",
                     header=TRUE,
                     quote = "")
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
    
      
    
      names(df) <- column.names  # rename columns
      
      df[df == "No data"] <- NA #Re-name N/A
      
      if (!is.null(mouse_genes)){
        df$Gene_symbol <- conversion.table[match(df$Gene_symbol,conversion.table$hgnc_symbol),]$mgi_symbol #convert human to mouse annotation
        OT.files[[i]] <- df
        } else {
          OT.files[[i]] <- df
        }
      i <- i+1
      disease.name <- sub(".*diseases_","", OT.file)
      disease.name <- gsub(".tsv", "", disease.name)
      disease.names <- append(disease.names, disease.name)
    }
  }

  names(OT.files) <-  disease.names
  OT.files <- map(OT.files, ~.x %>%
                    distinct())
  return(OT.files)
}
```

OBS! Update file location for relevant OpenTargets files
```{r}
OpenTargets.path <- "OpenTargets/"
OT.files <- get_opentarget( opentarget_dir = OpenTargets.path ,mouse_genes = "mouse_human_genes_feb_23.tsv")
OT.files.human <-get_opentarget(opentarget_dir = OpenTargets.path)

```

#Clean out genes not present in the Seurat object AND removes duplicates
```{r, clean OT.files from duplicates}
OT.files <- map(OT.files, ~.x %>%
  dplyr::select(Gene_symbol, Overall_assoc.score, Genetic_assoc.,Drugs, Animal_models)%>%
  distinct() %>%
  filter(!is.na(Gene_symbol)&Gene_symbol %in% rownames(se)) %>%
    group_by(Gene_symbol)%>%
  dplyr::slice(which.max(Overall_assoc.score))%>% #==> when there is a gene mentioned twice, only keep the row where the overall association score is the highest ==> reason for duplicates is that multiple human genes have the same mouse homolog etc...
    ungroup())

# saveRDS(OT.files, file = paste("OpenTargets", sample,"OT_files_list.rds", sep = "/"))


```

Gene sets for MOUSE
```{r, create gene sets from the }
all_gene_sets <- list()
list.names <- character()
i <- 1
j <- 1
for (df in OT.files){
  ## Genes overall association score
  GWAS_OpenTarget_Overall_assoc.score_xxx <- arrange(df, desc(Overall_assoc.score))
  GWAS_OpenTarget_Overall_assoc.score_xxx <- GWAS_OpenTarget_Overall_assoc.score_xxx[!is.na(GWAS_OpenTarget_Overall_assoc.score_xxx$Overall_assoc.score),]$Gene_symbol
  ## Genes genetic association score
  GWAS_OpenTarget_Genetic_assoc._xxx <- arrange(df, desc(Genetic_assoc.))
  GWAS_OpenTarget_Genetic_assoc._xxx <- GWAS_OpenTarget_Genetic_assoc._xxx[!is.na(GWAS_OpenTarget_Genetic_assoc._xxx$Genetic_assoc.),]$Gene_symbol
  print(length(GWAS_OpenTarget_Genetic_assoc._xxx))
  ## Genes drug target
  GWAS_OpenTarget_Drugs_xxx <- arrange(df, desc(Drugs))
  # print(dim(GWAS_OpenTarget_Drugs_xxx_top100_[!is.na("Drugs"),]))
  GWAS_OpenTarget_Drugs_xxx <- GWAS_OpenTarget_Drugs_xxx[!is.na(GWAS_OpenTarget_Drugs_xxx$Drugs),]$Gene_symbol
  all_gene_sets[[i]] <- unique(GWAS_OpenTarget_Overall_assoc.score_xxx)
  all_gene_sets[[i+1]] <- unique(GWAS_OpenTarget_Genetic_assoc._xxx)
  all_gene_sets[[i+2]] <- unique(GWAS_OpenTarget_Drugs_xxx)
  list.names <- append(list.names,(c(gsub("xxx", names(OT.files[j]),"GWAS_OpenTarget_Overall_assoc.score_xxx"),
                            gsub("xxx", names(OT.files[j]),"GWAS_OpenTarget_Genetic_assoc._xxx"),
                            gsub("xxx", names(OT.files[j]),"GWAS_OpenTarget_Drugs_xxx"))))
  j <- j+1
  i <- i+3
}
names(all_gene_sets) <- list.names
```


```{r, overlapping windows function}

splitWithOverlap <- function(vec, seg.length, move) {
  starts = seq(1, length(vec), by=move)
  ends   = starts + seg.length - 1
  ends[ends > length(vec)] = length(vec)

  lapply(1:length(starts), function(i) vec[starts[i]:ends[i]])
}
```


```{r, apply the splitWithOverlap function}
win.size <- 50
move.size <- 10
windows.list <- lapply(all_gene_sets, splitWithOverlap, seg.length = win.size, move = move.size)
```


BRAIN (Mouse): ASD
```{r}

#All
OpenTargets_ASD_Genetic <- unlist(all_gene_sets[2])
OpenTargets_ASD_Drugs <- unlist(all_gene_sets[3])

#Subset
window50_rank_list_ASD_Genetic <- windows.list[[2]]

#Re-name
Rank_names <- rep("ASD_Genetic_Rank", length(window50_rank_list_ASD_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ASD_Genetic) <- Rank_names

#Subset
window50_rank_list_ASD_Drugs <- windows.list[[3]]

#Re-name
Rank_names <- rep("ASD_Drugs_Rank", length(window50_rank_list_ASD_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ASD_Drugs) <- Rank_names


```


BRAIN (Mouse): ADHD
```{r}

#All
OpenTargets_ADHD_Genetic <- unlist(all_gene_sets[5])
OpenTargets_ADHD_Drugs <- unlist(all_gene_sets[6])

#Subset
window50_rank_list_ADHD_Genetic <- windows.list[[5]]

#Re-name
Rank_names <- rep("ADHD_Genetic_Rank", length(window50_rank_list_ADHD_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ADHD_Genetic) <- Rank_names

#Subset
window50_rank_list_ADHD_Drugs <- windows.list[[6]]

#Re-name
Rank_names <- rep("ADHD_Drugs_Rank", length(window50_rank_list_ADHD_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ADHD_Drugs) <- Rank_names


```


BRAIN (Mouse): ALZ
```{r}

#All
OpenTargets_ALZ_Genetic <- unlist(all_gene_sets[8])
OpenTargets_ALZ_Drugs <- unlist(all_gene_sets[9])

#Subset
window50_rank_list_ALZ_Genetic <- windows.list[[8]]

#Re-name
Rank_names <- rep("ALZ_Genetic_Rank", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ALZ_Genetic) <- Rank_names

#Subset
window50_rank_list_ALZ_Drugs <- windows.list[[9]]

#Re-name
Rank_names <- rep("ALZ_Drugs_Rank", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_ALZ_Drugs) <- Rank_names


```

BRAIN (Mouse): BIP
```{r}

#All
OpenTargets_BIP_Genetic <- unlist(all_gene_sets[11])
OpenTargets_BIP_Drugs <- unlist(all_gene_sets[12])

#Subset
window50_rank_list_BIP_Genetic <- windows.list[[11]]

#Re-name
Rank_names <- rep("BIP_Genetic_Rank", length(window50_rank_list_BIP_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_BIP_Genetic) <- Rank_names

#Subset
window50_rank_list_BIP_Drugs <- windows.list[[12]]

#Re-name
Rank_names <- rep("BIP_Drugs_Rank", length(window50_rank_list_BIP_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_BIP_Drugs) <- Rank_names


```


BRAIN (Mouse): SCZ
```{r}

#All
OpenTargets_SCZ_Genetic <- unlist(all_gene_sets[14])
OpenTargets_SCZ_Drugs <- unlist(all_gene_sets[15])

#Subset
window50_rank_list_SCZ_Genetic <- windows.list[[14]]

#Re-name
Rank_names <- rep("SCZ_Genetic_Rank", length(window50_rank_list_SCZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_SCZ_Genetic) <- Rank_names

#Subset
window50_rank_list_SCZ_Drugs <- windows.list[[15]]

#Re-name
Rank_names <- rep("SCZ_Drugs_Rank", length(window50_rank_list_SCZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))
Rank_names <- paste0(Rank_names,sep="_")
names(window50_rank_list_SCZ_Drugs) <- Rank_names


```



Save: OBS OBS OBS!!! Make sure to update the name. If Human "OpenTargets_..." If Mouse "Mouse_OpenTargets_..."
```{r, eval=FALSE}

#ASD
write.table(OpenTargets_ASD_Genetic,file = "OpenTargets_gene_sets/Mouse_OpenTargets_ASD_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ASD_Drugs,file = "OpenTargets_gene_sets/Mouse_OpenTargets_ASD_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ASD_Genetic,file = "OpenTargets_windowLists/Mouse_window50_rank_list_ASD_Genetic.RDS")

saveRDS(window50_rank_list_ASD_Drugs,file = "OpenTargets_windowLists/Mouse_window50_rank_list_ASD_Drugs.RDS")


#ADHD
write.table(OpenTargets_ADHD_Genetic,file = "OpenTargets_gene_sets/Mouse_OpenTargets_ADHD_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ADHD_Drugs,file = "OpenTargets_gene_sets/Mouse_OpenTargets_ADHD_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ADHD_Genetic,file = "OpenTargets_windowLists/Mouse_window50_rank_list_ADHD_Genetic.RDS")

saveRDS(window50_rank_list_ADHD_Drugs,file = "OpenTargets_windowLists/Mouse_window50_rank_list_ADHD_Drugs.RDS")



#ALZ
write.table(OpenTargets_ALZ_Genetic,file = "OpenTargets_gene_sets/Mouse_OpenTargets_ALZ_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_ALZ_Drugs,file = "OpenTargets_gene_sets/Mouse_OpenTargets_ALZ_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_ALZ_Genetic,file = "OpenTargets_windowLists/Mouse_window50_rank_list_ALZ_Genetic.RDS")

saveRDS(window50_rank_list_ALZ_Drugs,file = "OpenTargets_windowLists/Mouse_window50_rank_list_ALZ_Drugs.RDS")


#BIP
write.table(OpenTargets_BIP_Genetic,file = "OpenTargets_gene_sets/Mouse_OpenTargets_BIP_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_BIP_Drugs,file = "OpenTargets_gene_sets/Mouse_OpenTargets_BIP_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_BIP_Genetic,file = "OpenTargets_windowLists/Mouse_window50_rank_list_BIP_Genetic.RDS")

saveRDS(window50_rank_list_BIP_Drugs,file = "OpenTargets_windowLists/Mouse_window50_rank_list_BIP_Drugs.RDS")


#SCZ
write.table(OpenTargets_SCZ_Genetic,file = "OpenTargets_gene_sets/Mouse_OpenTargets_SCZ_Genetic.csv", row.names = F, col.names = F)

write.table(OpenTargets_SCZ_Drugs,file = "OpenTargets_gene_sets/Mouse_OpenTargets_SCZ_Drugs.csv", row.names = F, col.names = F)

saveRDS(window50_rank_list_SCZ_Genetic,file = "OpenTargets_windowLists/Mouse_window50_rank_list_SCZ_Genetic.RDS")

saveRDS(window50_rank_list_SCZ_Drugs,file = "OpenTargets_windowLists/Mouse_window50_rank_list_SCZ_Drugs.RDS")



```


SessionInfo
```{r}
sessionInfo()
```

