---
title: 'Step5.Run_STEAM_ASD'
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: readable
vignette: >
  %\VignetteIndexEntry{My Standalone Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



# Load libraries

Load the necessary libraries.
```{r, message=FALSE, warning=FALSE}
library(Seurat)
library(SeuratObject)
library(dplyr)
library(MASS)
library(viridis)
library(stringr)
library(ggplot2)
library(readr)
library(steam)
```


# Load data


Load Seurat object.
```{r}
se <- readRDS("Seurat_objects/Metacell_normalized.rds")
se
head(se[[]])
```




Load ranked gene lists (here from Open Targets). Please note that it is essential for downstream analysis that the gene lists are ranked from this point forward to do empirical selection of top genetic genes.
```{r class.source = 'fold-show'}

OpenTargets_ASD_Genetic_ <- as.character(t(read.table(file = "OpenTargets_gene_sets/Human_OpenTargets_ASD_Genetic.csv")))
length(OpenTargets_ASD_Genetic_)

```


# Prepare data for STEAM analysis


Filter out genes not present in the Seurat object.
```{r}
# Extract gene names from the Seurat object
gene_names <- rownames(se)

# Remove genes not present in the Seurat object from the gene lists
OpenTargets_ASD_Genetic_ <- unique(OpenTargets_ASD_Genetic_[OpenTargets_ASD_Genetic_ %in% gene_names])
length(OpenTargets_ASD_Genetic_)
```


Generate sliding window gene sets from gene lists. Select your choice of trait abbreviation (disease_abbr) and a gene list descriptive term (ot_gene_set_label). We select a window size of 50 genes, moving by 10 genes for each window.
```{r}
window_rank_list_ASD_Genetic <- generate_sliding_windows(OpenTargets_ASD_Genetic_, window_size = 50, step_size = 10, disease_abbr = "ASD", ot_gene_set_label = "Genetic")
```


Add gene sets to a list.
```{r}
all_gene_sets_OpenTargets <- list(OpenTargets_ASD_Genetic_=OpenTargets_ASD_Genetic_)
```


Merge all gene sets into one list.
```{r}
all_gene_sets <- all_gene_sets_OpenTargets
all_gene_sets <- append(all_gene_sets,window_rank_list_ASD_Genetic)
```


Calculate the average gene expression per gene list and check the percentage of genes present in the Seurat object. It is important that all genes used are present in the Seurat object, otherwise the downstream statistic assumptions are invalid.
```{r}
score.mat <- matrix(data = NA, nrow = length(all_gene_sets), ncol = 1, dimnames = list(names(all_gene_sets), "% of genes present"))

for (i in 1:length(all_gene_sets)) {
  genes <- unlist(all_gene_sets[i]) 
  score.mat[i] <- mean(genes %in% rownames(se))
  se <- AddModuleScore(se,list(genes), ctrl = 100, name = list(names(all_gene_sets[i])))
}

score.mat*100
```


```{r}
VlnPlot(se, features = c("OpenTargets_ASD_Genetic_1"), ncol = 1, group.by = "cluster_anno")
VlnPlot(se, features = c("ASD_Genetic_Rank1_1"), ncol = 1, group.by = "cluster_anno")
VlnPlot(se, features = c("ASD_Genetic_Rank2_1"), ncol = 1, group.by = "cluster_anno")
```

Load permutation matrices for your selected window size and genetic gene list (see separate vignette on how to generate these). OBS! Make sure that you create the Seurat object in the same way (package and filtering) when generating permutation matrices as when you run STEAM.
```{r}

perm_files <- c(
  "Permutation_matrices/perm.mat.par_p10000_g50.rds"
)

perm_matrices <- load_permutation_matrices(perm_files)
perm.mat.window.data <- as.data.frame(perm_matrices[[1]])

perm.mat.window.data[1:5,1:5]
```



# Empirical selection of top genetic genes


Derive an empirical threshold for top genes of a ranked gene list by comparing the ranked window gene set signal to a null gene set of equal size.
```{r}
 window_results.g <- window_rank_enrichment_analysis(
   se = se,
   perm.mat.window.data = perm.mat.window.data,
   window_rank_list = window_rank_list_ASD_Genetic,
   ot_gene_set_label = "Genetic",
   disease_abbr = "ASD",
   cluster_anno = "cluster_anno",
   imputation = "all"#,
   #log_file = "data/Data_brain_example/log_files/log_file_pval_mat_genetic_window_SC_ASD.txt"
 )

head(window_results.g)
```


Plot median scores for each window in each cluster. Use these to identify sets of top genes. The lines represent the null distribution where, blue line = median, bright red = 95-quantile, dark red = max value. Here we see that for several clusters the top 3 windows have signal above the max value, and we know the window size is 50 and moves by 10. Thus, we select the top 70 genes in this list to be our top set of genes.
```{r}
 rank_plot_for_clusters(
   window_results = window_results.g,
   perm.mat.window = perm.mat.window.data,
   ylim = c(-0.1, 0.3)
 )
```


# Plot sliding window enrichment


Do multiple correction of p-values based on number of windows.
```{r}
window_results.g$p_value.adj <- p.adjust(window_results.g$p_value,method = "BH")
```


Add stars for plotting based on p_value.adj.
```{r}
window_results.g <- window_results.g%>%
  mutate(significance.level = ifelse(p_value.adj < 0.001, "***",
                     ifelse(p_value.adj < 0.01, "**",
                     ifelse(p_value.adj < 0.05, "*",
                     ""))))


window_results.g <- window_results.g%>%
  mutate(significant = ifelse(p_value.adj < 0.05, "TRUE",
                     "FALSE"))


head(window_results.g)
```


Update cluster names in the cluster column.
```{r}
window_results.g$cluster <- gsub("^cluster_", "", window_results.g$cluster)
```


Plot window_rank_enrichment_analysis results.
```{r, fig.width=30, fig.height=30}

# Set the order of window based on the original order of rbind
window_results.g$window <- factor(window_results.g$window, 
                                     rev(unique(window_results.g$window)))


# Create the plot
p_all <- window_results.g %>%
  ggplot(aes(x = cluster, y = window)) +
  geom_tile(aes(fill = -log10(p_value.adj)), colour = "grey20") +  # Fill with adjusted p-value
  geom_text(data = window_results.g %>% filter(significant == TRUE),
            aes(label = significance.level),
            vjust = 0.75,
            size = 10,
            fontface = "bold") +
  theme(
    legend.key.width = unit(1.5, "cm"),
    legend.key.height = unit(1.5, "cm"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 40),
    axis.text.y = element_text(size = 15),axis.title.x = element_text(size = 40, face = "bold"),axis.title.y = element_text(size = 40, face = "bold"),plot.title = element_text(size = 50, face = "bold"),legend.title = element_text(size = 40),legend.text = element_text(size = 40)
  ) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 22)) +
  coord_fixed(ratio = 0.25) +  # May need to adjust or remove if you want free y scaling
  labs(title = "All genetically associated ASD genes",x = "Cluster", y = "Window rank", fill = "-log10(adj p-value) \n Benjamini & Hochberg") +
  scale_fill_viridis_c(begin = 0.2, option = "viridis") +
  scale_color_manual(values = c("*" = "white", "**" = "white", "***" = "white"),  
                     labels = c("***" = "***  p < 0.001", "**" = "**  p < 0.01", "*" = "*  p < 0.05"),
                     guide = guide_legend(override.aes = list(shape = c(21, 21, 23),
                                                              fill = c("white", "white", "white"),
                                                              size = 4)))

p_all
```


PDF
```{r, eval=FALSE}
pdf(file = "STEAM_plots/WindowRankEnrichmentPlot_ASD_adult.pdf", height = 50, width = 50)

p_all

dev.off()
```


# Fisher's exact test


Load DEGs data.
```{r}
DEG_genes <- read_csv2("DEG_output/DE_genes.csv")
DEG_genes <- as.data.frame(DEG_genes)
DEG_genes$p_val_adj <- as.numeric(DEG_genes$p_val_adj)
DEG_genes <- subset(DEG_genes, subset = p_val_adj <= 0.05) # using only significant DEG
```


Subset to select the top ranked genes.
```{r}
OpenTargets_ASD_Genetic_top <- OpenTargets_ASD_Genetic_[1:70]
length(OpenTargets_ASD_Genetic_top)
```


Run Fisher's exact test.
```{r}
fisher_results <- run_fisher_test_degs(se, DEG_genes = DEG_genes, OT_genes = OpenTargets_ASD_Genetic_top)
fisher_results
```


Save results
```{r, eval=T}
write.table(fisher_results,file="STEAM_results/STEAM_fisher_results_top_genes_ASD.csv", col.names = T, row.names = F,quote = FALSE,sep = ";")
```


Plot results.
```{r, fig.height=5, fig.width=8}
# Ensure clusters are ordered by significance
fisher_results$cluster <- factor(fisher_results$cluster, 
                                 levels = fisher_results$cluster[order(fisher_results$adj_p_value)])

# Create the updated plot with viridis scale
p1 <- ggplot(fisher_results, aes(x = cluster, color = -log10(p_value), y = -log10(adj_p_value), size = odds_ratio)) +
  geom_point() +  
  geom_hline(yintercept = -log10(0.05), linetype = "dashed", color = "gray50") +  
  scale_color_viridis(option = "D", direction = 1, name = "-log10(p-value)") +  # Use Viridis color scale
  scale_size_continuous(range = c(2, 8), name = "Odds ratio") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 1,size = 14),axis.text.y = element_text(size = 14),axis.title.x = element_text(size = 16, face = "bold"),axis.title.y = element_text(size = 16, face = "bold"),plot.title = element_text(size = 18, face = "bold"),legend.title = element_text(size = 14),legend.text = element_text(size = 12)) +  
  labs(title = "Enrichment of top genetically associated ASD genes",
       x = "Spatial structures",
       y = "-log10(adj p-value)") +
  guides(color = guide_colorbar(order = 1), size = guide_legend(order = 2))

p1
```


PDF
```{r, eval=FALSE}
pdf(file = "STEAM_plots/fishers_exact_test_DEGup_topSTEAM_ASD.pdf", height = 5, width = 8)

p1

dev.off()
```


Run Fisher's exact test.
```{r}
fisher_results <- run_fisher_test_degs(se, DEG_genes = DEG_genes, OT_genes = OpenTargets_ASD_Genetic_)
fisher_results
```


Plot results.
```{r, fig.height=5, fig.width=8}
# Ensure clusters are ordered by significance
fisher_results$cluster <- factor(fisher_results$cluster, 
                                 levels = fisher_results$cluster[order(fisher_results$adj_p_value)])

# Create the updated plot with viridis scale
p2 <- ggplot(fisher_results, aes(x = cluster, color = -log10(p_value), y = -log10(adj_p_value), size = odds_ratio)) +
  geom_point() +  
  geom_hline(yintercept = -log10(0.05), linetype = "dashed", color = "gray50") +  
  scale_color_viridis(option = "D", direction = 1, name = "-log10(p-value)") +  # Use Viridis color scale
  scale_size_continuous(range = c(2, 8), name = "Odds ratio") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 1,size = 14),axis.text.y = element_text(size = 14),axis.title.x = element_text(size = 16, face = "bold"),axis.title.y = element_text(size = 16, face = "bold"),plot.title = element_text(size = 18, face = "bold"),legend.title = element_text(size = 14),legend.text = element_text(size = 12)) +  
  labs(title = "Enrichment of all genetically associated ASD genes",
       x = "Spatial structures",
       y = "-log10(adj p-value)") +
  guides(color = guide_colorbar(order = 1), size = guide_legend(order = 2))

p2
```


PDF
```{r, eval=FALSE}
pdf(file = "STEAM_plots/fishers_exact_test_DEGup_all_ASD.pdf", height = 5, width = 8)

p2

dev.off()
```





<details>
  <summary>Click to show Session Info</summary>

```{r}
sessionInfo()
```

</details>

