---
title: "spatial_structures_[10X_Visium_mouse_brain_coronal]"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

NOTE: Example code for determining the spatial substructures. All datasets were processed with the same approach. The number or NNMF factors and which were used for determining the spatial substructures can be found for each dataset in Supplementary Table 5. The final substructure annotations can be found in Supplementary Table 2, and the differentially expressed genes for each substructure in Supplementary Table 3.

# Load and Normalize data

Load libraries:
```{r, message=FALSE}
library(STutility)
library(dplyr)
library(RColorBrewer)
library(scales)
library(reshape2)
```

Load ST data:
```{r}

infoTable <- read.csv("spatial_data/infoTable.csv", sep = ";")


se <- InputFromTable(infotable = infoTable, 
                      minUMICountsPerGene = 100, 
                      minSpotsPerGene = 5,
                      minUMICountsPerSpot = 500,
                      platform =  "Visium")

```


Load image:
```{r}
se <- LoadImages(se, time.resolve = FALSE)
```

View image:
```{r, fig.width=5, fig.height=4}
ImagePlot(se, method = "raster", annotate = F)
```

# QC plots  {.tabset}

QC metrics se:
```{r}
# Collect all genes coded on the mitochondrial genome
mt.genes <- grep(pattern = "^mt-", x = rownames(se), value = TRUE)
se$percent.mito <- (Matrix::colSums(se@assays$RNA@counts[mt.genes, ])/Matrix::colSums(se@assays$RNA@counts))*100

# Collect all genes coding for ribosomal proteins
rp.genes <- grep(pattern = "^Rpl|^Rps", x = rownames(se), value = TRUE)
se$percent.ribo <- (Matrix::colSums(se@assays$RNA@counts[rp.genes, ])/Matrix::colSums(se@assays$RNA@counts))*100
```

## percent.mito
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "percent.mito", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)

```

## percent.ribo
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "percent.ribo", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```

## nFeature_RNA
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "nFeature_RNA", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```

## nCount_RNA
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "nCount_RNA", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```


Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```

# NNMF, Clustering & Spatial plot   {.tabset}

non-negative matrix factorization (NNMF)
```{r}
se <- RunNMF(se, nfactors = 40)
```

## NMF factors 

Factors to not include (nmf 40): 23 and 40 not spatially specific, 33 driven by HB genes. These will not be included in downstream analysis. Include: c(1:22,24:32,34:39) 

Plot factors: 
```{r}
cscale <- c("darkblue", "cyan", "yellow", "red", "darkred")

ST.DimPlot(se, 
           dims = 1:10,
           ncol = 4, # Sets the number of columns at dimensions level
           grid.ncol = 4, # Sets the number of columns at sample level
           reduction = "NMF", 
           dark.theme = T, 
           pt.size = 0.5, 
           center.zero = F, 
           cols = cscale)

ST.DimPlot(se, 
           dims = 11:20,
           ncol = 4, # Sets the number of columns at dimensions level
           grid.ncol = 4, # Sets the number of columns at sample level
           reduction = "NMF", 
           dark.theme = T, 
           pt.size = 0.5, 
           center.zero = F, 
           cols = cscale)

ST.DimPlot(se, 
           dims = 21:30,
           ncol = 4, # Sets the number of columns at dimensions level
           grid.ncol = 4, # Sets the number of columns at sample level
           reduction = "NMF", 
           dark.theme = T, 
           pt.size = 0.5, 
           center.zero = F, 
           cols = cscale)

ST.DimPlot(se, 
           dims = 31:40,
           ncol = 4, # Sets the number of columns at dimensions level
           grid.ncol = 4, # Sets the number of columns at sample level
           reduction = "NMF", 
           dark.theme = T, 
           pt.size = 0.5, 
           center.zero = F, 
           cols = cscale)

```

## FactorGeneLoadingPlot

Check gene contribution of all factors:
```{r}
FactorGeneLoadingPlot(se, factor = 1)
FactorGeneLoadingPlot(se, factor = 2)
FactorGeneLoadingPlot(se, factor = 3)
FactorGeneLoadingPlot(se, factor = 4)
FactorGeneLoadingPlot(se, factor = 5)
FactorGeneLoadingPlot(se, factor = 6)
FactorGeneLoadingPlot(se, factor = 7)
FactorGeneLoadingPlot(se, factor = 8)
FactorGeneLoadingPlot(se, factor = 9)
FactorGeneLoadingPlot(se, factor = 10)
FactorGeneLoadingPlot(se, factor = 11)
FactorGeneLoadingPlot(se, factor = 12)
FactorGeneLoadingPlot(se, factor = 13)
FactorGeneLoadingPlot(se, factor = 14)
FactorGeneLoadingPlot(se, factor = 15)
FactorGeneLoadingPlot(se, factor = 16)
FactorGeneLoadingPlot(se, factor = 17)
FactorGeneLoadingPlot(se, factor = 18)
FactorGeneLoadingPlot(se, factor = 19)
FactorGeneLoadingPlot(se, factor = 20)
FactorGeneLoadingPlot(se, factor = 21)
FactorGeneLoadingPlot(se, factor = 22)
FactorGeneLoadingPlot(se, factor = 23)
FactorGeneLoadingPlot(se, factor = 24)
FactorGeneLoadingPlot(se, factor = 25)
FactorGeneLoadingPlot(se, factor = 26)
FactorGeneLoadingPlot(se, factor = 27)
FactorGeneLoadingPlot(se, factor = 28)
FactorGeneLoadingPlot(se, factor = 29)
FactorGeneLoadingPlot(se, factor = 30)
FactorGeneLoadingPlot(se, factor = 31)
FactorGeneLoadingPlot(se, factor = 32)
FactorGeneLoadingPlot(se, factor = 33)
FactorGeneLoadingPlot(se, factor = 34)
FactorGeneLoadingPlot(se, factor = 35)
FactorGeneLoadingPlot(se, factor = 36)
FactorGeneLoadingPlot(se, factor = 37)
FactorGeneLoadingPlot(se, factor = 38)
FactorGeneLoadingPlot(se, factor = 39)
FactorGeneLoadingPlot(se, factor = 40)
```

## Clustering

Shared Nearest Neighbor (SSN) Graph
```{r class.source = 'fold-show'}
se <- FindNeighbors(object = se, verbose = FALSE, reduction = "NMF", dims = c(1:22,24:32,34:39))
```

Clustering using a modularity optimizer 
```{r class.source = 'fold-show'}
se <- FindClusters(object = se, verbose = FALSE)
```

col_vector
```{r}
n <- 19
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
col_vector[6] <- "black"
col_vector[8] <- "lightpink"
col_vector[10] <- "firebrick1"
col_vector[11] <- "darkmagenta"
col_vector[14] <- "darkorange2"
col_vector[18] <- "deepskyblue"
```

## Cluster split

```{r}
ST.FeaturePlot(object = se, features = "seurat_clusters", pt.size = 0.5, split.labels = T, indices = 1, show.sb = FALSE, ncol = 5, cols = col_vector)
```

Save cluster annotations
```{r, eval=FALSE}
seurat_clusters <- as.data.frame(se$seurat_clusters)
seurat_clusters$Barcode <- colnames(se)
seurat_clusters$seurat_clusters <- seurat_clusters$`se$seurat_clusters`
seurat_clusters$`se$seurat_clusters` <- NULL

write.table(seurat_clusters,file="spatial_structures/seurat_clusters.csv", col.names = T, row.names = F,quote = FALSE,sep = ";")
```


## Spatial plots

Spatial plot
```{r, fig.width=10, fig.height=8}
ST.FeaturePlot(object = se, features = "seurat_clusters", pt.size = 2, cols = col_vector)
```

Spatial plot
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(object = se, features = "seurat_clusters", pt.size = 1, cols = col_vector)
```


FeatureOverlay:
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.9
point.size = 1

FeatureOverlay(se, 
               features = c("seurat_clusters"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               cols = col_vector)

```


# DEGs & UMAP

DE analysis, for all clusters

```{r}
DefaultAssay(se) <- "RNA"
se <- se %>%
  NormalizeData() %>%
  ScaleData() 

se <- SetIdent(se, value = "seurat_clusters")
N.markers <- FindAllMarkers(se, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25,slot = "data")
```

Save N.markers
```{r, eval=FALSE}
write.table(N.markers,file="spatial_structures/DE_genes.csv", col.names = T, row.names = F,quote = FALSE,sep = ";")

```


Select top genes to plot
```{r}
topGenes <- N.markers %>% 
            group_by(cluster) %>% 
            arrange(cluster,p_val_adj) %>%
            slice_head(n=10)
topGenes
```

UMAP
```{r}
se <- RunUMAP(se, reduction = "NMF", dims = c(1:22,24:32,34:39), n.neighbors = 10)
```

UMAP clusters
```{r}
DimPlot(se, reduction = "umap", label = T,label.size = 4,cols = col_vector)
```


Subset
```{r}
cluster0_marker_topGenes <- as.character(t(subset(topGenes,cluster==0, select = gene)))
cluster1_marker_topGenes <- as.character(t(subset(topGenes,cluster==1, select = gene)))
cluster2_marker_topGenes <- as.character(t(subset(topGenes,cluster==2, select = gene)))
cluster3_marker_topGenes <- as.character(t(subset(topGenes,cluster==3, select = gene)))
cluster4_marker_topGenes <- as.character(t(subset(topGenes,cluster==4, select = gene)))
cluster5_marker_topGenes <- as.character(t(subset(topGenes,cluster==5, select = gene)))
cluster6_marker_topGenes <- as.character(t(subset(topGenes,cluster==6, select = gene)))
cluster7_marker_topGenes <- as.character(t(subset(topGenes,cluster==7, select = gene)))
cluster8_marker_topGenes <- as.character(t(subset(topGenes,cluster==8, select = gene)))
cluster9_marker_topGenes <- as.character(t(subset(topGenes,cluster==9, select = gene)))
cluster10_marker_topGenes <- as.character(t(subset(topGenes,cluster==10, select = gene)))
cluster11_marker_topGenes <- as.character(t(subset(topGenes,cluster==11, select = gene)))
cluster12_marker_topGenes <- as.character(t(subset(topGenes,cluster==12, select = gene)))
cluster13_marker_topGenes <- as.character(t(subset(topGenes,cluster==13, select = gene)))
cluster14_marker_topGenes <- as.character(t(subset(topGenes,cluster==14, select = gene)))
cluster15_marker_topGenes <- as.character(t(subset(topGenes,cluster==15, select = gene)))
cluster16_marker_topGenes <- as.character(t(subset(topGenes,cluster==16, select = gene)))
cluster17_marker_topGenes <- as.character(t(subset(topGenes,cluster==17, select = gene)))
cluster18_marker_topGenes <- as.character(t(subset(topGenes,cluster==18, select = gene)))
```

# Marker genes  {.tabset}

UMAP and Spatial visualization of top markers for each cluster

## cluster 0
```{r, fig.height=6, fig.width=9}
# Define colors for heatmap
heatmap.colors <- c("lightgray", "mistyrose", "red", "darkred", "black")


# cluster 0
FeaturePlot(se, features = cluster0_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster0_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 1
```{r, fig.height=6, fig.width=9}
# cluster 1
FeaturePlot(se, features = cluster1_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster1_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)
```

## cluster 2
```{r, fig.height=6, fig.width=9}
# cluster 2
FeaturePlot(se, features = cluster2_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster2_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)
```

## cluster 3
```{r, fig.height=6, fig.width=9}
# cluster 3
FeaturePlot(se, features = cluster3_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster3_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)
```

## cluster 4
```{r, fig.height=6, fig.width=9}
# cluster 4
FeaturePlot(se, features = cluster4_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster4_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 5
```{r, fig.height=6, fig.width=9}
# cluster 5
FeaturePlot(se, features = cluster5_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster5_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 6
```{r, fig.height=6, fig.width=9}
# cluster 6
FeaturePlot(se, features = cluster6_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster6_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 7
```{r, fig.height=6, fig.width=9}
# cluster 7
FeaturePlot(se, features = cluster7_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster7_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 8
```{r, fig.height=6, fig.width=9}
# cluster 8
FeaturePlot(se, features = cluster8_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster8_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 9
```{r, fig.height=6, fig.width=9}
# cluster 9
FeaturePlot(se, features = cluster9_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster9_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 10
```{r, fig.height=6, fig.width=9}
# cluster 10
FeaturePlot(se, features = cluster10_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster10_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 11
```{r, fig.height=6, fig.width=9}
# cluster 11
FeaturePlot(se, features = cluster11_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster11_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 12
```{r, fig.height=6, fig.width=9}
# cluster 12
FeaturePlot(se, features = cluster12_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster12_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 13
```{r, fig.height=6, fig.width=9}
# cluster 13
FeaturePlot(se, features = cluster13_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster13_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 14
```{r, fig.height=6, fig.width=9}
# cluster 14
FeaturePlot(se, features = cluster14_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster14_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 15
```{r, fig.height=6, fig.width=9}
# cluster 15
FeaturePlot(se, features = cluster15_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster15_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 16
```{r, fig.height=6, fig.width=9}
# cluster 16
FeaturePlot(se, features = cluster16_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster16_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 17
```{r, fig.height=6, fig.width=9}
# cluster 17
FeaturePlot(se, features = cluster17_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster17_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

## cluster 18
```{r, fig.height=6, fig.width=9}
# cluster 18
FeaturePlot(se, features = cluster18_marker_topGenes, reduction = "umap", order = TRUE, cols = heatmap.colors, ncol = 4)
ST.FeaturePlot(se, features = cluster18_marker_topGenes, grid.ncol = 4, cols = heatmap.colors, pt.size = 1, show.sb = FALSE)

```

# DEGs Heatmap

Select top N genes to plot
```{r}
N <- 10

topN <- N.markers %>% 
            group_by(cluster) %>% 
            arrange(cluster,p_val_adj) %>%
            slice_head(n=N)
topN
```


Plot heat map of top N genes in each cluster:
```{r, fig.height=20, fig.width=13}
DoHeatmap(se, features = topN$gene, group.colors = col_vector)
```

# Jaccard index

Save marker genes from clusters

Select top M genes from each cluster
```{r}
M <- 10

topM <- N.markers %>% 
            group_by(cluster) %>% 
            arrange(cluster,p_val_adj) %>%
            slice_head(n=M)
topM
```

Subset
```{r}
cluster0_marker_genes_ <- as.character(t(subset(topM,cluster==0, select = gene)))
cluster1_marker_genes_ <- as.character(t(subset(topM,cluster==1, select = gene)))
cluster2_marker_genes_ <- as.character(t(subset(topM,cluster==2, select = gene)))
cluster3_marker_genes_ <- as.character(t(subset(topM,cluster==3, select = gene)))
cluster4_marker_genes_ <- as.character(t(subset(topM,cluster==4, select = gene)))
cluster5_marker_genes_ <- as.character(t(subset(topM,cluster==5, select = gene)))
cluster6_marker_genes_ <- as.character(t(subset(topM,cluster==6, select = gene)))
cluster7_marker_genes_ <- as.character(t(subset(topM,cluster==7, select = gene)))
cluster8_marker_genes_ <- as.character(t(subset(topM,cluster==8, select = gene)))
cluster9_marker_genes_ <- as.character(t(subset(topM,cluster==9, select = gene)))
cluster10_marker_genes_ <- as.character(t(subset(topM,cluster==10, select = gene)))
cluster11_marker_genes_ <- as.character(t(subset(topM,cluster==11, select = gene)))
cluster12_marker_genes_ <- as.character(t(subset(topM,cluster==12, select = gene)))
cluster13_marker_genes_ <- as.character(t(subset(topM,cluster==13, select = gene)))
cluster14_marker_genes_ <- as.character(t(subset(topM,cluster==14, select = gene)))
cluster15_marker_genes_ <- as.character(t(subset(topM,cluster==15, select = gene)))
cluster16_marker_genes_ <- as.character(t(subset(topM,cluster==16, select = gene)))
cluster17_marker_genes_ <- as.character(t(subset(topM,cluster==17, select = gene)))
cluster18_marker_genes_ <- as.character(t(subset(topM,cluster==18, select = gene)))
```

Make a list of all gene sets:
```{r}
all_gene_sets <- list(cluster0_marker_genes_=cluster0_marker_genes_,cluster1_marker_genes_=cluster1_marker_genes_,cluster2_marker_genes_=cluster2_marker_genes_,cluster3_marker_genes_=cluster3_marker_genes_,cluster4_marker_genes_=cluster4_marker_genes_,cluster5_marker_genes_=cluster5_marker_genes_,cluster6_marker_genes_=cluster6_marker_genes_,cluster7_marker_genes_=cluster7_marker_genes_,cluster8_marker_genes_=cluster8_marker_genes_,cluster9_marker_genes_=cluster9_marker_genes_,cluster10_marker_genes_=cluster10_marker_genes_,cluster11_marker_genes_=cluster11_marker_genes_,cluster12_marker_genes_=cluster12_marker_genes_,cluster13_marker_genes_=cluster13_marker_genes_,cluster14_marker_genes_=cluster14_marker_genes_,cluster15_marker_genes_=cluster15_marker_genes_,cluster16_marker_genes_=cluster16_marker_genes_,cluster17_marker_genes_=cluster17_marker_genes_,cluster18_marker_genes_=cluster18_marker_genes_)
```


Jaccard function:
```{r}
jaccard <- function(a, b) {
  intersection = length(intersect(a, b))
  union = length(a) + length(b) - intersection
  return (intersection/union)
}
```

Print all genes shared combinations:
```{r}
# två for-loopar
# Börja med att skapa en tom matrix med lika många kolumner som rader
# kolumn- och rad-namn ska vara samma som namnen på hallmark gene sets
length.mat <- matrix(data = NA, 
                  nrow = length(all_gene_sets), 
                  ncol = length(all_gene_sets), 
                  dimnames = list(names(all_gene_sets), 
                                  names(all_gene_sets)))


# Iterera över två for-loopar, en för rader och en för kolumner
for (i in 1:length(all_gene_sets)) {
  for (j in 1:length(all_gene_sets)) {
    # Spara jaccard mellan par av gene sets
    length.mat[i, j] <- jaccard(all_gene_sets[[i]],all_gene_sets[[j]])
  }
}


```

```{r, fig.height=12, fig.width=14}
length.mat.df <- as.data.frame(length.mat)

library(tidyverse)

df2 <- length.mat.df %>%
  rownames_to_column() %>%
  gather(colname, value, -rowname)
head(df2)

df2$value <- ifelse(df2$rowname == df2$colname, NA, df2$value)

ggplot(df2, aes(x = rowname, y = colname, fill = value)) +
  geom_tile()
```

Re-format plot

```{r, fig.height=12, fig.width=14}
# Get lower triangle of the correlation matrix
  get_lower_tri<-function(length.mat){
    length.mat[upper.tri(length.mat)] <- NA
    return(length.mat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(length.mat){
    length.mat[lower.tri(length.mat)]<- NA
    return(length.mat)
  }


# Reorder function
reorder_length.mat <- function(length.mat){
# Use correlation between variables as distance
dd <- as.dist((1-length.mat)/2)
hc <- hclust(dd)
length.mat <-length.mat[hc$order, hc$order]
}

# Reorder the correlation matrix
length.mat <- reorder_length.mat(length.mat)
lower_tri <- get_lower_tri(length.mat)
# Melt the correlation matrix
melted_length.mat <- melt(lower_tri, na.rm = TRUE)
melted_length.mat$value <- ifelse(melted_length.mat$Var1 == melted_length.mat$Var2, NA, melted_length.mat$value)
# Create a ggheatmap
ggheatmap <- ggplot(melted_length.mat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, space = "Lab", 
    name="Jaccard index", limits=c(0,1)) +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()+
  geom_text(aes(label = round(value, 2)))

# Print the heatmap
ggheatmap + ggtitle("All traits")
```


```{r, fig.height=12, fig.width=14}
# Get lower triangle of the correlation matrix
  get_lower_tri<-function(length.mat){
    length.mat[upper.tri(length.mat)] <- NA
    return(length.mat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(length.mat){
    length.mat[lower.tri(length.mat)]<- NA
    return(length.mat)
  }


# Reorder function
reorder_length.mat <- function(length.mat){
# Use correlation between variables as distance
dd <- as.dist((1-length.mat)/2)
hc <- hclust(dd)
length.mat <-length.mat[hc$order, hc$order]
}

# Reorder the correlation matrix
length.mat <- reorder_length.mat(length.mat)
lower_tri <- get_lower_tri(length.mat)
# Melt the correlation matrix
melted_length.mat <- melt(lower_tri, na.rm = TRUE)
melted_length.mat$value <- ifelse(melted_length.mat$Var1 == melted_length.mat$Var2, NA, melted_length.mat$value)
# Create a ggheatmap
ggheatmap <- ggplot(melted_length.mat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, space = "Lab", 
    name="Jaccard index") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()+
  geom_text(aes(label = round(value, 2)))

# Print the heatmap
ggheatmap + ggtitle("All traits")
```

Save
```{r, eval=FALSE}
write.table(cluster0_marker_genes_,file = "spatial_structures/cluster0_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster1_marker_genes_,file = "spatial_structures/cluster1_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster2_marker_genes_,file = "spatial_structures/cluster2_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster3_marker_genes_,file = "spatial_structures/cluster3_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster4_marker_genes_,file = "spatial_structures/cluster4_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster5_marker_genes_,file = "spatial_structures/cluster5_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster6_marker_genes_,file = "spatial_structures/cluster6_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster7_marker_genes_,file = "spatial_structures/cluster7_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster8_marker_genes_,file = "spatial_structures/cluster8_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster9_marker_genes_,file = "spatial_structures/cluster9_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster10_marker_genes_,file = "spatial_structures/cluster10_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster11_marker_genes_,file = "spatial_structures/cluster11_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster12_marker_genes_,file = "spatial_structures/cluster12_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster13_marker_genes_,file = "spatial_structures/cluster13_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster14_marker_genes_,file = "spatial_structures/cluster14_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster15_marker_genes_,file = "spatial_structures/cluster15_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster16_marker_genes_,file = "spatial_structures/cluster16_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster17_marker_genes_,file = "spatial_structures/cluster17_marker_genes_.csv", row.names = F, col.names = F)
write.table(cluster18_marker_genes_,file = "spatial_structures/cluster18_marker_genes_.csv", row.names = F, col.names = F)
```


# Notes

Session info
```{r}
sessionInfo()
```

