---
title: "NULL_permutation_all_genes_ALZ_[human_JBO0018]_NegCtrl"
author: "Linda Kvastad"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
 html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

# Load and Normalize data

Load libraries:
```{r, message=FALSE}
library(STutility)
library(dplyr)
library(RColorBrewer)
library(scales)
library(reshape2)
library(corrplot)
library(lawstat)
library(MASS)
library(viridis)
```

Load ST data:
```{r}

infoTable <- read.csv("spatial_data/infoTable.csv", sep = ";")


se <- InputFromTable(infotable = infoTable, 
                      minUMICountsPerGene = 100, 
                      minSpotsPerGene = 5,
                      minUMICountsPerSpot = 500,
                      platform =  "Visium")

```


Load image:
```{r}
se <- LoadImages(se, time.resolve = FALSE)
```

View image:
```{r, fig.height=4, fig.width=5}
ImagePlot(se, method = "raster", annotate = FALSE)
```

# QC plots  {.tabset}

QC metrics se:
```{r}
# Collect all genes coded on the mitochondrial genome
mt.genes <- grep(pattern = "^MT-", x = rownames(se), value = TRUE)
se$percent.mito <- (Matrix::colSums(se@assays$RNA@counts[mt.genes, ])/Matrix::colSums(se@assays$RNA@counts))*100

# Collect all genes coding for ribosomal proteins
rp.genes <- grep(pattern = "^RPL|^RPS", x = rownames(se), value = TRUE)
se$percent.ribo <- (Matrix::colSums(se@assays$RNA@counts[rp.genes, ])/Matrix::colSums(se@assays$RNA@counts))*100
```

## percent.mito
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "percent.mito", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)

```

## percent.ribo
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "percent.ribo", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```

## nFeature_RNA
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "nFeature_RNA", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```

## nCount_RNA
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(se, features = "nCount_RNA", cols = c("lightgray", "mistyrose", "red", "dark red", "black"), pt.size = 1.3)
```


# Spatial clusters  {.tabset}

Normalize data: se <- SCTransform(se,return.only.var.genes = T)
```{r, message=FALSE, include=FALSE}
se <- SCTransform(se,return.only.var.genes = T)
```

Load cluster annotations
```{r}
seurat_clusters <- read.csv(file = "spatial_structures/seurat_clusters.csv", sep = ";")
```

Add annotations to seurat object
```{r}
rownames(seurat_clusters) <- seurat_clusters$Barcode
seurat_clusters$Barcode <- NULL
se$seurat_clusters <- seurat_clusters
se$seurat_clusters_plot <- as.factor(se$seurat_clusters) # For plotting of spatial structures
head(se[[]])
```

## Plot seurat_clusters
```{r, fig.height=4, fig.width=5}
n <- 6
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
  
col_vector <- col_vector[1:6]

se <- SetIdent(se, value = "seurat_clusters_plot")
ST.FeaturePlot(object = se, features = "seurat_clusters_plot", pt.size = 1, cols = col_vector)
```

## FeatureOverlay seurat_clusters
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1

FeatureOverlay(se, 
               features = c("seurat_clusters_plot"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = col_vector)
```


# OpenTargets gene sets

Load OpenTargets gene sets
```{r class.source = 'fold-show'}

OpenTargets_ALZ_Genetic_ <- as.character(t(read.table(file = "OpenTargets_gene_sets/Human_OpenTargets_ALZ_Genetic.csv")))
length(OpenTargets_ALZ_Genetic_)

OpenTargets_ALZ_Genetic_topGenes_ <- OpenTargets_ALZ_Genetic_[1:50]

OpenTargets_ALZ_Drugs_ <- as.character(t(read.table(file = "OpenTargets_gene_sets/Human_OpenTargets_ALZ_Drugs.csv")))
length(OpenTargets_ALZ_Drugs_)

```



Load structure marker gene sets
```{r}
cluster0_marker_genes_ <- as.character(t(read.table(file = "spatial_structures/cluster0_marker_genes_.csv")))
cluster1_marker_genes_ <- as.character(t(read.table(file = "spatial_structures/cluster1_marker_genes_.csv")))
cluster2_marker_genes_ <- as.character(t(read.table(file = "spatial_structures/cluster2_marker_genes_.csv")))
cluster3_marker_genes_ <- as.character(t(read.table(file = "spatial_structures/cluster3_marker_genes_.csv")))
cluster4_marker_genes_ <- as.character(t(read.table(file = "spatial_structures/cluster4_marker_genes_.csv")))
cluster5_marker_genes_ <- as.character(t(read.table(file = "spatial_structures/cluster5_marker_genes_.csv")))
```


Load window rank lists
```{r}
window50_rank_list_ALZ_Genetic <- readRDS(file = "OpenTargets_windowLists/Human_window50_rank_list_ALZ_Genetic.RDS")
window50_rank_list_ALZ_Drugs <- readRDS(file = "OpenTargets_windowLists/Human_window50_rank_list_ALZ_Drugs.RDS")

```


Make a list of all OpenTargets gene sets:
```{r}
all_gene_sets_OpenTargets <- list(OpenTargets_ALZ_Genetic_=OpenTargets_ALZ_Genetic_,OpenTargets_ALZ_Genetic_topGenes_=OpenTargets_ALZ_Genetic_topGenes_,OpenTargets_ALZ_Drugs_=OpenTargets_ALZ_Drugs_)
```


Structure marker gene sets
```{r}
all_gene_sets_structure_markers <- list(cluster0_marker_genes_=cluster0_marker_genes_,cluster1_marker_genes_=cluster1_marker_genes_,cluster2_marker_genes_=cluster2_marker_genes_,cluster3_marker_genes_=cluster3_marker_genes_,cluster4_marker_genes_=cluster4_marker_genes_,cluster5_marker_genes_=cluster5_marker_genes_)
```


Merge gene sets
```{r}
all_gene_sets <- all_gene_sets_OpenTargets
all_gene_sets <- append(all_gene_sets,all_gene_sets_structure_markers)
all_gene_sets <- append(all_gene_sets,window50_rank_list_ALZ_Genetic)
all_gene_sets <- append(all_gene_sets,window50_rank_list_ALZ_Drugs)
```


# Score data based on gene sets

AddModuleScore loop se:

```{r, eval=FALSE}
score.mat <- matrix(data = NA, nrow = length(all_gene_sets), ncol = 1, dimnames = list(names(all_gene_sets), "% of genes present"))

for (i in 1:length(all_gene_sets)) {
  genes <- unlist(all_gene_sets[i]) # character vector of genes in a gene set
  score.mat[i] <- mean(genes %in% rownames(se)) # calculate and collect % of genes present in se from the gene set
  print(list(names(all_gene_sets[i])))
  se <- AddModuleScore(se,list(genes), ctrl = 100, name = list(names(all_gene_sets[i])))
}

```


```{r, message=FALSE, include=FALSE}

score.mat <- matrix(data = NA, nrow = length(all_gene_sets), ncol = 1, dimnames = list(names(all_gene_sets), "% of genes present"))

for (i in 1:length(all_gene_sets)) {
  genes <- unlist(all_gene_sets[i]) # character vector of genes in a gene set
  score.mat[i] <- mean(genes %in% rownames(se)) # calculate and collect % of genes present in se from the gene set
  print(list(names(all_gene_sets[i])))
  se <- AddModuleScore(se,list(genes), ctrl = 100, name = list(names(all_gene_sets[i])))
}

```

Print % of genes present in scores, should be 100 %
```{r}
score.mat*100
```


# Violin plots {.tabset}

```{r}
se <- SetIdent(se, value = "seurat_clusters")
```

## ALZ_Genetic
```{r}
VlnPlot(se, features = c("OpenTargets_ALZ_Genetic_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
```

## ALZ_Genetic_topGenes
```{r}
VlnPlot(se, features = c("OpenTargets_ALZ_Genetic_topGenes_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
```

## ALZ_Drugs
```{r}
VlnPlot(se, features = c("OpenTargets_ALZ_Drugs_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
```

## nFeature_RNA
```{r}
VlnPlot(se, features = c("nFeature_RNA"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
```

## nCount_RNA
```{r}
VlnPlot(se, features = c("nCount_RNA"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
```


# Spatial plots


FeatureOverlay: Genetic & Drugs
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1


FeatureOverlay(se, 
               features = c("OpenTargets_ALZ_Genetic_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"))

FeatureOverlay(se, 
               features = c("OpenTargets_ALZ_Genetic_topGenes_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"))


FeatureOverlay(se, 
               features = c("OpenTargets_ALZ_Drugs_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"))

```


# NULL set permutation


Load perm.mat from NULL gene sets
```{r class.source = 'fold-show'}
perm.mat.window50 <- readRDS(file = "Permutation_matrices/perm.mat_p10000_g50.RDS")
perm.mat.genetic <- readRDS(file = "Permutation_matrices/perm.mat_p10000_g233.RDS")
perm.mat.drugs <- readRDS(file = "Permutation_matrices/perm.mat_p10000_g73.RDS")
```


Permutation test settings
```{r class.source = 'fold-show'}
permutation.nr <- 10000

perm.mat.window50.data <- as.data.frame(perm.mat.window50)
perm.mat.genetic.data <- as.data.frame(perm.mat.genetic)
perm.mat.drugs.data <- as.data.frame(perm.mat.drugs)

nr_of_tests <- 6 

#Cluster names
cluster_names <- rep("cluster_", length(table(se$seurat_clusters)))
cluster_names <- paste0(cluster_names,as.character(0:(length(table(se$seurat_clusters))-1)))

#P-value matrices
p.val.mat.g <- matrix(data = NA, nrow = 2, ncol = length(cluster_names), dimnames = list(c("-log10(p.val)","-log10(p.val.adj)"),cluster_names))
p.val.mat.d <- matrix(data = NA, nrow = 2, ncol = length(cluster_names), dimnames = list(c("-log10(p.val)","-log10(p.val.adj)"),cluster_names))

```



# Sliding window OT Genetic

Subset to relevant spatial structures
```{r}
se_0 <- SubsetSTData(se, expression = seurat_clusters == 0)
se_1 <- SubsetSTData(se, expression = seurat_clusters == 1)
se_2 <- SubsetSTData(se, expression = seurat_clusters == 2)
se_3 <- SubsetSTData(se, expression = seurat_clusters == 3)
se_4 <- SubsetSTData(se, expression = seurat_clusters == 4)
se_5 <- SubsetSTData(se, expression = seurat_clusters == 5)
```

Extract meta data and AddModuleScores
```{r}
meta_data_se <- se[[]]
meta_data_se_0 <- se_0[[]]
meta_data_se_1 <- se_1[[]]
meta_data_se_2 <- se_2[[]]
meta_data_se_3 <- se_3[[]]
meta_data_se_4 <- se_4[[]]
meta_data_se_5 <- se_5[[]]
```

Subset data: ALZ_Genetic
```{r}
start_with_ALZ_Genetic <- grep("^ALZ_Genetic", colnames(meta_data_se), value = TRUE)
meta_data_se_ALZ_Genetic <- subset(meta_data_se, select = start_with_ALZ_Genetic)

start_with_ALZ_Genetic <- grep("^ALZ_Genetic", colnames(meta_data_se_0), value = TRUE)
meta_data_se_0_ALZ_Genetic <- subset(meta_data_se_0, select = start_with_ALZ_Genetic)

start_with_ALZ_Genetic <- grep("^ALZ_Genetic", colnames(meta_data_se_1), value = TRUE)
meta_data_se_1_ALZ_Genetic <- subset(meta_data_se_1, select = start_with_ALZ_Genetic)

start_with_ALZ_Genetic <- grep("^ALZ_Genetic", colnames(meta_data_se_2), value = TRUE)
meta_data_se_2_ALZ_Genetic <- subset(meta_data_se_2, select = start_with_ALZ_Genetic)

start_with_ALZ_Genetic <- grep("^ALZ_Genetic", colnames(meta_data_se_3), value = TRUE)
meta_data_se_3_ALZ_Genetic <- subset(meta_data_se_3, select = start_with_ALZ_Genetic)

start_with_ALZ_Genetic <- grep("^ALZ_Genetic", colnames(meta_data_se_4), value = TRUE)
meta_data_se_4_ALZ_Genetic <- subset(meta_data_se_4, select = start_with_ALZ_Genetic)

start_with_ALZ_Genetic <- grep("^ALZ_Genetic", colnames(meta_data_se_5), value = TRUE)
meta_data_se_5_ALZ_Genetic <- subset(meta_data_se_5, select = start_with_ALZ_Genetic)
```


## ALZ_Genetic all structures {.tabset}

Extract quantile: ALZ_Genetic all structures
```{r}
meta_data_vector <- NULL
ALZ_Genetic_structure <- NULL

for (i in 1:length(meta_data_se_ALZ_Genetic)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$quantile <- quantile(as.numeric(meta_data_se_ALZ_Genetic[,i]), probs = 0.99)
        ALZ_Genetic_structure <- rbind(ALZ_Genetic_structure,meta_data_vector)
}
rownames(ALZ_Genetic_structure) <- 1:length(meta_data_se_ALZ_Genetic)
ALZ_Genetic_structure <- as.data.frame(ALZ_Genetic_structure)
ALZ_Genetic_structure <- unlist(ALZ_Genetic_structure$quantile)
ALZ_Genetic_structure <- as.data.frame(ALZ_Genetic_structure)
ALZ_Genetic_structure$Rank <- 1:length(meta_data_se_ALZ_Genetic)
colnames(ALZ_Genetic_structure) <- c("quantile","Rank")
```

### ALZ_Genetic all structures
```{r, fig.width=10}
plot(ALZ_Genetic_structure$Rank,ALZ_Genetic_structure$quantile, main = "ALZ Genetic all structures", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.1,0.5))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50), col="darkred", lwd = 2, lty = 2)
```

### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se, 
               features = c("ALZ_Genetic_Rank1_1","ALZ_Genetic_Rank2_1","ALZ_Genetic_Rank3_1","ALZ_Genetic_Rank4_1","ALZ_Genetic_Rank5_1","ALZ_Genetic_Rank6_1","ALZ_Genetic_Rank7_1","ALZ_Genetic_Rank8_1","ALZ_Genetic_Rank9_1","ALZ_Genetic_Rank10_1","ALZ_Genetic_Rank11_1","ALZ_Genetic_Rank12_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")


ST.FeaturePlot(se, 
               features = c("ALZ_Genetic_Rank13_1","ALZ_Genetic_Rank14_1","ALZ_Genetic_Rank15_1","ALZ_Genetic_Rank16_1","ALZ_Genetic_Rank17_1","ALZ_Genetic_Rank18_1","ALZ_Genetic_Rank19_1","ALZ_Genetic_Rank20_1","ALZ_Genetic_Rank21_1","ALZ_Genetic_Rank22_1","ALZ_Genetic_Rank23_1","ALZ_Genetic_Rank24_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")


```


### Violin plots 1-10
```{r}
se <- SetIdent(se, value = "seurat_clusters")

VlnPlot(se, features = c("ALZ_Genetic_Rank1_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank2_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank3_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank4_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank5_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank6_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank7_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank8_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank9_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Genetic_Rank10_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))

```



## ALZ_Genetic structure 0 {.tabset}

Extract median: ALZ_Genetic structure 0
```{r}
meta_data_vector <- NULL
ALZ_Genetic_structure_0 <- NULL

for (i in 1:length(meta_data_se_0_ALZ_Genetic)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_0_ALZ_Genetic[,i])
        ALZ_Genetic_structure_0 <- rbind(ALZ_Genetic_structure_0,meta_data_vector)
}
rownames(ALZ_Genetic_structure_0) <- 1:length(meta_data_se_0_ALZ_Genetic)
ALZ_Genetic_structure_0 <- as.data.frame(ALZ_Genetic_structure_0)
```

### ALZ_Genetic windows
```{r, fig.width=10}
plot(ALZ_Genetic_structure_0$Rank,ALZ_Genetic_structure_0$Median, main = "ALZ Genetic Structure 0", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,1]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,1]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,1]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,1]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,1]), col="darkred", lwd = 2, lty = 2)
```

Permutation p-value windows: ALZ Genetic Structure 0
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster0 <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Genetic), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Genetic)){
  
  OT_genetic_window <- as.numeric(ALZ_Genetic_structure_0[i,2])
  perm.mat.window50.cluster0_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_0 >= OT_genetic_window)
  
  cluster0_w_p.val <- (nrow(perm.mat.window50.cluster0_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster0[i,1] <- as.numeric(cluster0_w_p.val)
  
  cluster0_w_p.val.adj <- p.adjust(cluster0_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster0[i,2] <- as.numeric(cluster0_w_p.val.adj)
}

p.mat.cluster0[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_0, 
               features = c("ALZ_Genetic_Rank1_1","ALZ_Genetic_Rank2_1","ALZ_Genetic_Rank3_1","ALZ_Genetic_Rank4_1","ALZ_Genetic_Rank5_1","ALZ_Genetic_Rank6_1","ALZ_Genetic_Rank7_1","ALZ_Genetic_Rank8_1","ALZ_Genetic_Rank9_1","ALZ_Genetic_Rank10_1","ALZ_Genetic_Rank11_1","ALZ_Genetic_Rank12_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```



### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_0 <- as.data.frame(perm.mat.genetic.data$cluster_0)
colnames(median_score_NULL_permutations_cluster_0) <- c("Median_scores")

# permutation p-value
perm.mat.genetic.cluster0_bigger <- subset(perm.mat.genetic.data,perm.mat.genetic.data$cluster_0 >= as.numeric(median(se_0$OpenTargets_ALZ_Genetic_1)))

cluster0_p.val.g <- (nrow(perm.mat.genetic.cluster0_bigger)+1)/(permutation.nr+1)
cluster0_p.val.g.adj <- p.adjust(cluster0_p.val.g,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

p.val.mat.g[1,1] <- -log10(cluster0_p.val.g)
p.val.mat.g[2,1] <- -log10(cluster0_p.val.g.adj)

cluster0_p.val.g.adj_text <- as.character(round(cluster0_p.val.g.adj, digits = 4))
cluster0_p.val.g.adj_text <- paste0(c("p.val.adj = "),cluster0_p.val.g.adj_text)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_0 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_0$OpenTargets_ALZ_Genetic_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster0_p.val.g.adj_text)+
  ggtitle("Structure 0")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```


## ALZ_Genetic structure 1 {.tabset}


Extract median: ALZ_Genetic structure 1
```{r}
meta_data_vector <- NULL
ALZ_Genetic_structure_1 <- NULL

for (i in 1:length(meta_data_se_1_ALZ_Genetic)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_1_ALZ_Genetic[,i])
        ALZ_Genetic_structure_1 <- rbind(ALZ_Genetic_structure_1,meta_data_vector)
}
rownames(ALZ_Genetic_structure_1) <- 1:length(meta_data_se_1_ALZ_Genetic)
ALZ_Genetic_structure_1 <- as.data.frame(ALZ_Genetic_structure_1)
```

### ALZ_Genetic windows
```{r, fig.width=10}
plot(ALZ_Genetic_structure_1$Rank,ALZ_Genetic_structure_1$Median, main = "ALZ Genetic Structure 1", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,2]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,2]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,2]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,2]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,2]), col="darkred", lwd = 2, lty = 2)
```

Permutation p-value windows: ALZ Genetic Structure 1
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster1 <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Genetic), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Genetic)){
  
  OT_genetic_window <- as.numeric(ALZ_Genetic_structure_1[i,2])
  perm.mat.window50.cluster1_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_1 >= OT_genetic_window)
  
  cluster1_w_p.val <- (nrow(perm.mat.window50.cluster1_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster1[i,1] <- as.numeric(cluster1_w_p.val)
  
  cluster1_w_p.val.adj <- p.adjust(cluster1_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster1[i,2] <- as.numeric(cluster1_w_p.val.adj)
}

p.mat.cluster1[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_1, 
               features = c("ALZ_Genetic_Rank1_1","ALZ_Genetic_Rank2_1","ALZ_Genetic_Rank3_1","ALZ_Genetic_Rank4_1","ALZ_Genetic_Rank5_1","ALZ_Genetic_Rank6_1","ALZ_Genetic_Rank7_1","ALZ_Genetic_Rank8_1","ALZ_Genetic_Rank9_1","ALZ_Genetic_Rank10_1","ALZ_Genetic_Rank11_1","ALZ_Genetic_Rank12_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_1 <- as.data.frame(perm.mat.genetic.data$cluster_1)
colnames(median_score_NULL_permutations_cluster_1) <- c("Median_scores")

# permutation p-value
perm.mat.genetic.cluster1_bigger <- subset(perm.mat.genetic.data,perm.mat.genetic.data$cluster_1 >= as.numeric(median(se_1$OpenTargets_ALZ_Genetic_1)))

cluster1_p.val.g <- (nrow(perm.mat.genetic.cluster1_bigger)+1)/(permutation.nr+1)
cluster1_p.val.g.adj <- p.adjust(cluster1_p.val.g,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster1_p.val.g.adj_text <- as.character(round(cluster1_p.val.g.adj, digits = 4))
cluster1_p.val.g.adj_text <- paste0(c("p.val.adj = "),cluster1_p.val.g.adj_text)

p.val.mat.g[1,2] <- -log10(cluster1_p.val.g)
p.val.mat.g[2,2] <- -log10(cluster1_p.val.g.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_1 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_1$OpenTargets_ALZ_Genetic_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster1_p.val.g.adj_text)+
  ggtitle("Structure 1")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```




## ALZ_Genetic structure 2 {.tabset}


Extract median: ALZ_Genetic structure 2
```{r}
meta_data_vector <- NULL
ALZ_Genetic_structure_2 <- NULL

for (i in 1:length(meta_data_se_2_ALZ_Genetic)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_2_ALZ_Genetic[,i])
        ALZ_Genetic_structure_2 <- rbind(ALZ_Genetic_structure_2,meta_data_vector)
}
rownames(ALZ_Genetic_structure_2) <- 1:length(meta_data_se_2_ALZ_Genetic)
ALZ_Genetic_structure_2 <- as.data.frame(ALZ_Genetic_structure_2)
```

### ALZ_Genetic windows
```{r, fig.width=10}
plot(ALZ_Genetic_structure_2$Rank,ALZ_Genetic_structure_2$Median, main = "ALZ Genetic Structure 2", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,3]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,3]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,3]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,3]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,3]), col="darkred", lwd = 2, lty = 2)
```

Permutation p-value windows: ALZ Genetic Structure 2
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster2 <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Genetic), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Genetic)){
  
  OT_genetic_window <- as.numeric(ALZ_Genetic_structure_2[i,2])
  perm.mat.window50.cluster2_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_2 >= OT_genetic_window)
  
  cluster2_w_p.val <- (nrow(perm.mat.window50.cluster2_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster2[i,1] <- as.numeric(cluster2_w_p.val)
  
  cluster2_w_p.val.adj <- p.adjust(cluster2_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster2[i,2] <- as.numeric(cluster2_w_p.val.adj)
}


p.mat.cluster2[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_2, 
               features = c("ALZ_Genetic_Rank1_1","ALZ_Genetic_Rank2_1","ALZ_Genetic_Rank3_1","ALZ_Genetic_Rank4_1","ALZ_Genetic_Rank5_1","ALZ_Genetic_Rank6_1","ALZ_Genetic_Rank7_1","ALZ_Genetic_Rank8_1","ALZ_Genetic_Rank9_1","ALZ_Genetic_Rank10_1","ALZ_Genetic_Rank11_1","ALZ_Genetic_Rank12_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_2 <- as.data.frame(perm.mat.genetic.data$cluster_2)
colnames(median_score_NULL_permutations_cluster_2) <- c("Median_scores")

# permutation p-value
perm.mat.genetic.cluster2_bigger <- subset(perm.mat.genetic.data,perm.mat.genetic.data$cluster_2 >= as.numeric(median(se_2$OpenTargets_ALZ_Genetic_1)))

cluster2_p.val.g <- (nrow(perm.mat.genetic.cluster2_bigger)+1)/(permutation.nr+1)
cluster2_p.val.g.adj <- p.adjust(cluster2_p.val.g,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster2_p.val.g.adj_text <- as.character(round(cluster2_p.val.g.adj, digits = 4))
cluster2_p.val.g.adj_text <- paste0(c("p.val.adj = "),cluster2_p.val.g.adj_text)

p.val.mat.g[1,3] <- -log10(cluster2_p.val.g)
p.val.mat.g[2,3] <- -log10(cluster2_p.val.g.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_2 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_2$OpenTargets_ALZ_Genetic_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster2_p.val.g.adj_text)+
  ggtitle("Structure 2")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```



## ALZ_Genetic structure 3 {.tabset}


Extract median: ALZ_Genetic structure 3
```{r}
meta_data_vector <- NULL
ALZ_Genetic_structure_3 <- NULL

for (i in 1:length(meta_data_se_3_ALZ_Genetic)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_3_ALZ_Genetic[,i])
        ALZ_Genetic_structure_3 <- rbind(ALZ_Genetic_structure_3,meta_data_vector)
}
rownames(ALZ_Genetic_structure_3) <- 1:length(meta_data_se_3_ALZ_Genetic)
ALZ_Genetic_structure_3 <- as.data.frame(ALZ_Genetic_structure_3)
```

### ALZ_Genetic windows
```{r, fig.width=10}
plot(ALZ_Genetic_structure_3$Rank,ALZ_Genetic_structure_3$Median, main = "ALZ Genetic Structure 3", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,4]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,4]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,4]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,4]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,4]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Genetic Structure 3
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster3 <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Genetic), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Genetic)){
  
  OT_genetic_window <- as.numeric(ALZ_Genetic_structure_3[i,2])
  perm.mat.window50.cluster3_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_3 >= OT_genetic_window)
  
  cluster3_w_p.val <- (nrow(perm.mat.window50.cluster3_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster3[i,1] <- as.numeric(cluster3_w_p.val)
  
  cluster3_w_p.val.adj <- p.adjust(cluster3_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster3[i,2] <- as.numeric(cluster3_w_p.val.adj)
}

p.mat.cluster3[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_3, 
               features = c("ALZ_Genetic_Rank1_1","ALZ_Genetic_Rank2_1","ALZ_Genetic_Rank3_1","ALZ_Genetic_Rank4_1","ALZ_Genetic_Rank5_1","ALZ_Genetic_Rank6_1","ALZ_Genetic_Rank7_1","ALZ_Genetic_Rank8_1","ALZ_Genetic_Rank9_1","ALZ_Genetic_Rank10_1","ALZ_Genetic_Rank11_1","ALZ_Genetic_Rank12_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_3 <- as.data.frame(perm.mat.genetic.data$cluster_3)
colnames(median_score_NULL_permutations_cluster_3) <- c("Median_scores")

# permutation p-value
perm.mat.genetic.cluster3_bigger <- subset(perm.mat.genetic.data,perm.mat.genetic.data$cluster_3 >= as.numeric(median(se_3$OpenTargets_ALZ_Genetic_1)))

cluster3_p.val.g <- (nrow(perm.mat.genetic.cluster3_bigger)+1)/(permutation.nr+1)
cluster3_p.val.g.adj <- p.adjust(cluster3_p.val.g,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster3_p.val.g.adj_text <- as.character(round(cluster3_p.val.g.adj, digits = 4))
cluster3_p.val.g.adj_text <- paste0(c("p.val.adj = "),cluster3_p.val.g.adj_text)

p.val.mat.g[1,4] <- -log10(cluster3_p.val.g)
p.val.mat.g[2,4] <- -log10(cluster3_p.val.g.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_3 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_3$OpenTargets_ALZ_Genetic_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster3_p.val.g.adj_text)+
  ggtitle("Structure 3")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```



## ALZ_Genetic structure 4 {.tabset}


Extract median: ALZ_Genetic structure 4
```{r}
meta_data_vector <- NULL
ALZ_Genetic_structure_4 <- NULL

for (i in 1:length(meta_data_se_4_ALZ_Genetic)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_4_ALZ_Genetic[,i])
        ALZ_Genetic_structure_4 <- rbind(ALZ_Genetic_structure_4,meta_data_vector)
}
rownames(ALZ_Genetic_structure_4) <- 1:length(meta_data_se_4_ALZ_Genetic)
ALZ_Genetic_structure_4 <- as.data.frame(ALZ_Genetic_structure_4)
```

### ALZ_Genetic windows
```{r, fig.width=10}
plot(ALZ_Genetic_structure_4$Rank,ALZ_Genetic_structure_4$Median, main = "ALZ Genetic Structure 4", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,5]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,5]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,5]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,5]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,5]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Genetic Structure 4
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster4 <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Genetic), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Genetic)){
  
  OT_genetic_window <- as.numeric(ALZ_Genetic_structure_4[i,2])
  perm.mat.window50.cluster4_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_4 >= OT_genetic_window)
  
  cluster4_w_p.val <- (nrow(perm.mat.window50.cluster4_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster4[i,1] <- as.numeric(cluster4_w_p.val)
  
  cluster4_w_p.val.adj <- p.adjust(cluster4_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster4[i,2] <- as.numeric(cluster4_w_p.val.adj)
}

p.mat.cluster4[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_4, 
               features = c("ALZ_Genetic_Rank1_1","ALZ_Genetic_Rank2_1","ALZ_Genetic_Rank3_1","ALZ_Genetic_Rank4_1","ALZ_Genetic_Rank5_1","ALZ_Genetic_Rank6_1","ALZ_Genetic_Rank7_1","ALZ_Genetic_Rank8_1","ALZ_Genetic_Rank9_1","ALZ_Genetic_Rank10_1","ALZ_Genetic_Rank11_1","ALZ_Genetic_Rank12_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_4 <- as.data.frame(perm.mat.genetic.data$cluster_4)
colnames(median_score_NULL_permutations_cluster_4) <- c("Median_scores")

# permutation p-value
perm.mat.genetic.cluster4_bigger <- subset(perm.mat.genetic.data,perm.mat.genetic.data$cluster_4 >= as.numeric(median(se_4$OpenTargets_ALZ_Genetic_1)))

cluster4_p.val.g <- (nrow(perm.mat.genetic.cluster4_bigger)+1)/(permutation.nr+1)
cluster4_p.val.g.adj <- p.adjust(cluster4_p.val.g,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster4_p.val.g.adj_text <- as.character(round(cluster4_p.val.g.adj, digits = 4))
cluster4_p.val.g.adj_text <- paste0(c("p.val.adj = "),cluster4_p.val.g.adj_text)

p.val.mat.g[1,5] <- -log10(cluster4_p.val.g)
p.val.mat.g[2,5] <- -log10(cluster4_p.val.g.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_4 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_4$OpenTargets_ALZ_Genetic_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster4_p.val.g.adj_text)+
  ggtitle("Structure 4")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```



## ALZ_Genetic structure 5 {.tabset}


Extract median: ALZ_Genetic structure 5
```{r}
meta_data_vector <- NULL
ALZ_Genetic_structure_5 <- NULL

for (i in 1:length(meta_data_se_5_ALZ_Genetic)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_5_ALZ_Genetic[,i])
        ALZ_Genetic_structure_5 <- rbind(ALZ_Genetic_structure_5,meta_data_vector)
}
rownames(ALZ_Genetic_structure_5) <- 1:length(meta_data_se_5_ALZ_Genetic)
ALZ_Genetic_structure_5 <- as.data.frame(ALZ_Genetic_structure_5)
```

### ALZ_Genetic windows
```{r, fig.width=10}
plot(ALZ_Genetic_structure_5$Rank,ALZ_Genetic_structure_5$Median, main = "ALZ Genetic Structure 5", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,6]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,6]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,6]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,6]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,6]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Genetic Structure 5
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Genetic))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster5 <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Genetic), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Genetic)){
  
  OT_genetic_window <- as.numeric(ALZ_Genetic_structure_5[i,2])
  perm.mat.window50.cluster5_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_5 >= OT_genetic_window)
  
  cluster5_w_p.val <- (nrow(perm.mat.window50.cluster5_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster5[i,1] <- as.numeric(cluster5_w_p.val)
  
  cluster5_w_p.val.adj <- p.adjust(cluster5_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster5[i,2] <- as.numeric(cluster5_w_p.val.adj)
}

p.mat.cluster5[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_5, 
               features = c("ALZ_Genetic_Rank1_1","ALZ_Genetic_Rank2_1","ALZ_Genetic_Rank3_1","ALZ_Genetic_Rank4_1","ALZ_Genetic_Rank5_1","ALZ_Genetic_Rank6_1","ALZ_Genetic_Rank7_1","ALZ_Genetic_Rank8_1","ALZ_Genetic_Rank9_1","ALZ_Genetic_Rank10_1","ALZ_Genetic_Rank11_1","ALZ_Genetic_Rank12_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_5 <- as.data.frame(perm.mat.genetic.data$cluster_5)
colnames(median_score_NULL_permutations_cluster_5) <- c("Median_scores")

# permutation p-value
perm.mat.genetic.cluster5_bigger <- subset(perm.mat.genetic.data,perm.mat.genetic.data$cluster_5 >= as.numeric(median(se_5$OpenTargets_ALZ_Genetic_1)))

cluster5_p.val.g <- (nrow(perm.mat.genetic.cluster5_bigger)+1)/(permutation.nr+1)
cluster5_p.val.g.adj <- p.adjust(cluster5_p.val.g,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster5_p.val.g.adj_text <- as.character(round(cluster5_p.val.g.adj, digits = 4))
cluster5_p.val.g.adj_text <- paste0(c("p.val.adj = "),cluster5_p.val.g.adj_text)

p.val.mat.g[1,6] <- -log10(cluster5_p.val.g)
p.val.mat.g[2,6] <- -log10(cluster5_p.val.g.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_5 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_5$OpenTargets_ALZ_Genetic_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster5_p.val.g.adj_text)+
  ggtitle("Structure 5")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```





# Sliding window OT Drugs


Subset data: ALZ_Drugs
```{r}
start_with_ALZ_Drugs <- grep("^ALZ_Drugs", colnames(meta_data_se), value = TRUE)
meta_data_se_ALZ_Drugs <- subset(meta_data_se, select = start_with_ALZ_Drugs)

start_with_ALZ_Drugs <- grep("^ALZ_Drugs", colnames(meta_data_se_0), value = TRUE)
meta_data_se_0_ALZ_Drugs <- subset(meta_data_se_0, select = start_with_ALZ_Drugs)

start_with_ALZ_Drugs <- grep("^ALZ_Drugs", colnames(meta_data_se_1), value = TRUE)
meta_data_se_1_ALZ_Drugs <- subset(meta_data_se_1, select = start_with_ALZ_Drugs)

start_with_ALZ_Drugs <- grep("^ALZ_Drugs", colnames(meta_data_se_2), value = TRUE)
meta_data_se_2_ALZ_Drugs <- subset(meta_data_se_2, select = start_with_ALZ_Drugs)

start_with_ALZ_Drugs <- grep("^ALZ_Drugs", colnames(meta_data_se_3), value = TRUE)
meta_data_se_3_ALZ_Drugs <- subset(meta_data_se_3, select = start_with_ALZ_Drugs)

start_with_ALZ_Drugs <- grep("^ALZ_Drugs", colnames(meta_data_se_4), value = TRUE)
meta_data_se_4_ALZ_Drugs <- subset(meta_data_se_4, select = start_with_ALZ_Drugs)

start_with_ALZ_Drugs <- grep("^ALZ_Drugs", colnames(meta_data_se_5), value = TRUE)
meta_data_se_5_ALZ_Drugs <- subset(meta_data_se_5, select = start_with_ALZ_Drugs)
```


## ALZ_Drugs all structures {.tabset}

Extract quantile: ALZ_Drugs all structures
```{r}
meta_data_vector <- NULL
ALZ_Drugs_structure <- NULL

for (i in 1:length(meta_data_se_ALZ_Drugs)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$quantile <- quantile(as.numeric(meta_data_se_ALZ_Drugs[,i]), probs = 0.99)
        ALZ_Drugs_structure <- rbind(ALZ_Drugs_structure,meta_data_vector)
}
rownames(ALZ_Drugs_structure) <- 1:length(meta_data_se_ALZ_Drugs)
ALZ_Drugs_structure <- as.data.frame(ALZ_Drugs_structure)
ALZ_Drugs_structure <- unlist(ALZ_Drugs_structure$quantile)
ALZ_Drugs_structure <- as.data.frame(ALZ_Drugs_structure)
ALZ_Drugs_structure$Rank <- 1:length(meta_data_se_ALZ_Drugs)
colnames(ALZ_Drugs_structure) <- c("quantile","Rank")
```

### ALZ_Drugs all structures
```{r, fig.width=10}
plot(ALZ_Drugs_structure$Rank,ALZ_Drugs_structure$quantile, main = "ALZ Drugs all structures", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.1,0.5))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50), col="darkred", lwd = 2, lty = 2)
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se, 
               features = c("ALZ_Drugs_Rank1_1","ALZ_Drugs_Rank2_1","ALZ_Drugs_Rank3_1","ALZ_Drugs_Rank4_1","ALZ_Drugs_Rank5_1","ALZ_Drugs_Rank6_1","ALZ_Drugs_Rank7_1","ALZ_Drugs_Rank8_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### Violin plots 1-8
```{r}
se <- SetIdent(se, value = "seurat_clusters")

VlnPlot(se, features = c("ALZ_Drugs_Rank1_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Drugs_Rank2_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Drugs_Rank3_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Drugs_Rank4_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Drugs_Rank5_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Drugs_Rank6_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Drugs_Rank7_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))
VlnPlot(se, features = c("ALZ_Drugs_Rank8_1"), ncol = 1, group.by = "seurat_clusters", cols = col_vector) + geom_boxplot(width=0.4) + theme(plot.title = element_text(size = 12))

```


## ALZ_Drugs structure 0 {.tabset}


Extract median: ALZ_Drugs structure 0
```{r}
meta_data_vector <- NULL
ALZ_Drugs_structure_0 <- NULL

for (i in 1:length(meta_data_se_0_ALZ_Drugs)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_0_ALZ_Drugs[,i])
        ALZ_Drugs_structure_0 <- rbind(ALZ_Drugs_structure_0,meta_data_vector)
}
rownames(ALZ_Drugs_structure_0) <- 1:length(meta_data_se_0_ALZ_Drugs)
ALZ_Drugs_structure_0 <- as.data.frame(ALZ_Drugs_structure_0)
```

### ALZ_Drugs windows
```{r, fig.width=10}
plot(ALZ_Drugs_structure_0$Rank,ALZ_Drugs_structure_0$Median, main = "ALZ Drugs Structure 0", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,1]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,1]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,1]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,1]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,1]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Drugs Structure 0
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster0_d <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Drugs), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Drugs)){
  
  OT_genetic_window <- as.numeric(ALZ_Drugs_structure_0[i,2])
  perm.mat.window50.cluster0_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_0 >= OT_genetic_window)
  
  cluster0_w_p.val <- (nrow(perm.mat.window50.cluster0_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster0_d[i,1] <- as.numeric(cluster0_w_p.val)
  
  cluster0_w_p.val.adj <- p.adjust(cluster0_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster0_d[i,2] <- as.numeric(cluster0_w_p.val.adj)
}

p.mat.cluster0_d[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_0, 
               features = c("ALZ_Drugs_Rank1_1","ALZ_Drugs_Rank2_1","ALZ_Drugs_Rank3_1","ALZ_Drugs_Rank4_1","ALZ_Drugs_Rank5_1","ALZ_Drugs_Rank6_1","ALZ_Drugs_Rank7_1","ALZ_Drugs_Rank8_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_0 <- as.data.frame(perm.mat.drugs.data$cluster_0)
colnames(median_score_NULL_permutations_cluster_0) <- c("Median_scores")

# permutation p-value
perm.mat.drugs.cluster0_bigger <- subset(perm.mat.drugs.data,perm.mat.drugs.data$cluster_0 >= as.numeric(median(se_0$OpenTargets_ALZ_Drugs_1)))

cluster0_p.val.d <- (nrow(perm.mat.drugs.cluster0_bigger)+1)/(permutation.nr+1)
cluster0_p.val.d.adj <- p.adjust(cluster0_p.val.d,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster0_p.val.d.adj_text <- as.character(round(cluster0_p.val.d.adj, digits = 4))
cluster0_p.val.d.adj_text <- paste0(c("p.val.adj = "),cluster0_p.val.d.adj_text)

p.val.mat.d[1,1] <- -log10(cluster0_p.val.d)
p.val.mat.d[2,1] <- -log10(cluster0_p.val.d.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_0 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_0$OpenTargets_ALZ_Drugs_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster0_p.val.d.adj_text)+
  ggtitle("Structure 0")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```


## ALZ_Drugs structure 1 {.tabset}


Extract median: ALZ_Drugs structure 1
```{r}
meta_data_vector <- NULL
ALZ_Drugs_structure_1 <- NULL

for (i in 1:length(meta_data_se_1_ALZ_Drugs)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_1_ALZ_Drugs[,i])
        ALZ_Drugs_structure_1 <- rbind(ALZ_Drugs_structure_1,meta_data_vector)
}
rownames(ALZ_Drugs_structure_1) <- 1:length(meta_data_se_1_ALZ_Drugs)
ALZ_Drugs_structure_1 <- as.data.frame(ALZ_Drugs_structure_1)
```

### ALZ_Drugs windows
```{r, fig.width=10}
plot(ALZ_Drugs_structure_1$Rank,ALZ_Drugs_structure_1$Median, main = "ALZ Drugs Structure 1", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,2]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,2]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,2]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,2]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,2]), col="darkred", lwd = 2, lty = 2)
```

Permutation p-value windows: ALZ Drugs Structure 1
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster1_d <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Drugs), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Drugs)){
  
  OT_genetic_window <- as.numeric(ALZ_Drugs_structure_1[i,2])
  perm.mat.window50.cluster1_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_1 >= OT_genetic_window)
  
  cluster1_w_p.val <- (nrow(perm.mat.window50.cluster1_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster1_d[i,1] <- as.numeric(cluster1_w_p.val)
  
  cluster1_w_p.val.adj <- p.adjust(cluster1_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster1_d[i,2] <- as.numeric(cluster1_w_p.val.adj)
}

p.mat.cluster1_d[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_1, 
               features = c("ALZ_Drugs_Rank1_1","ALZ_Drugs_Rank2_1","ALZ_Drugs_Rank3_1","ALZ_Drugs_Rank4_1","ALZ_Drugs_Rank5_1","ALZ_Drugs_Rank6_1","ALZ_Drugs_Rank7_1","ALZ_Drugs_Rank8_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_1 <- as.data.frame(perm.mat.drugs.data$cluster_1)
colnames(median_score_NULL_permutations_cluster_1) <- c("Median_scores")

# permutation p-value
perm.mat.drugs.cluster1_bigger <- subset(perm.mat.drugs.data,perm.mat.drugs.data$cluster_1 >= as.numeric(median(se_1$OpenTargets_ALZ_Drugs_1)))

cluster1_p.val.d <- (nrow(perm.mat.drugs.cluster1_bigger)+1)/(permutation.nr+1)
cluster1_p.val.d.adj <- p.adjust(cluster1_p.val.d,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster1_p.val.d.adj_text <- as.character(round(cluster1_p.val.d.adj, digits = 4))
cluster1_p.val.d.adj_text <- paste0(c("p.val.adj = "),cluster1_p.val.d.adj_text)

p.val.mat.d[1,2] <- -log10(cluster1_p.val.d)
p.val.mat.d[2,2] <- -log10(cluster1_p.val.d.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_1 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_1$OpenTargets_ALZ_Drugs_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster1_p.val.d.adj_text)+
  ggtitle("Structure 1")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```

## ALZ_Drugs structure 2 {.tabset}


Extract median: ALZ_Drugs structure 2
```{r}
meta_data_vector <- NULL
ALZ_Drugs_structure_2 <- NULL

for (i in 1:length(meta_data_se_2_ALZ_Drugs)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_2_ALZ_Drugs[,i])
        ALZ_Drugs_structure_2 <- rbind(ALZ_Drugs_structure_2,meta_data_vector)
}
rownames(ALZ_Drugs_structure_2) <- 1:length(meta_data_se_2_ALZ_Drugs)
ALZ_Drugs_structure_2 <- as.data.frame(ALZ_Drugs_structure_2)
```

### ALZ_Drugs windows
```{r, fig.width=10}
plot(ALZ_Drugs_structure_2$Rank,ALZ_Drugs_structure_2$Median, main = "ALZ Drugs Structure 2", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,3]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,3]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,3]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,3]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,3]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Drugs Structure 2
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster2_d <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Drugs), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Drugs)){
  
  OT_genetic_window <- as.numeric(ALZ_Drugs_structure_2[i,2])
  perm.mat.window50.cluster2_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_2 >= OT_genetic_window)
  
  cluster2_w_p.val <- (nrow(perm.mat.window50.cluster2_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster2_d[i,1] <- as.numeric(cluster2_w_p.val)
  
  cluster2_w_p.val.adj <- p.adjust(cluster2_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster2_d[i,2] <- as.numeric(cluster2_w_p.val.adj)
}

p.mat.cluster2_d[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_2, 
               features = c("ALZ_Drugs_Rank1_1","ALZ_Drugs_Rank2_1","ALZ_Drugs_Rank3_1","ALZ_Drugs_Rank4_1","ALZ_Drugs_Rank5_1","ALZ_Drugs_Rank6_1","ALZ_Drugs_Rank7_1","ALZ_Drugs_Rank8_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_2 <- as.data.frame(perm.mat.drugs.data$cluster_2)
colnames(median_score_NULL_permutations_cluster_2) <- c("Median_scores")

# permutation p-value
perm.mat.drugs.cluster2_bigger <- subset(perm.mat.drugs.data,perm.mat.drugs.data$cluster_2 >= as.numeric(median(se_2$OpenTargets_ALZ_Drugs_1)))

cluster2_p.val.d <- (nrow(perm.mat.drugs.cluster2_bigger)+1)/(permutation.nr+1)
cluster2_p.val.d.adj <- p.adjust(cluster2_p.val.d,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster2_p.val.d.adj_text <- as.character(round(cluster2_p.val.d.adj, digits = 4))
cluster2_p.val.d.adj_text <- paste0(c("p.val.adj = "),cluster2_p.val.d.adj_text)

p.val.mat.d[1,3] <- -log10(cluster2_p.val.d)
p.val.mat.d[2,3] <- -log10(cluster2_p.val.d.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_2 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_2$OpenTargets_ALZ_Drugs_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster2_p.val.d.adj_text)+
  ggtitle("Structure 2")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```


## ALZ_Drugs structure 3 {.tabset}


Extract median: ALZ_Drugs structure 3
```{r}
meta_data_vector <- NULL
ALZ_Drugs_structure_3 <- NULL

for (i in 1:length(meta_data_se_3_ALZ_Drugs)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_3_ALZ_Drugs[,i])
        ALZ_Drugs_structure_3 <- rbind(ALZ_Drugs_structure_3,meta_data_vector)
}
rownames(ALZ_Drugs_structure_3) <- 1:length(meta_data_se_3_ALZ_Drugs)
ALZ_Drugs_structure_3 <- as.data.frame(ALZ_Drugs_structure_3)
```


### ALZ_Drugs windows
```{r, fig.width=10}
plot(ALZ_Drugs_structure_3$Rank,ALZ_Drugs_structure_3$Median, main = "ALZ Drugs Structure 3", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,4]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,4]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,4]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,4]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,4]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Drugs Structure 3
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster3_d <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Drugs), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Drugs)){
  
  OT_genetic_window <- as.numeric(ALZ_Drugs_structure_3[i,2])
  perm.mat.window50.cluster3_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_3 >= OT_genetic_window)
  
  cluster3_w_p.val <- (nrow(perm.mat.window50.cluster3_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster3_d[i,1] <- as.numeric(cluster3_w_p.val)
  
  cluster3_w_p.val.adj <- p.adjust(cluster3_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster3_d[i,2] <- as.numeric(cluster3_w_p.val.adj)
}

p.mat.cluster3_d[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_3, 
               features = c("ALZ_Drugs_Rank1_1","ALZ_Drugs_Rank2_1","ALZ_Drugs_Rank3_1","ALZ_Drugs_Rank4_1","ALZ_Drugs_Rank5_1","ALZ_Drugs_Rank6_1","ALZ_Drugs_Rank7_1","ALZ_Drugs_Rank8_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_3 <- as.data.frame(perm.mat.drugs.data$cluster_3)
colnames(median_score_NULL_permutations_cluster_3) <- c("Median_scores")

# permutation p-value
perm.mat.drugs.cluster3_bigger <- subset(perm.mat.drugs.data,perm.mat.drugs.data$cluster_3 >= as.numeric(median(se_3$OpenTargets_ALZ_Drugs_1)))

cluster3_p.val.d <- (nrow(perm.mat.drugs.cluster3_bigger)+1)/(permutation.nr+1)
cluster3_p.val.d.adj <- p.adjust(cluster3_p.val.d,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster3_p.val.d.adj_text <- as.character(round(cluster3_p.val.d.adj, digits = 4))
cluster3_p.val.d.adj_text <- paste0(c("p.val.adj = "),cluster3_p.val.d.adj_text)

p.val.mat.d[1,4] <- -log10(cluster3_p.val.d)
p.val.mat.d[2,4] <- -log10(cluster3_p.val.d.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_3 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_3$OpenTargets_ALZ_Drugs_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster3_p.val.d.adj_text)+
  ggtitle("Structure 3")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```


## ALZ_Drugs structure 4 {.tabset}


Extract median: ALZ_Drugs structure 4
```{r}
meta_data_vector <- NULL
ALZ_Drugs_structure_4 <- NULL

for (i in 1:length(meta_data_se_4_ALZ_Drugs)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_4_ALZ_Drugs[,i])
        ALZ_Drugs_structure_4 <- rbind(ALZ_Drugs_structure_4,meta_data_vector)
}
rownames(ALZ_Drugs_structure_4) <- 1:length(meta_data_se_4_ALZ_Drugs)
ALZ_Drugs_structure_4 <- as.data.frame(ALZ_Drugs_structure_4)
```

### ALZ_Drugs windows
```{r, fig.width=10}
plot(ALZ_Drugs_structure_4$Rank,ALZ_Drugs_structure_4$Median, main = "ALZ Drugs Structure 4", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,5]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,5]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,5]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,5]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,5]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Drugs Structure 4
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster4_d <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Drugs), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Drugs)){
  
  OT_genetic_window <- as.numeric(ALZ_Drugs_structure_4[i,2])
  perm.mat.window50.cluster4_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_4 >= OT_genetic_window)
  
  cluster4_w_p.val <- (nrow(perm.mat.window50.cluster4_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster4_d[i,1] <- as.numeric(cluster4_w_p.val)
  
  cluster4_w_p.val.adj <- p.adjust(cluster4_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster4_d[i,2] <- as.numeric(cluster4_w_p.val.adj)
}

p.mat.cluster4_d[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_4, 
               features = c("ALZ_Drugs_Rank1_1","ALZ_Drugs_Rank2_1","ALZ_Drugs_Rank3_1","ALZ_Drugs_Rank4_1","ALZ_Drugs_Rank5_1","ALZ_Drugs_Rank6_1","ALZ_Drugs_Rank7_1","ALZ_Drugs_Rank8_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_4 <- as.data.frame(perm.mat.drugs.data$cluster_4)
colnames(median_score_NULL_permutations_cluster_4) <- c("Median_scores")

# permutation p-value
perm.mat.drugs.cluster4_bigger <- subset(perm.mat.drugs.data,perm.mat.drugs.data$cluster_4 >= as.numeric(median(se_4$OpenTargets_ALZ_Drugs_1)))

cluster4_p.val.d <- (nrow(perm.mat.drugs.cluster4_bigger)+1)/(permutation.nr+1)
cluster4_p.val.d.adj <- p.adjust(cluster4_p.val.d,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster4_p.val.d.adj_text <- as.character(round(cluster4_p.val.d.adj, digits = 4))
cluster4_p.val.d.adj_text <- paste0(c("p.val.adj = "),cluster4_p.val.d.adj_text)

p.val.mat.d[1,5] <- -log10(cluster4_p.val.d)
p.val.mat.d[2,5] <- -log10(cluster4_p.val.d.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_4 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_4$OpenTargets_ALZ_Drugs_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster4_p.val.d.adj_text)+
  ggtitle("Structure 4")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```



## ALZ_Drugs structure 5 {.tabset}


Extract median: ALZ_Drugs structure 5
```{r}
meta_data_vector <- NULL
ALZ_Drugs_structure_5 <- NULL

for (i in 1:length(meta_data_se_5_ALZ_Drugs)){
        meta_data_vector$Rank <- as.character(i)
        meta_data_vector$Median <- median(meta_data_se_5_ALZ_Drugs[,i])
        ALZ_Drugs_structure_5 <- rbind(ALZ_Drugs_structure_5,meta_data_vector)
}
rownames(ALZ_Drugs_structure_5) <- 1:length(meta_data_se_5_ALZ_Drugs)
ALZ_Drugs_structure_5 <- as.data.frame(ALZ_Drugs_structure_5)
```

### ALZ_Drugs windows
```{r, fig.width=10}
plot(ALZ_Drugs_structure_5$Rank,ALZ_Drugs_structure_5$Median, main = "ALZ Drugs Structure 5", xlab = "Rank", ylab = "Score", type = "o", ylim=c(-0.3,0.3))
axis(1, at = seq(1, 200, by = 1), cex.axis = 0.5)

abline(h = max(perm.mat.window50[,6]), col="darkred", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,6]), probs = 0.95), col = "red", lwd = 2, lty = 2)
abline(h = median(perm.mat.window50[,6]), col="blue", lwd = 2, lty = 2)
abline(h = quantile(as.numeric(perm.mat.window50[,6]), probs = 0.05), col = "red", lwd = 2, lty = 2)
abline(h = min(perm.mat.window50[,6]), col="darkred", lwd = 2, lty = 2)
```


Permutation p-value windows: ALZ Drugs Structure 5
```{r}

#P.value across window ranks
Rank_names <- rep("Rank_nr", length(window50_rank_list_ALZ_Drugs))
Rank_names <- paste0(Rank_names,sep=1:length(Rank_names))

#P.value matrix
p.mat.cluster5_d <- matrix(data = NA, nrow = length(window50_rank_list_ALZ_Drugs), ncol = 2, dimnames = list(Rank_names,c("p.val","p.val.adj")))


for (i in 1:length(window50_rank_list_ALZ_Drugs)){
  
  OT_genetic_window <- as.numeric(ALZ_Drugs_structure_5[i,2])
  perm.mat.window50.cluster5_bigger_window <- subset(perm.mat.window50.data,perm.mat.window50.data$cluster_5 >= OT_genetic_window)
  
  cluster5_w_p.val <- (nrow(perm.mat.window50.cluster5_bigger_window)+1)/(permutation.nr+1)
  p.mat.cluster5_d[i,1] <- as.numeric(cluster5_w_p.val)
  
  cluster5_w_p.val.adj <- p.adjust(cluster5_w_p.val,method = c("bonferroni"), n=nr_of_tests)
  p.mat.cluster5_d[i,2] <- as.numeric(cluster5_w_p.val.adj)
}

p.mat.cluster5_d[,1]
```


### ST.FeaturePlot
```{r, fig.width=10, fig.height=6}

spot_alpha = 0.5
point.size = 1

ST.FeaturePlot(se_5, 
               features = c("ALZ_Drugs_Rank1_1","ALZ_Drugs_Rank2_1","ALZ_Drugs_Rank3_1","ALZ_Drugs_Rank4_1","ALZ_Drugs_Rank5_1","ALZ_Drugs_Rank6_1","ALZ_Drugs_Rank7_1","ALZ_Drugs_Rank8_1"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               grid.ncol = 4,
               cols = c("black", "darkblue", "cyan", "yellow", "red", "darkred"),
               value.scale = "all")

```


### P.val.adj structure
```{r}
# Median score of NULL gene set permutations
median_score_NULL_permutations_cluster_5 <- as.data.frame(perm.mat.drugs.data$cluster_5)
colnames(median_score_NULL_permutations_cluster_5) <- c("Median_scores")

# permutation p-value
perm.mat.drugs.cluster5_bigger <- subset(perm.mat.drugs.data,perm.mat.drugs.data$cluster_5 >= as.numeric(median(se_5$OpenTargets_ALZ_Drugs_1)))

cluster5_p.val.d <- (nrow(perm.mat.drugs.cluster5_bigger)+1)/(permutation.nr+1)
cluster5_p.val.d.adj <- p.adjust(cluster5_p.val.d,method = c("bonferroni"), n=nr_of_tests) # Bonferroni

cluster5_p.val.d.adj_text <- as.character(round(cluster5_p.val.d.adj, digits = 4))
cluster5_p.val.d.adj_text <- paste0(c("p.val.adj = "),cluster5_p.val.d.adj_text)

p.val.mat.d[1,6] <- -log10(cluster5_p.val.d)
p.val.mat.d[2,6] <- -log10(cluster5_p.val.d.adj)

theme_set(theme_classic()) # Density plot
median_score_NULL_permutations_cluster_5 %>%
  ggplot( aes(x=Median_scores)) +
    geom_density(fill="#69b3a2", alpha=0.8)+ 
    geom_vline(xintercept = as.numeric(median(se_5$OpenTargets_ALZ_Drugs_1)), color = "purple", size=1)+
  annotate("text", x=0, y=0, label= cluster5_p.val.d.adj_text)+
  ggtitle("Structure 5")+
  xlab("Median score NULL gene set")+
  ylab("Density")

```




# Spatial p-value plot Genetic {.tabset}

Adding p.val genetic to metadata
```{r}
se$p.val.g <- se$seurat_clusters

se$p.val.g[se$p.val.g == '0'] <- p.val.mat.g[1,1]
se$p.val.g[se$p.val.g == '1'] <- p.val.mat.g[1,2]
se$p.val.g[se$p.val.g == '2'] <- p.val.mat.g[1,3]
se$p.val.g[se$p.val.g == '3'] <- p.val.mat.g[1,4]
se$p.val.g[se$p.val.g == '4'] <- p.val.mat.g[1,5]
se$p.val.g[se$p.val.g == '5'] <- p.val.mat.g[1,6]
```


## ST.FeaturePlot viridis
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(object = se, features = "p.val.g", pt.size = 1.5, cols = viridis(nr_of_tests))
```

## FeatureOverlay viridis
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1

FeatureOverlay(se, 
               features = c("p.val.g"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = viridis(nr_of_tests))
```



# Spatial p-value plot Genetic (bonferroni) {.tabset}

Adding p.val.adj genetic to metadata
```{r}
se$p.val.adj.g <- se$seurat_clusters

se$p.val.adj.g[se$p.val.adj.g == '0'] <- p.val.mat.g[2,1]
se$p.val.adj.g[se$p.val.adj.g == '1'] <- p.val.mat.g[2,2]
se$p.val.adj.g[se$p.val.adj.g == '2'] <- p.val.mat.g[2,3]
se$p.val.adj.g[se$p.val.adj.g == '3'] <- p.val.mat.g[2,4]
se$p.val.adj.g[se$p.val.adj.g == '4'] <- p.val.mat.g[2,5]
se$p.val.adj.g[se$p.val.adj.g == '5'] <- p.val.mat.g[2,6]
```


## ST.FeaturePlot viridis
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(object = se, features = "p.val.adj.g", pt.size = 1.5, cols = viridis(nr_of_tests))

p.val.mat.g
```

## FeatureOverlay viridis
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1

FeatureOverlay(se, 
               features = c("p.val.adj.g"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = viridis(nr_of_tests))
```


# Spatial p-value plot Drugs {.tabset}

Adding p.val drugs to metadata
```{r}
se$p.val.d <- se$seurat_clusters

se$p.val.d[se$p.val.d == '0'] <- p.val.mat.d[1,1]
se$p.val.d[se$p.val.d == '1'] <- p.val.mat.d[1,2]
se$p.val.d[se$p.val.d == '2'] <- p.val.mat.d[1,3]
se$p.val.d[se$p.val.d == '3'] <- p.val.mat.d[1,4]
se$p.val.d[se$p.val.d == '4'] <- p.val.mat.d[1,5]
se$p.val.d[se$p.val.d == '5'] <- p.val.mat.d[1,6]
```


## ST.FeaturePlot viridis
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(object = se, features = "p.val.d", pt.size = 1.5, cols = viridis(nr_of_tests)) 
```

## FeatureOverlay viridis
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1

FeatureOverlay(se, 
               features = c("p.val.d"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = viridis(nr_of_tests))
```


# Spatial p-value plot Drugs (bonferroni) {.tabset}

Adding p.val.adj drugs to metadata
```{r}
se$p.val.adj.d <- se$seurat_clusters

se$p.val.adj.d[se$p.val.adj.d == '0'] <- p.val.mat.d[2,1]
se$p.val.adj.d[se$p.val.adj.d == '1'] <- p.val.mat.d[2,2]
se$p.val.adj.d[se$p.val.adj.d == '2'] <- p.val.mat.d[2,3]
se$p.val.adj.d[se$p.val.adj.d == '3'] <- p.val.mat.d[2,4]
se$p.val.adj.d[se$p.val.adj.d == '4'] <- p.val.mat.d[2,5]
se$p.val.adj.d[se$p.val.adj.d == '5'] <- p.val.mat.d[2,6]
```


## ST.FeaturePlot viridis
```{r, fig.width=5, fig.height=4}
ST.FeaturePlot(object = se, features = "p.val.adj.d", pt.size = 1.5, cols = viridis(nr_of_tests)) 

p.val.mat.d
```

## FeatureOverlay viridis
```{r, fig.width=5, fig.height=4}
spot_alpha = 0.5
point.size = 1

FeatureOverlay(se, 
               features = c("p.val.adj.d"),
               pt.alpha = spot_alpha,
               pt.size = point.size,
               add.alpha=T,
               ncols = 1,
               cols = viridis(nr_of_tests))
```


# Save p-val files

```{r}
meta.data_all <- se@meta.data
meta.data_all$CellID <- rownames(meta.data_all)

meta.data <- data.frame(matrix(nrow = nrow(meta.data_all), ncol = 1))

meta.data$CellID <- meta.data_all$CellID

meta.data$neg.log10.p.val.g <- meta.data_all$p.val.g
meta.data$neg.log10.p.val.g <- as.numeric(meta.data$neg.log10.p.val.g)

meta.data$neg.log10.p.val.adj.g <- meta.data_all$p.val.adj.g
meta.data$neg.log10.p.val.adj.g <- as.numeric(meta.data$neg.log10.p.val.adj.g)


meta.data$neg.log10.p.val.d <- meta.data_all$p.val.d
meta.data$neg.log10.p.val.d <- as.numeric(meta.data$neg.log10.p.val.d)

meta.data$neg.log10.p.val.adj.d <- meta.data_all$p.val.adj.d
meta.data$neg.log10.p.val.adj.d <- as.numeric(meta.data$neg.log10.p.val.adj.d)

meta.data$matrix.nrow...nrow.meta.data_all...ncol...1. <- NULL
```


```{r, eval=T}
saveRDS(meta.data,file = "Meta_data_pval/meta.data.pval_ALZ_all_genes.RDS")

write.matrix(meta.data,file="Meta_data_pval/meta.data.pval_ALZ_all_genes.csv",sep = ";")
```



Create matrix
```{r}
p.val.distribution <- matrix(data = NA, nrow = 8, ncol = length(cluster_names), dimnames = list(c("median(genes)","median(umi)","median(score_genetic)","-log10(p.val_genetic)","-log10(p.val.adj_genetic)","median(score_drugs)","-log10(p.val_drugs)","-log10(p.val.adj_drugs)"),cluster_names))
```


Add data to matrix
```{r}
p.val.distribution[4,] <- p.val.mat.g[1,]
p.val.distribution[5,] <- p.val.mat.g[2,]

p.val.distribution[7,] <- p.val.mat.d[1,]
p.val.distribution[8,] <- p.val.mat.d[2,]
```


Collect and add data to matrix
```{r}
# Calculate structure specific median number of genes
p.val.distribution[1,1] <- as.numeric(median(se_0$nFeature_RNA))
p.val.distribution[1,2] <- as.numeric(median(se_1$nFeature_RNA))
p.val.distribution[1,3] <- as.numeric(median(se_2$nFeature_RNA))
p.val.distribution[1,4] <- as.numeric(median(se_3$nFeature_RNA))
p.val.distribution[1,5] <- as.numeric(median(se_4$nFeature_RNA))
p.val.distribution[1,6] <- as.numeric(median(se_5$nFeature_RNA))

# Calculate structure specific median number of umis
p.val.distribution[2,1] <- as.numeric(median(se_0$nCount_RNA))
p.val.distribution[2,2] <- as.numeric(median(se_1$nCount_RNA))
p.val.distribution[2,3] <- as.numeric(median(se_2$nCount_RNA))
p.val.distribution[2,4] <- as.numeric(median(se_3$nCount_RNA))
p.val.distribution[2,5] <- as.numeric(median(se_4$nCount_RNA))
p.val.distribution[2,6] <- as.numeric(median(se_5$nCount_RNA))

# Calculate structure specific median number of genetic score
p.val.distribution[3,1] <- as.numeric(median(se_0$OpenTargets_ALZ_Genetic_1))
p.val.distribution[3,2] <- as.numeric(median(se_1$OpenTargets_ALZ_Genetic_1))
p.val.distribution[3,3] <- as.numeric(median(se_2$OpenTargets_ALZ_Genetic_1))
p.val.distribution[3,4] <- as.numeric(median(se_3$OpenTargets_ALZ_Genetic_1))
p.val.distribution[3,5] <- as.numeric(median(se_4$OpenTargets_ALZ_Genetic_1))
p.val.distribution[3,6] <- as.numeric(median(se_5$OpenTargets_ALZ_Genetic_1))

# Calculate structure specific median number of drugs score
p.val.distribution[6,1] <- as.numeric(median(se_0$OpenTargets_ALZ_Drugs_1))
p.val.distribution[6,2] <- as.numeric(median(se_1$OpenTargets_ALZ_Drugs_1))
p.val.distribution[6,3] <- as.numeric(median(se_2$OpenTargets_ALZ_Drugs_1))
p.val.distribution[6,4] <- as.numeric(median(se_3$OpenTargets_ALZ_Drugs_1))
p.val.distribution[6,5] <- as.numeric(median(se_4$OpenTargets_ALZ_Drugs_1))
p.val.distribution[6,6] <- as.numeric(median(se_5$OpenTargets_ALZ_Drugs_1))

p.val.distribution <- as.data.frame(p.val.distribution)
p.val.distribution_plot <- as.data.frame(t(p.val.distribution))

p.val.distribution_plot$cluster <- rownames(p.val.distribution_plot)
```


# Plot p.value.adj cluster Genetic
```{r}
parameter <- par(mfrow=c(2,2))

parameter <- plot(p.val.distribution_plot$`median(genes)`,p.val.distribution_plot$`-log10(p.val.adj_genetic)`,pch = 19, ylab = "-log10(p.val.adj_genetic)", xlab = "median(genes)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")

parameter <- plot(p.val.distribution_plot$`median(umi)`,p.val.distribution_plot$`-log10(p.val.adj_genetic)`,pch = 19, ylab = "-log10(p.val.adj_genetic)", xlab = "median(umi)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")

parameter <- plot(p.val.distribution_plot$`median(score_genetic)`,p.val.distribution_plot$`-log10(p.val.adj_genetic)`,pch = 19, ylab = "-log10(p.val.adj_genetic)", xlab = "median(score_genetic)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")

parameter <- plot(p.val.distribution_plot$`median(score_drugs)`,p.val.distribution_plot$`-log10(p.val.adj_genetic)`,pch = 19, ylab = "-log10(p.val.adj_genetic)", xlab = "median(score_drugs)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")
```


# Plot p.value.adj cluster Drugs
```{r}
parameter <- par(mfrow=c(2,2))

parameter <- plot(p.val.distribution_plot$`median(genes)`,p.val.distribution_plot$`-log10(p.val.adj_drugs)`,pch = 19, ylab = "-log10(p.val.adj_drugs)", xlab = "median(genes)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")

parameter <- plot(p.val.distribution_plot$`median(umi)`,p.val.distribution_plot$`-log10(p.val.adj_drugs)`,pch = 19, ylab = "-log10(p.val.adj_drugs)", xlab = "median(umi)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")

parameter <- plot(p.val.distribution_plot$`median(score_genetic)`,p.val.distribution_plot$`-log10(p.val.adj_drugs)`,pch = 19, ylab = "-log10(p.val.adj_drugs)", xlab = "median(score_genetic)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")

parameter <- plot(p.val.distribution_plot$`median(score_drugs)`,p.val.distribution_plot$`-log10(p.val.adj_drugs)`,pch = 19, ylab = "-log10(p.val.adj_drugs)", xlab = "median(score_drugs)",ylim=c(0,4))
abline(h=-log10(0.05),col = "red")
```



```{r, eval=T}
saveRDS(p.val.distribution_plot,file = "p_value_distribution/pval.distribution_ALZ_all_genes.RDS")

write.matrix(p.val.distribution_plot,file="p_value_distribution/pval.distribution_ALZ_all_genes.csv",sep = ";")
```


# Jaccard index

Jaccard function:
```{r}
jaccard <- function(a, b) {
  intersection = length(intersect(a, b))
  union = length(a) + length(b) - intersection
  return (intersection/union)
}
```


Print all genes shared combinations:
```{r}
# två for-loopar
# Börja med att skapa en tom matrix med lika många kolumner som rader
# kolumn- och rad-namn ska vara samma som namnen på hallmark gene sets
length.mat <- matrix(data = NA, 
                  nrow = length(all_gene_sets), 
                  ncol = length(all_gene_sets), 
                  dimnames = list(names(all_gene_sets), 
                                  names(all_gene_sets)))


# Iterera över två for-loopar, en för rader och en för kolumner
for (i in 1:length(all_gene_sets)) {
  for (j in 1:length(all_gene_sets)) {
    # Spara jaccard mellan par av gene sets
    length.mat[i, j] <- jaccard(all_gene_sets[[i]],all_gene_sets[[j]])
  }
}


```


```{r, fig.height=12, fig.width=14}
length.mat.df <- as.data.frame(length.mat)

library(tidyverse)

df2 <- length.mat.df %>%
  rownames_to_column() %>%
  gather(colname, value, -rowname)
head(df2)

df2$value <- ifelse(df2$rowname == df2$colname, NA, df2$value)

```


Re-format plot
```{r, fig.height=28, fig.width=35}


# Create a ggheatmap
ggheatmap <- ggplot(df2, aes(colname, rowname, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, space = "Lab", 
    name="Jaccard\nindex", limits=c(0,1)) +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()

# Print the heatmap
ggheatmap + ggtitle("All gene sets")


```

# Notes

Session info
```{r}
sessionInfo()
```

